### 2019-06-28 README.Rmd
Initial commit

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# worldheritagewikipedia

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)

This repository contains the data and code for our paper:

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to cite

Please cite this compendium as:

> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

### How to download or install

You can download the compendium as a zip from from this URL: </archive/master.zip>

Or you can install this compendium as an R package, worldheritagewikipedia, from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("/")
```

### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

### 2019-06-28 analysis/paper/paper.Rmd
getting organised

---
title: "Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia"
author:
  - Ben Marwick
  - Prema Smith
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  Text of abstract
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

<!-- This is the format for text comments that will be ignored during renderings. Do not put R code in these comments because it will not be ignored. -->

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  comment = "#>",
  fig.path = "../figures/"
)
```

# Introduction

Here is a citation [@Marwick2017]

# Background

# Methods

# Results

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

# Discussion

# Conclusion

# Acknowledgements

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

# References 
<!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
<div id="refs"></div>

##### pagebreak

### Colophon

This report was generated on `r Sys.time()` using the following computational environment and dependencies:

```{r colophon, cache = FALSE}
# which R packages and versions?
devtools::session_info()
```

The current Git commit details are:

```{r}
# what commit is this file at? 
git2r::repository(here::here())
```

### 2019-06-28 analysis/paper/000-russia.R

@@ -1,0 +1,83 @@
+
+
+russia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Russia"
+
+russia__xml_tables <- 
+read_html(russia) %>% 
+  html_nodes("table")
+
+russia_tables_tbl <- 
+map(russia__xml_tables, 
+    ~html_table(.x, fill = TRUE) %>% as_tibble(., .name_repair = "unique")) 
+
+russia_tables_tbl_culture <- 
+russia_tables_tbl[[2]] %>% 
+  mutate(type = ifelse(Image == "", NA, Image),
+         type = zoo::na.locf(type)) %>% 
+  filter(type == "Cultural") %>% 
+  slice(-1) %>% 
+  select(Name, Location, Yearlisted, Description) %>% 
+  set_names(c("Site", "Location", "Year", "Description")) %>% 
+  mutate(Year_num = ifelse(is.integer(Year), Year, parse_number(Year))) 
+
+
+# scrape out the coords for mapping
+coords_chars <- "\\d|°|′|″|N|E|S|W|\\."
+russia_tables_tbl_culture_coords <- 
+  map_chr(str_extract_all(russia_tables_tbl_culture$Location, 
+                          coords_chars), 
+          ~paste0(.x, collapse = "") %>% 
+            str_replace_all(., "^[A-Z]*", "") %>% 
+            str_extract(., ".+?(?=E|W)"))
+
+russia_coords_clean <- 
+  russia_tables_tbl_culture_coords %>% 
+  str_split("N|S") %>% 
+  Reduce(rbind, .) %>% 
+  as_tibble(., .name_repair = "universal") %>% 
+  mutate(lat = parse_lat(`...1`),
+         lon = parse_lon(`...2`))
+
+# attach clean coords to main table
+russia_tbl_coords <- 
+  russia_tables_tbl_culture %>% 
+  bind_cols(russia_coords_clean)
+
+# get country of site from location text
+russia_tbl_coords <- 
+  russia_tbl_coords %>% 
+  mutate(country = "Russia",
+         Criteria = 'Cultural',
+         `Areaha (acre)` = NA)
+ 
+# get links to each site's wiki page 
+get_link <- function(html_table, Site){
+  html_table %>% 
+    html_nodes(xpath=paste0("//a[text()='", Site, "']")) %>% 
+    html_attr("href")
+}
+
+cols_we_want <-
+  c(
+    "Site"     ,
[…]

### 2019-06-28 analysis/paper/000-scrape-wikipedia-random-pages.R

@@ -1,0 +1,40 @@
+library(tidyverse)
+library('rvest')
+library(vegan)
+
+# gets a random WP page
+rando <- "https://en.wikipedia.org/wiki/Special:Random"
+
+# gets data about n WP pages
+n <- 10000
+random_page_data <- rerun(n, get_data_about_page_safe(rando) )
+
+# drops the pages that returned an error
+random_page_data_lst <- transpose(random_page_data)[["result"]]
+
+random_page_data_lst <- discard(random_page_data_lst, ~.x[1] == "some_problem")
+
+# put page data into a table
+random_page_data_tbl <- 
+  tibble(page_wordcount =      map_int(random_page_data_lst, ~.x$page_wordcount),
+         page_wikilinks_out =  map_int(random_page_data_lst, ~.x$page_wikilinks_out),
+         page_wikilinks_in =   map_int(random_page_data_lst, ~.x$page_wikilinks_in),
+         page_cited_items_on = map_int(random_page_data_lst, ~.x$page_cited_items_on),
+         rh_user_simpson_idx = map_dbl(random_page_data_lst, ~.x$rh_user_simpson_idx),
+         rh_user_bot_prop =    map_dbl(random_page_data_lst, ~.x$rh_user_bot_prop), 
+         rh_revert_prop =      map_dbl(random_page_data_lst, ~.x$rh_revert_prop), 
+         talk_page_wordcount = map_dbl(random_page_data_lst, ~.x$talk_page_wordcount),
+         page_views_last_n_days_total = map_int(random_page_data_lst, ~.x$page_views_last_n_days_total)
+  )
+
+random_page_data_tbl %>% 
+  gather(variable, value) %>% 
+  ggplot(aes(value)) +
+  geom_histogram() +
+  facet_wrap( ~ variable, scales = "free")
+
+
+
+saveRDS(random_page_data_tbl, "data/random_page_data_tbl.rds")
+
+saveRDS(random_page_data_lst, "data/random_page_data_lst.rds")

### 2019-06-28 analysis/paper/000-scrape-wikipedia.R

@@ -1,0 +1,530 @@
+# list of lists
+url <- "https://en.wikipedia.org/wiki/Lists_of_World_Heritage_Sites"
+
+# Table of sites per country can be found at each of these pages
+# probably the simplest entry point
+
+# Africa
+africa <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Africa"
+
+# Americas
+n_america <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_North_America"
+c_america <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Central_America"
+caribbean <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_the_Caribbean"
+s_america <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_South_America"
+
+# Asia
+n_and_c_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Northern_and_Central_Asia"
+w_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Western_Asia"
+e_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_sites_in_Eastern_Asia"
+s_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_sites_in_Southern_Asia"
+se_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Southeast_Asia"
+# # SE Asia list currently removed due to copyvio :( "https://en.wikipedia.org/w/index.php?title=List_of_World_Heritage_Sites_in_Southeast_Asia&direction=prev&oldid=878049179"
+
+# Europe
+n_europe <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Northern_Europe"
+w_europe <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_sites_in_Western_Europe"
+e_europe <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_sites_in_Eastern_Europe"
+s_europe <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Southern_Europe"
+
+# Oceania
+oceania <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Oceania"
+
+#-----------------------------------------------------
+
[…]

### 2019-06-28 analysis/paper/001-EDA.R

@@ -1,0 +1,307 @@
+library(tidyverse)
+
+page_data_for_all_pages <- readRDS("data/page_data_for_all_pages.rds")
+
+names(page_data_for_all_pages)
+
+normalize = function(x) (x-min(x))/(max(x)-min(x))
+
+#--------------------------------------------------------------------------
+# take a look at the distribution of page variables
+some_page_variables <- 
+  page_data_for_all_pages %>% 
+  select(page_wordcount, 
+         page_wikilinks_out,
+         page_wikilinks_in,
+         page_cited_items_on) %>% 
+  mutate(page_wikilinks_out_per_word = page_wikilinks_out / page_wordcount,
+         page_cited_items_on_per_word = page_cited_items_on / page_wordcount) 
+  
+some_page_variables %>% 
+  gather(variable, value) %>% 
+ggplot(aes(value)) +
+  geom_histogram() +
+  facet_wrap( ~ variable, 
+              scales = "free") +
+  scale_x_log10() +
+  theme_minimal()
+
+library(GGally)
+ggpairs( some_page_variables %>% 
+           mutate_all(log)) +
+  theme_minimal()
+
+# umap
+library(uwot)
+library("tmap")
+data("World")
+
+pages_umap_input <- 
+  some_page_variables  %>% 
+  mutate(page_wordcount_norm = normalize(page_wordcount),
+         page_wikilinks_in_norm= normalize(page_wikilinks_in),
+         page_wikilinks_out_per_word_norm = normalize(page_wikilinks_out_per_word),
+         page_cited_items_on_per_word_norm = normalize(page_cited_items_on_per_word)) %>% 
+  select(-page_wordcount,
+         -page_cited_items_on, 
+         -page_wikilinks_out,
+         -page_wikilinks_in,
+         -page_wikilinks_out_per_word,
+         -page_cited_items_on_per_word) %>% 
+  bind_cols(., page_data_for_all_pages[ , 'country'] ) %>% 
+  filter_all(all_vars(!is.na(.))) %>% 
+  left_join(World %>% 
+              select(name, continent), 
+            by = c('country' = 'name'))
+
+# compute umap
+
+pages_umap_input_selected <- 
+  pages_umap_input %>% 
+  select(-country, 
+         -continent,
+         -geometry
+         )  
+    
+pages_umap_output <- 
+  pages_umap_input_selected %>% 
[…]

### 2019-06-28 README.Rmd
a bit out of order

@@
 
-[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh///master?urlpath=rstudio)
+[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/worldheritagewikipedia/master?urlpath=rstudio)
 
@@
 
-You can download the compendium as a zip from from this URL: </archive/master.zip>
+You can download the compendium as a zip from from this URL: <https://github.com/benmarwick/worldheritagewikipedia/archive/master.zip>
 
@@
 # install.packages("devtools")
-remotes::install_github("/")
+remotes::install_github("benmarwick/worldheritagewikipedia")
 ```

### 2019-06-29 analysis/paper/paper.Rmd
Added schedule outline to test

@@
 ```
+# schedule outline
+Schedule:
+Breakdown –
+July
+-          6 pages (3 single)// 1500w BM
+-          section from background “what is…” 200w PS
+-          section from background “what are scholars saying about it…” 400w PS
+August
+-          6 pages (3 single)// 1500w BM
+-          continue section from background “what are scholars saying about it…” 400w PS
+September
+-          6 pages (3 single)// 1500w BM
+-          continue editing section PS
+-          Complete 1st draft before sept. 26th, UW term begins. Preferably by 19th, one week before to avoid overlapping.
+October
+-          Continue building to target word count BM/PS
+-          Complete 2nd draft by end of October
+November
+-          Continue editing, complete 3rd draft by date TBD
 

### 2019-06-30 analysis/paper/paper.Rmd
remove some stuff, put schedule into an issue

--- 2019-06-28 analysis/paper/paper.Rmd
@@
   Text of abstract
-keywords: |
-  keyword 1; keyword 2; keyword 3
-highlights: |
-  These are the highlights. 
 ---
@@
 
-Here is a citation [@Marwick2017]
-
 # Background
@@
 # Results
-
-```{r get-data, eval = FALSE}
-# Note the path that we need to use to access our data files when rendering this document
-my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
-```
-
-```{r demo-plot, fig.cap="A plot of random numbers"}
-plot(rnorm(10))
-```
-
-Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot
-
-```{r demo-inline-code}
-x <- round(pi, 2)
-```
-
-Here is an example of inline code `r x` in the middle of a sentence.
 

### 2019-08-06 analysis/paper/paper-with-sage-template/paper-with-sage-template.tex
add Sage Rmd template for 'Big Data and Society'

\documentclass[Royal,times,sageh]{sagej}

\usepackage{moreverb,url,natbib, multirow, tabularx}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\begin{document}

\title{A demonstration of the \LaTeX class file for Statistical Methods in
Medical Research with Rmarkdown}

\runninghead{Uthor \emph{et al}.}

\author{A. Uthor*\affilnum{1,2}, O. Tro\affilnum{2}, O. Vriga\affilnum{3}}

\affiliation{\affilnum{1}{Department of Incredible Research, University A, City A, Country A}\\\affilnum{2}{Department of Applied Things, University B, City B, Country B}\\\affilnum{3}{Very Important Stuff Committee, Institute C, City C, Country C}}

\corrauth{Corresponding author name, This is sample corresponding address.}

\email{\href{mailto:correspondingauthor@protonmail.com}{\nolinkurl{correspondingauthor@protonmail.com}}}

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean ut elit
odio. Donec fermentum tellus neque, vitae fringilla orci pretium vitae.
Fusce maximus finibus facilisis. Donec ut ullamcorper turpis. Donec ut
porta ipsum. Nullam cursus mauris a sapien ornare pulvinar. Aenean
malesuada molestie erat quis mattis. Praesent scelerisque posuere
faucibus. Praesent nunc nulla, ullamcorper ut ullamcorper sed, molestie
ut est. Donec consequat libero nisi, non semper velit vulputate et.
Quisque eleifend tincidunt ligula, bibendum finibus massa cursus eget.
Curabitur aliquet vehicula quam non pulvinar. Aliquam facilisis tortor
nec purus finibus, sit amet elementum eros sodales. Ut porta porttitor
vestibulum. Integer molestie, leo ut maximus aliquam, velit dui iaculis
nibh, eget hendrerit purus risus sit amet dolor. Sed sed tincidunt ex.
Curabitur imperdiet egestas tellus in iaculis. Maecenas ante neque,
pretium vel nisl at, lobortis lacinia neque. In gravida elit vel
volutpat imperdiet. Sed ut nulla arcu. Proin blandit interdum ex sit
amet laoreet. Phasellus efficitur, sem hendrerit mattis dapibus, nunc
tellus ornare nisi, nec eleifend enim nibh ac ipsum. Aenean tincidunt
nisl sit amet facilisis faucibus. Donec odio erat, bibendum eu imperdiet
sed, gravida luctus turpis.
\end{abstract}

\keywords{Class file; \LaTeX; SMMR; Rmarkdown;}

\maketitle

\hypertarget{the-article-header-information}{%
\section{The Article Header
Information}\label{the-article-header-information}}

YAML header:

\begin{verbatim}
output:
  rticles::sim_article:
    keep_tex: TRUE
\end{verbatim}

Configure the YAML header including the following elements:

\begin{itemize}
\item
  \texttt{title}: Title
\item
  \texttt{runninghead}: Author last names, use \emph{et al.} if there
  are three or more authors.
\item
  \texttt{author}: List of author(s) containing \texttt{name} and
  \texttt{num}
\item
  \texttt{corrauth}: Corresponding author's name and address.
\item
  \texttt{email}: Correspondence email
\item
  \texttt{abstract}: Limited to 200 words
\item
  \texttt{keywords}: Keywords for the article
\item
  \texttt{bibliography}: BibTeX \texttt{.bib} file
\item
  \texttt{bibliographystyle}: sageh or sagev
\item
  \texttt{classoption}: options of the \texttt{sagej} class
\end{itemize}

\hypertarget{remarks}{%
\subsection{Remarks}\label{remarks}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\item
  \texttt{bibliographystyle}
\item
  \texttt{classoption}
\item
  Keywords are separated by commas.
\end{enumerate}

\hypertarget{the-body-of-the-article}{%
\section{The Body of the Article}\label{the-body-of-the-article}}

\hypertarget{mathematics}{%
\subsection{Mathematics}\label{mathematics}}

Use mathematics in Rmarkdown as usual.

\hypertarget{figures-and-tables}{%
\subsection{Figures and Tables}\label{figures-and-tables}}

Figures are supported from R code:

\begin{verbatim}
x = rnorm(10)
y = rnorm(10)
plot(x, y)
\end{verbatim}

\begin{figure}
\includegraphics[width=1\linewidth]{paper-with-sage-template_files/figure-latex/plot-ref-1} \caption{Fancy Caption\label{fig:plot}}\label{fig:plot-ref}
\end{figure}

\ldots{}and can be referenced (Figure \ref{fig:plot}) by including the
\texttt{\textbackslash{}\textbackslash{}label\{\}} tag in the
\texttt{fig.cap} attribute of the R chunk:
\texttt{fig.cap\ =\ "Fancy\ Caption\textbackslash{}\textbackslash{}label\{fig:plot\}"}.
It is a quirky hack at the moment, see
\href{https://github.com/yihui/knitr/issues/323}{here}.

Analogously, use Rmarkdown to produce tables as usual:

\begin{verbatim}
if (!require("xtable")) install.packages("xtable")
\end{verbatim}

\begin{verbatim}
## Loading required package: xtable
\end{verbatim}

\begin{verbatim}
xt <- xtable(head(cars), caption = "A table", label = "tab:table")
print(xt, comment = FALSE)
\end{verbatim}

\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & speed & dist \\ 
  \hline
1 & 4.00 & 2.00 \\ 
  2 & 4.00 & 10.00 \\ 
  3 & 7.00 & 4.00 \\ 
  4 & 7.00 & 22.00 \\ 
  5 & 8.00 & 16.00 \\ 
  6 & 9.00 & 10.00 \\ 
   \hline
\end{tabular}
\caption{A table} 
\label{tab:table}
\end{table}

Referenced via \ref{tab:table}. You can also use the YAML option
\texttt{header-includes} to includes custom \LaTeX packages for tables
(keep in mind that \texttt{pandoc} uses \texttt{longtables} by default,
and it is hardcoded; some things may require including the package
\texttt{longtable}). E.g., using \texttt{ctable}:

\begin{verbatim}
header-includes:
- \usepackage{ctable}
\end{verbatim}

Then, just write straight-up \LaTeX code and reference is as usual
(\texttt{\textbackslash{}ref\{tab:ctable\}}):

\begin{verbatim}
\ctable[cap = {Short caption},
        caption = {A caption for this table.},
        label={tab:ctable},]
        {cc}
        {
        \tnote[$\ast$]{Footnote 1}
        \tnote[$\dagger$]{Other footnote}
        \tnote[b]{Mistakes are possible.}
        }{
        \FL
        COL 1\tmark[a] & COL 2\tmark[$\ast$]
        \ML
        6.92\tmark[$\dagger$] & 0.09781 \\
        6.93\tmark[$\dagger$] & 0.09901 \\
        97 & 2000
        \LL
}
\end{verbatim}

It is also possible to set the \texttt{YAML} option
\texttt{longtable:\ true} and use markdown tables (or the
\texttt{knitr::kable} function): \texttt{knitr::kable(head(cars))}
produces the same table as the \texttt{xtable} example presented before.

\hypertarget{cross-referencing}{%
\subsection{Cross-referencing}\label{cross-referencing}}

The use of the Rmarkdown equivalent of the \LaTeX cross-reference system
for figures, tables, equations, etc., is encouraged (using
\texttt{{[}@\textless{}name\textgreater{}{]}}, equivalent of
\texttt{\textbackslash{}ref\{\textless{}name\textgreater{}\}} and
\texttt{\textbackslash{}label\{\textless{}name\textgreater{}\}}). That
works well for citations in Rmarkdown, not so well for figures and
tables. In that case, it is possible to revert to standard
\LaTeX syntax.

\hypertarget{double-spacing}{%
\subsection{Double Spacing}\label{double-spacing}}

If you need to double space your document for submission please use the
\texttt{doublespace} option in the header.

\hypertarget{bibliography}{%
\section{Bibliography}\label{bibliography}}

Link a \texttt{.bib} document via the YAML header, and bibliography will
be printed at the very end (as usual). The default bibliography style is
provided by Wiley as in \texttt{WileyNJD-AMA.bst}, do not delete that
file.

Use the Rmarkdown equivalent of the \LaTeX citation system using
\texttt{{[}@\textless{}name\textgreater{}{]}}. Example:
\citep{Taylor1937}, \citep{Knupp1999, Kamm2000}.

To include all citation from the \texttt{.bib} file, add
\texttt{\textbackslash{}nocite\{*\}} before the end of the document.

\hypertarget{further-information}{%
\section{Further information}\label{further-information}}

All \LaTeX enviroments supported by the main template are supported here
as well; see the \texttt{.tex} sample file
\href{http://onlinelibrary.wiley.com/journal/10.1002/(ISSN)1097-0258/homepage/la_tex_class_file.htm}{here}
for more details and example.

\bibliographystyle{sageh}
\bibliography{bibfile}

\end{document}

### 2019-12-02 analysis/paper/paper.Rmd
a bit of intro

@@
 # Introduction
+
+Heritage is the processes and outcomes of people engaging with elements of the past – material and immaterial – and attributing social and cultural meanings to them in the present (Smith 2006; Harrison 2013).
+These are important to understand because they shape peoples' identidies and influence how they think and behave towards other people.
+Digital heritage are these engagements that are enabled by the Internet (Bonacchi and Krzyzanska 2019), leaving traces that can be identified and quantified using data science methods.
+Recent work on digital heritage has opened a new field of study.s
+
+• Represents a major turn from post- modernism, critical theory, & deeply qualitative, towards digital heritage ontologies, data-intensive ethnographies, role of heritage scholars
 

### 2020-05-21 analysis/paper/paper.Rmd
intro and background

--- 2019-06-30 analysis/paper/paper.Rmd
@@
 )
+
+# slides: https://drive.google.com/drive/u/1/folders/1TI7JpQHZpMFqxJvNwUPSJhoVCduarCcm
+# OSF: https://doi.org/10.17605/OSF.IO/AY27G 
+# Video: https://youtu.be/2sWpw8MIDDA 
 ```
@@
 # Introduction
+
+Heritage is the processes and outcomes of people engaging with elements of the past – material and immaterial – and attributing social and cultural meanings to them in the present (Smith 2006; Harrison 2013).
+These are important to understand because they shape peoples' identities and influence how they think and behave towards other people.
+Digital heritage are these engagements that are enabled by the Internet [@bonacchi2019digital], leaving traces that can be identified and quantified using data science methods.
+Digital heritage studies represent a major turn from traditional heritage studies, characterized by post-modernism [@kristiansen2014towards], critical theory, and qualitative methods, towards novel ontologies, data-intensive ethnographies, and a new role for heritage scholars as data scientists.
+Bonacchi et al.
+[-@Krzyzanska_2018; -@bonacchi2019digital] have sketched out the new digital heritage research program with their combination of data-intensive and qualitative investigations of 1.4m Facebook posts in Brexit-related community groups.
+They found recurring parallels – both pro- and anti-Brexit – made by Facebook users between the European Union, the Roman Empire and "barbarians" as they use heritage to support their political activism.
+They demonstrate the potential for understanding public perceptions and experiences of the past in contemporary society using big data obtained from social media.
+In this paper we extend the digital heritage research program in two important new directions.
+First, we introduce Wikipedia as an example of an online peer production community where people engage with elements of the past in measurable ways.
+Second, present a case study using data science methods to investigate the ways people create and consume Wikipedia articles on cultural sites inscribed on the UNESCO World Heritage List (hereafter CS-WHL).
+
+While social media is a vast and diverse online space that we are only just beginning to explore how people engage with the past, there are other contexts of online interactions where heritage is practiced in distinctive, if poorly understood, ways.
+We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with peer production communities, where online users participate in the collaborative, asynchronous creation, sharing, promoting, and classification of content in highly structured ways [@wilkinson2008strong].
+Online peer production communities are comparable to more traditions kinds of voluntary associations where groups set and execute goals, with explicitly democratic organizational ideals.
+While the ideals of many online peer production communities emphasize nonhierarchical and nonbureaucratic organization, analysis of large amounts of user activity indicates that most of these communities are actually undemocratic and noninclusive, functioning as entrenched oligarchies [@shaw2014laboratories].
+This emphasis on governance and management of collective action is a key detail that distinguishes online communities on social media from online communities on peer production projects.
+It follows that user interactions in the process of generating context in online peer production communities includes technological and social mechanisms that enact the community's governance policies, for example, limiting a user's activity according to their status in the community's hierarchy, or managing conflict with highly structured procedures.
+These distinctive organizational and technical qualities of online peer production communities make them an intriguing novel context of heritage production to study digital traces of human activity resulting from engagement with the past
+
+Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, Wikipedia, a highly influential (11 billion page views per month.
+https://stats.wikimedia.org/#/en.wikipedia.org) and well-known online encyclopedia that anyone can edit.
+Although anyone can edit, most internet users do not, and the characteristics of people who do edit are important to understand to identify biases in the encyclopedia's content.
+In a survey of 1,512 American adults, @shaw2018pipeline found that majority of internet users (96.5%) had heard of Wikipedia, and 82.5% of those said that they had ever visited the site.
+Just over two thirds (67.3%) knew that Wikipedia can be edited, but only 8.2% of the full sample had ever edited any page.
+Factors that strongly predict if a user has ever edited Wikipedia include their gender (male), age (younger), education level (has BA), Internet use frequency (higher) and Internet use skills (higher).
+@hill2013wikipedia a similarly found that among U.S.
+adult contributors to the English-language edition of Wikipedia, at least 75% are male.
+While gender disparities have been documented throughout Wikipedia [@adams2015wikipedia; @ford2017anyone], there are also geographical disparities.
+@johnson2016not examined 218,709 English geotagged articles about places in the
+contiguous United States and 46,124 Chinese geotagged articles about places in China to investigate differences in articles about urban and rural places.
+They found that articles about rural areas have systematically lower quality, are less likely to have been produced by contributors who focus on the local  area, and are more likely to have been generated by bots (automated software agents).
+
+The software that Wikipedia runs on, MediaWiki, is a complex toolkit that structures user behaviors in ways that are well suited to data science methods the enable efficient computational analysis of large numbers Wikipedia articles.
+While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity.
+The technical schemas of MediaWiki result in very specific types of relationships between human users and the technical elements of the Wikipedia project.
+For example, every edit to every article is tracked in a publicly accessible version control system.
+This exposes the article creation process in highly granular detail; we can see how many editors contributed, the size of their edits and their distribution over time.
+Wikipedia has a special category of edit called the 'revert' which allows a user to restore an article to an earlier state to remove recent vandalism (such as the addition of irrelevant or offensive material).
+
+Technicity: The efficacy, functionality, or experience of a particular technology.
+relationship between technology and humanity (or humans), Simondon‘s philosophy, technicity is undertaken as a result of the relationship among technical objects and humans.
+An incredible sociotechnical system of content production and maintenance with human and non-human actors: people, bots: https://www.makeuseof.com/tag/bots-edit-wikipedia-humans-made/  (eg.
+rambot) and “software-assisted human editors” https://journals.sagepub.com/doi/pdf/10.1177/1461444810365297 (good figs here)
+Editing mechanics (http://www.contropedia.net/ ), bots (fighting https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0171774 but see https://dl.acm.org/citation.cfm?id=3134684), reverts, Talk pages
+Conflict detection: https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0038869
+
+Specifically we investigate how people interact with Wikipedia articles about cultural sites inscribed on the WHL.
+We chose the CS-WHL as a bounded set of cultural heritage elements with near-global distribution, broad public interest, a wide temporal distribution in both the age of the cultural sites, and the age of inscription on the WHL, and the high intensity of cultural and political discussions that often surround the inscription of site on the WHL.
+These qualities make it an ideal data set as an entry point for digital heritage studies of online peer production communities, which are typically goal-driven (e.g.
+'write quality articles') compared to social media activity where activity is more event-driven analysis (e.g.
+'share reactions to Brexit').
+
+We survey the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics) to answer the question: how does engagement with the past compare on Wikipedia compare to engagement with other topics?
+We use a random sample of 10,000 Wikipedia articles as a random sample to compare with articles about cultural sites on the UNESCO World Heritage List.
+We investigate spatial patterns of behaviour on these Wikipedia articles to answer the question:  are the editors of CS-WHL located near the sites they edit, indicating local community interest in the online representation of their heritage, or in other countries, impling a digital colonalism of world heritage information on Wikipedia where one community's heritage is interpreted and communicated by another?
+Finally we investigate temporal patterns of activity on CS-WHL Wikipedia pages to answer the question of how correlated editing activity is with events outside of Wikipedia relating to the CS-WHL sites, such as their inscription on the WHL.
+
+In this paper we contribute to digital heritage studies into a new online domain
 
@@
 
+Kristiansen, K. 2014. “Towards a New Paradigm? the Third Science Revolution and Its Possible Consequences in Archaeology.” Current Swedish Archaeology 22: 11–34.
+
 ##### pagebreak

### 2020-05-21 analysis/paper/paper.Rmd
more background

@@
 ---
-title: "Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia"
+title: "World Heritage Sites on Wikipedia: Inscription Controversies in a Context of Constrained Agency for Cultural Heritage Activism"
 author:
@@
 abstract: |
-  Text of abstract
+  UNESCO World Heritage sites are places of outstanding significance, and often key sources of information that influence how people interact with the past today.
+The process of inscription on the UNESCO list is complicated and intersects with political and commercial controversies.
+But how well are these controversies known to the public?
+Wikipedia pages on these sites offer a unique dataset for insights into public understanding of heritage controversies.
+The unique technicity of Wikipedia, with its bot ecosystem and editing mechanics, shapes how knowledge about cultural heritage is constructed, and how controversies are negotiated and communicated.
+In this article we investigate the patterns of production, consumption and spatial and temporal distributions of Wikipedia pages for World Heritage cultural sites.
+We find that Wikipedia provides a distinctive context for investigating how people experience and relate to the past in the present.
+The agency of participants is highly constrained, but distinctive, behind-the-scenes expressions of cultural heritage activism are evident.
+Concerns about state-like actors, violence and destruction, deal-making, etc.
+in the World Heritage inscription process are poorly represented on Wikipedia’s World Heritage pages, instead hyper-local, and process issues dominate controversies on Wikipedia.
+We will consider how this kind of research, drawing on big data and data science methods, adds new dimensions to the debate on heritage controversies, especially its unique contributions, and also its limitations.
 ---
@@
 While social media is a vast and diverse online space that we are only just beginning to explore how people engage with the past, there are other contexts of online interactions where heritage is practiced in distinctive, if poorly understood, ways.
-We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with peer production communities, where online users participate in the collaborative, asynchronous creation, sharing, promoting, and classification of content in highly structured ways [@wilkinson2008strong].
+We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with peer production communities, where online users participate in the collaborative, asynchronous creation, sharing, promoting, and classification of content in highly structured and goal-directed ways [@wilkinson2008strong].
 Online peer production communities are comparable to more traditions kinds of voluntary associations where groups set and execute goals, with explicitly democratic organizational ideals.
-While the ideals of many online peer production communities emphasize nonhierarchical and nonbureaucratic organization, analysis of large amounts of user activity indicates that most of these communities are actually undemocratic and noninclusive, functioning as entrenched oligarchies [@shaw2014laboratories].
+While the ideals of many online peer production communities emphasize non-hierarchical and non-bureaucratic organization, analysis of large amounts of user activity indicates that most of these communities are actually undemocratic and noninclusive, functioning as entrenched oligarchies [@shaw2014laboratories].
 This emphasis on governance and management of collective action is a key detail that distinguishes online communities on social media from online communities on peer production projects.
@@
 
-Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, Wikipedia, a highly influential (11 billion page views per month.
-https://stats.wikimedia.org/#/en.wikipedia.org) and well-known online encyclopedia that anyone can edit.
+Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, Wikipedia.
+This is a highly influential, with 11 billion page views per month (https://stats.wikimedia.org/#/en.wikipedia.org), and well-known online encyclopedia that anyone can edit.
 Although anyone can edit, most internet users do not, and the characteristics of people who do edit are important to understand to identify biases in the encyclopedia's content.
@@
 While gender disparities have been documented throughout Wikipedia [@adams2015wikipedia; @ford2017anyone], there are also geographical disparities.
-@johnson2016not examined 218,709 English geotagged articles about places in the
-contiguous United States and 46,124 Chinese geotagged articles about places in China to investigate differences in articles about urban and rural places.
+@johnson2016not examined 218,709 English geotagged articles about places in the contiguous United States and 46,124 Chinese geotagged articles about places in China to investigate differences in articles about urban and rural places.
 They found that articles about rural areas have systematically lower quality, are less likely to have been produced by contributors who focus on the local  area, and are more likely to have been generated by bots (automated software agents).
+These studies indicate that inequalities on a range of variables mean that participation in online peer production communities often exacerbates existing patterns of social exclusion.
 
-The software that Wikipedia runs on, MediaWiki, is a complex toolkit that structures user behaviors in ways that are well suited to data science methods the enable efficient computational analysis of large numbers Wikipedia articles.
-While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity.
-The technical schemas of MediaWiki result in very specific types of relationships between human users and the technical elements of the Wikipedia project.
-For example, every edit to every article is tracked in a publicly accessible version control system.
-This exposes the article creation process in highly granular detail; we can see how many editors contributed, the size of their edits and their distribution over time.
+An additional consideration for understanding participation in online peer production communities are the technical schemas of the software that Wikipedia runs on, MediaWiki.
+This is a complex toolkit that enables participation in Wikipedia in highly structured ways.
+On one hand, these structured behaviours produce structured datasets that are well suited to data science methods for efficient computational analysis of large numbers Wikipedia articles.
+On the other hand, they constrain and limit the agency of the user, canalizing their behaviour into a small number of possible actions and acceptable modes of discourse and engagement with other users [@iba2010analyzing].
+While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity, resulting in very specific types of relationships between human users and the technical elements of the Wikipedia project [@niederer2010wisdom].
+For example, every edit to an article is tracked in a publicly accessible version control system attached to that article.
+This exposes the article creation process in highly granular detail; for any given article, we can see how many editors contributed, the size of their edits and their distribution over time, among other things [@priedhorsky2007creating].
 Wikipedia has a special category of edit called the 'revert' which allows a user to restore an article to an earlier state to remove recent vandalism (such as the addition of irrelevant or offensive material).
+This special revert action, combined with a 'talk' page attached to each encyclopedia article for threaded discussion among editors, allows us to detect and study the dynamics of conflicts arising from the creation and editing of articles [@suh2007us].
+For example, a high proportion of 'revert' type edits, and a high word count on the talk page can indicate the controversiality of an article [@yasseri2012dynamics].
 
-Technicity: The efficacy, functionality, or experience of a particular technology.
-relationship between technology and humanity (or humans), Simondon‘s philosophy, technicity is undertaken as a result of the relationship among technical objects and humans.
+In addition to the human users and the technological system that enables and constrains their activities on Wikipedia, there is an important third element of the ecosystem that contributes to Wikipedia's uniqeness: the bots.
+While bots are not unique to Wikipedia, they are important contributors, responsible for a large proportion of edits, and shape the human experience in signficant ways [@niederer2010wisdom' @geiger2009social].
+Wikipedia bots are computer scripts that automatically handle repetitive and mundane tasks to develop, improve, and maintain the encyclopedia.
+@zheng2019roles
+
+@tsvetkova2017even  @geiger2017operationalizing
+
 An incredible sociotechnical system of content production and maintenance with human and non-human actors: people, bots: https://www.makeuseof.com/tag/bots-edit-wikipedia-humans-made/  (eg.
 rambot) and “software-assisted human editors” https://journals.sagepub.com/doi/pdf/10.1177/1461444810365297 (good figs here)
-Editing mechanics (http://www.contropedia.net/ ), bots (fighting https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0171774 but see https://dl.acm.org/citation.cfm?id=3134684), reverts, Talk pages
-Conflict detection: https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0038869
+Editing mechanics (http://www.contropedia.net/ ), bots (fighting https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0171774 but see https://dl.acm.org/citation.cfm?id=3134684),
 
@@
 
+# Methods
+
 We survey the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics) to answer the question: how does engagement with the past compare on Wikipedia compare to engagement with other topics?
@@
 In this paper we contribute to digital heritage studies into a new online domain
-
-# Background
-
-# Methods
 

### 2020-05-24 analysis/paper/999-code-for-the-Stirling-ppt.Rmd
more writing abotu WHL

---
title: "Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia"
---

## Load the data

```{r}
library(tidyverse)

# load the random pages
ten_k_random_wp_pages <- readRDS(here::here("data", "random_page_data_tbl.rds"))

# load the random pages revision histories
ten_k_random_wp_pages_lst <- readRDS(here::here("data", "random_page_data_lst.rds"))

# all WH sites with WP pages (n = 584)
page_data_for_all_pages <-
  readRDS(here::here("data",
                     "page_data_for_all_pages.rds"))

# all WH sites, with and without WP pages (n = 846)
wh_wiki_table <-
  read_csv(here::here("data",
                      "wh_wiki_table.csv"))

# the talk pages for all WH sites, with WP pages (n = 846)
wh_wiki_talk_pages <-  readRDS(here::here("data",
                     "wh_wiki_table_talk_page_content.rds"))

# all WH sites according to UNESCO
# from https://whc.unesco.org/en/syndication
wh_unesco <- readxl::read_excel(here::here("data",
                                           "whc-sites-2018.xls")) %>%
  filter(category %in% c("Cultural"))

library("rnaturalearth")
library("rnaturalearthdata")
world <- ne_countries(scale = "medium", returnclass = "sf")

# functions used more than once:

estimate_mode <- function(x) {
  d <- density(x)
  d$x[which.max(d$y)]
}

theme_nogrid <- function (base_size = 12, base_family = "") {
  theme_bw(base_size = base_size,
           base_family = base_family) %+replace%
    theme(panel.grid = element_blank() )   
}
```

## Overall clusters

```{r}
normalize = function(x) (x-min(x))/(max(x)-min(x))

#--------------------------------------------------------------------------
# take a look at the distribution of page variables
some_page_variables <-
  page_data_for_all_pages %>%
  select(page_wordcount,
         page_wikilinks_out,
         page_wikilinks_in,
         page_cited_items_on) %>%
  mutate(page_wikilinks_out_per_word = page_wikilinks_out / page_wordcount,
         page_cited_items_on_per_word = page_cited_items_on / page_wordcount)

# umap
library(uwot)
library("tmap")
data("World")

pages_umap_input <-
  some_page_variables  %>%
  mutate(page_wordcount_norm = normalize(page_wordcount),
         page_wikilinks_in_norm= normalize(page_wikilinks_in),
         page_wikilinks_out_per_word_norm = normalize(page_wikilinks_out_per_word),
         page_cited_items_on_per_word_norm = normalize(page_cited_items_on_per_word)) %>%
  select(-page_wordcount,
         -page_cited_items_on,
         -page_wikilinks_out,
         -page_wikilinks_in,
         -page_wikilinks_out_per_word,
         -page_cited_items_on_per_word) %>%
  bind_cols(., page_data_for_all_pages[ , 'country'] ) %>%
  filter_all(all_vars(!is.na(.))) %>%
  left_join(World %>%
              select(name, continent),
            by = c('country' = 'name'))

# compute umap

pages_umap_input_selected <-
  pages_umap_input %>%
  select(-country,
         -continent,
         -geometry
         )

pages_umap_output <-
  pages_umap_input_selected %>%
  umap(.,
       n_neighbors = 60,
       min_dist = 0.7,
       nn_method = "annoy",
       init = "spca") %>%
  as_tibble()

# compute hdbscan clusters
library(dbscan)
hdbscan_out <- hdbscan(pages_umap_output,
                       minPts = 5)

table(hdbscan_out$cluster)

main_plot <-
ggplot(pages_umap_output,
       aes(V1, V2)) +
  geom_point(
    aes(colour = factor(hdbscan_out$cluster),
        size =  pages_umap_input_selected$page_wordcount_norm  ,
        shape = pages_umap_input$continent
        )) +
  scale_size(range = c(2,7), guide = FALSE) +
  scale_shape(name = "Continent") +
  scale_color_viridis_d(guide = FALSE) +
  theme_minimal() +
  theme(legend.position = c(0.1, 0.8)) +
  xlab("") +
  ylab("")

# train a feature-selecting classificator like random forests on
# the cluster labels

rand_forest_input <-
  pages_umap_input_selected %>%
  mutate(clus = hdbscan_out$cluster) %>%
  filter(clus != 0)

library(caret)

fit <- train(
  clus ~ .,
  data = rand_forest_input,
  method = "ranger",
  trControl = trainControl(method="cv",
                            number = 10,
                            allowParallel = TRUE,
                            verbose = TRUE),
  importance = 'permutation')

fit
var_imp_tbl <- tibble(var = row.names(varImp(fit)$importance),
                      imp = varImp(fit)$importance$Overall)

theme_nogrid <- function (base_size = 12, base_family = "") {
  theme_bw(base_size = base_size,
           base_family = base_family) %+replace%
    theme(panel.grid = element_blank() )   
}

sub_plot <-
ggplot(var_imp_tbl,
       aes(reorder( var, -imp ),
           imp)) +
  geom_col() +
  coord_flip() +
  xlab("") +
  ylab("") +
  theme_nogrid(base_size = 6)

# plot plus subplot
main_plot +
  annotation_custom(ggplotGrob(sub_plot),
                    xmin = 3,
                    xmax = 6,
                    ymin= 6.5,
                    ymax= 3.5)

ggsave("figures/wh_country_umap_hdbscan.png")
```

## Representation by country

Where are the WH sites, before looking into WP

```{r}

wh_unesco_countries <-
wh_unesco %>%
  separate_rows(states_name_en, convert = TRUE, sep = ",") %>%
  mutate(country = case_when(
    states_name_en == "Bolivia (Plurinational State of)"  ~ "Bolivia",
    states_name_en == "Cabo Verde"  ~ "Republic of Cabo Verde",
    states_name_en == "Czechia"  ~ "Czech Republic",
    states_name_en == "Democratic People's Republic of Korea"  ~ "Republic of Korea",
    states_name_en == "Gambia (the)"  ~ "The Gambia",
    states_name_en == "Holy See"  ~ "Vatican",
    states_name_en == "Iran (Islamic Republic of)"  ~ "Iran",
    states_name_en == "Lao People's Democratic Republic"  ~ "Lao PDR",
    states_name_en == "Micronesia (Federated States of)"  ~ "Federated States of Micronesia",
    states_name_en == "Syrian Arab Republic"  ~ "Syria",
    states_name_en == "the former Yugoslav Republic of Macedonia"  ~ "Macedonia",
    states_name_en == "United Kingdom of Great Britain and Northern Ireland"  ~ "United Kingdom",
    states_name_en == "United Republic of Tanzania"  ~ "Tanzania",
    states_name_en == "United States of America"  ~ "United States",
    states_name_en == "Venezuela (Bolivarian Republic of)"  ~ "Venezuela",
    states_name_en == "United States of America"  ~ "United States",
    states_name_en == "Viet Nam"  ~ "Vietnam",
    states_name_en == "Republic of Moldova"  ~ "Moldova",
    TRUE ~ as.character(states_name_en)
  ))

wh_unesco_countries_count <-  
  wh_unesco_countries %>%
  count(country)

median_number_unesco_sites_per_country <-
  median(wh_unesco_countries_count$n)

mode_number_unesco_sites_per_country <-
  round(estimate_mode(wh_unesco_countries_count$n), 1)

wh_unesco_country_counts_hist <-
ggplot(wh_unesco_countries_count,
       aes(n)) +
  geom_histogram() +
  annotate("text", x = 30, y = 30,
           label = str_glue('Median =\n{median_number_unesco_sites_per_country} WH sites/country\nMode =\n{mode_number_unesco_sites_per_country} WH sites/country'),
           size = 3) +
  theme_nogrid(8)

sf_map_data_unesco <-
world %>%
  left_join(wh_unesco_countries_count,
            by = c( 'name_long' = 'country')) %>%
  select(name, n, geometry) %>%
  mutate(n = ifelse(is.na(n), 0, n)) %>%
  filter(name != "Antartica")

wh_country_unesco_count_map <-
ggplot(data = sf_map_data_unesco) +
    geom_sf(aes(fill = n), lwd = 0) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  theme_minimal() +
  ggtitle("Cultural Sites on the UNESCO World Heritage list",
          subtitle = "from https://whc.unesco.org/en/syndication")

wh_country_unesco_count_map +
  annotation_custom(ggplotGrob(wh_unesco_country_counts_hist),
                    xmin = -190,
                    xmax = -90,
                    ymin= 10,
                    ymax=-70)

ggsave("figures/wh_country_unesco_count_map.png")

```

What countries are most represented?

```{r}
  # get country of site from location text
  # Laos, Czech Republic, Micronesia, Zimbabwe, South Sudan, Chad,
  # Central African Republic, Congo, Gabon, Cameroon, Nigeria, Bosnia and Herzegovina
  #  Cote d'Ivoire, Sierra Leone, Guyana, Belize,
  country_names <-  paste(c(world$name,
                            "United States",
                            "Czech Republic",
                             "Antigua & Barbuda",
                            "Saint Kitts and Nevis"
                            ),
                          collapse="|")

  page_data_for_all_pages_location <-
    page_data_for_all_pages %>%
    mutate(country = str_extract(Location,
                                 regex(country_names,
                                       ignore.case=TRUE))) %>%
    mutate(country = case_when(
      country == "United States" ~ "United States of America",
      country == "Czech Republic" ~ "Czechia",
      country == "Antigua & Barbuda" ~ "Antigua and Barb.",
      country == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
      TRUE ~ as.character(country)))

wh_wiki_table_location <-
  wh_wiki_table %>%
  mutate(country = str_extract(Location,
                                 regex(country_names,
                                       ignore.case=TRUE))) %>%
    mutate(country = case_when(
      country == "United States" ~ "United States of America",
      country == "Czech Republic" ~ "Czechia",
      country == "Antigua & Barbuda" ~ "Antigua and Barb.",
      country == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
      TRUE ~ as.character(country)))

```

## More maps

```{r}

wh_wk_country_counts <-
page_data_for_all_pages_location %>%
  count(country) %>%
  filter(!is.na(country))

theme_nogrid <- function (base_size = 12, base_family = "") {
  theme_bw(base_size = base_size,
           base_family = base_family) %+replace%
    theme(panel.grid = element_blank() )   
}

median_number_wp_pages_per_country <-
  median(wh_wk_country_counts$n)

estimate_mode <- function(x) {
  d <- density(x)
  d$x[which.max(d$y)]
}

mode_number_wp_pages_per_country <-
  round(estimate_mode(wh_wk_country_counts$n), 1)

wh_wk_country_counts_hist <-
ggplot(wh_wk_country_counts,
       aes(n)) +
  geom_histogram() +
  annotate("text", x = 15, y = 30,
           label = str_glue('Median = {median_number_wp_pages_per_country} WP pages/country\nMode = {mode_number_wp_pages_per_country} WP pages/country'),
           size = 2) +
  theme_nogrid(12)

wh_wk_country_counts_bar <-
ggplot(wh_wk_country_counts,
       aes(reorder(country, n),
           n)) +
  geom_col() +
  coord_flip() +
  theme_minimal(base_size = 6) +
  xlab("")
```

## Here's a map of countries showing which has the most WP pages for WH sites

```{r}
sf_map_data <-
world %>%
  left_join(wh_wk_country_counts,
            by = c( 'name' = 'country')) %>%
  select(name, n, geometry) %>%
  mutate(n = ifelse(is.na(n), 0, n)) %>%
  filter(name != "Antartica")

wh_wk_country_count_map <-
ggplot(data = sf_map_data) +
    geom_sf(aes(fill = n), lwd = 0) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  theme_minimal() +
  ggtitle("Cultural Sites on the UNESCO World Heritage list with Wikipedia pages",
          subtitle = str_glue("The top five are {wh_wk_country_counts %>%
                                                  arrange(-n) %>%
                                                  slice(1:5) %>%
                                                  pull(country) %>%
                                                  str_flatten(collapse = ', ')}"))

wh_wk_country_count_map +
  annotation_custom(ggplotGrob(wh_wk_country_counts_hist),
                    xmin = -190,
                    xmax = -90,
                    ymin= 10,
                    ymax=-70)

ggsave("figures/wh_country_wikpedia_pages_count_map.png")
```

## Map of the ratio of WH sites with WP pages, per country

```{r}
wh_wiki_table_location_prop <-
wh_wiki_table_location %>%
  mutate(has_wp_page = ifelse(!is.na(site_page_name), 1, 0)) %>%
  group_by(country) %>%
  summarise(prop_sites_with_pages = sum(has_wp_page) / n()) %>%
  filter(!is.na(country))

wh_wk_country_prop_hist <-
ggplot(wh_wiki_table_location_prop,
       aes(prop_sites_with_pages)) +
  geom_histogram() +
  theme_nogrid(10)

wh_wk_country_all_counts <-
wh_wiki_table_location %>%
  count(country) %>%
  filter(!is.na(country)) %>%
  left_join(wh_wiki_table_location_prop)

wh_wk_country_prop_scatter <-
ggplot(wh_wk_country_all_counts,
       aes(prop_sites_with_pages, n)) +
  geom_point(alpha = 0.5) +
  coord_fixed(0.02) +
  theme_nogrid(6)

wh_wk_country_prop_scatter_marginal <-
ggExtra::ggMarginal(wh_wk_country_prop_scatter,
                    type = "histogram")

sf_map_data_prop <-
world %>%
  filter(name != "Antartica") %>%
  left_join(wh_wiki_table_location_prop,
            by = c( 'name' = 'country')) %>%
  select(name,
         prop_sites_with_pages,
         geometry)  %>%
  mutate(prop_sites_with_pages = ifelse(is.na(prop_sites_with_pages), 0, prop_sites_with_pages))

wh_wk_country_prop_map <-
ggplot(data = sf_map_data_prop) +
    geom_sf(aes(fill = prop_sites_with_pages), lwd = 0) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf(ylim = c(-50, 90), datum = NA) +
  theme_minimal() +
  ggtitle("Ratio of number of Cultural Sites on the UNESCO World Heritage list\nto the number of those sites with Wikipedia pages")

wh_wk_country_prop_map +
  annotation_custom((wh_wk_country_prop_scatter_marginal),
                    xmin = -190,
                    xmax = -90,
                    ymin= 10,
                    ymax=-70)

ggsave("figures/wh_country_wikpedia_pages_ratio_map.png")
```

## Basic qualities of the content of WP articles about WH sites

```{r}
ten_k_random_wp_pages_basic_qualities <-
ten_k_random_wp_pages %>%
  select(page_wordcount,
         page_wikilinks_out,
         page_cited_items_on) %>%
  mutate(rnd_page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
         rnd_page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000,
         rnd_page_wordcount = page_wordcount) %>%
  select(-page_wikilinks_out,
         -page_cited_items_on,
         -page_wordcount)

ten_k_random_wp_pages_basic_qualities_long <-
  ten_k_random_wp_pages_basic_qualities %>%
  gather(variable, value)
```

Length: correlate with ??
number of links out/word
number of references/word: scholarly or not

```{r}
page_data_for_all_pages_basic_qualities <-
page_data_for_all_pages %>%
  select(page_wordcount,
         page_wikilinks_out,
         page_cited_items_on) %>%
  mutate(page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
         page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000) %>%
  select(-page_wikilinks_out,
         -page_cited_items_on)

page_data_for_all_pages_basic_qualities_long <-
page_data_for_all_pages_basic_qualities %>%
  gather(variable, value) %>%
  bind_rows(ten_k_random_wp_pages_basic_qualities_long) %>%
  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages", "World Heritage pages")) %>%
  mutate(variable = str_remove(variable, "rnd_"))

label_names <- list(
  "page_wordcount"="Page word count",
  "page_wikilinks_out_per_1k_words"="Number of wikilinks\nper 1k words",
  "page_cited_items_on_per_1k_words"="Number of sources cited\nper 1k words"
)

labeller <- function(variable,value){
  return(label_names[value])
}

# density plots
  ggplot(page_data_for_all_pages_basic_qualities_long,
         aes(value)) +
  geom_density(aes(fill = source),
               alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d() +
  facet_wrap( ~ variable,
              scales = "free",
              labeller = labeller) +
  theme_minimal() +
    ggtitle("Basic qualities about Wikipedia article content")

  ggsave("figures/wh_wikpedia_pages_basic_content.png")
```

# basic qualities scatterplot

```{r}
# scatterplots
  ggplot() +
      geom_point(data = ten_k_random_wp_pages_basic_qualities,
             aes(rnd_page_wikilinks_out_per_1k_words,
                 rnd_page_cited_items_on_per_1k_words,
                 size = rnd_page_wordcount),
             colour = "grey80",
             alpha = 0.4) +
  geom_point(data = page_data_for_all_pages_basic_qualities,
             aes(page_wikilinks_out_per_1k_words,
                 page_cited_items_on_per_1k_words,
                 size = page_wordcount),
             colour = "red",
             alpha = 0.8) +
  scale_x_log10() +
  scale_y_log10() +
  scale_fill_viridis_d() +
  coord_fixed() +
  theme_minimal()

```

## Basic qualities of the consumption of WP articles about WH sites

number of links in
page_views_last_n_days_total

```{r}
library(ggrepel)
ten_k_random_wp_pages_attent <-
ten_k_random_wp_pages %>%
  select(page_wikilinks_in,
         page_views_last_n_days_total)

page_data_for_all_pages_attent <-
page_data_for_all_pages %>%
  select(page_wikilinks_in,
         page_views_last_n_days_total)

page_data_for_all_pages_attent_long <-
page_data_for_all_pages_attent %>%
  gather(variable, value) %>%
  bind_rows(ten_k_random_wp_pages_attent %>%
              gather(variable, value) %>%
              mutate(variable =  str_glue('rnd_{variable}'))) %>%
  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages",
                         "World Heritage pages")) %>%
  mutate(variable = str_remove(variable, "rnd_"))

# density plots

label_names <- list(
  "page_wikilinks_in"="Number of wikilinks to the page",
  "page_views_last_n_days_total"="Total page views\n(last 100 days)"
)

labeller <- function(variable,value){
  return(label_names[value])
}

  ggplot(page_data_for_all_pages_attent_long,
         aes(value)) +
  geom_density(aes(fill = source),
               alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d() +
  facet_wrap( ~ variable,
              scales = "free",
              labeller = labeller) +
  theme_minimal() +
    ggtitle("Basic qualities about consumption of Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_consumption.png")
```

## Scatterplot showing the WP sites that get the most attention

```{r}
library(ggrepel)
page_data_for_all_pages %>%
  select( Site,
          page_wordcount,
         page_wikilinks_in,
         page_views_last_n_days_total)  %>%
  ggplot(aes(page_wikilinks_in,
             page_views_last_n_days_total,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size = page_wordcount,
                 colour = page_wordcount)) +
    geom_text_repel(
    data          = page_data_for_all_pages %>%  
                      filter(page_views_last_n_days_total > 190000),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10(expand = c(1, 0.05)) +
  scale_x_log10(limits = c(1, 10000)) +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Wordcount",
                        labels = c(20000, 15000, 10000, 5000),
                        breaks = c(20000, 15000, 10000, 5000)) +
  scale_size_continuous(name = "Wordcount",
                        labels = c(20000, 15000, 10000, 5000),
                        breaks = c(20000, 15000, 10000, 5000)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of wikilinks to the page",
       y = "Total page views (last 100 days)") +
    ggtitle("Basic qualities about the consumption of Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_consumption_scatterplot.png")
```

## Basic qualities of the editing process of WP articles about WH sites

number of edits, total, edit density (prop/words), size of edits
how many bot edits, how many reverts per page
diversity of editors

```{r}
# wh sites on wp
revision_history_page_details <-
  tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t,
      ~.x$revision_history_page_details)) %>%
  mutate(Site =         page_data_for_all_pages$Site,
         Country =      page_data_for_all_pages$country,
         rh_n_editors = map_int(revision_history_page_details, ~n_distinct(.x$rh_user)),
         rh_n_edits =   map_int(revision_history_page_details, ~nrow(.x)),
         rh_user_simpson_idx = page_data_for_all_pages$rh_user_simpson_idx,
         rh_user_bot_prop = page_data_for_all_pages$rh_user_bot_prop,
         rh_revert_prop = page_data_for_all_pages$rh_revert_prop)

# random sites

ten_k_random_wp_pages_revision_history_page_details <-
  map_df(ten_k_random_wp_pages_lst,
         ~.x$revision_history_page_details,
         .id = 'Site')

# very slow!
ten_k_random_wp_pages_revision_history_page_details_summary_tbl <-
  ten_k_random_wp_pages_revision_history_page_details %>%
  mutate(Site = as.numeric(Site)) %>%
  group_by(Site) %>%
  summarise(
         rh_n_editors = n_distinct(rh_user),
         rh_n_edits =   n(),
         rh_n_bot_edits = sum(bot),
         rh_n_reverts = sum(revert)) %>%
  mutate(rh_revert_prop = rh_n_reverts / rh_n_edits,
         rh_bot_edits_prop = rh_n_bot_edits / rh_n_edits)

# plot both samples, number of edits per page
bind_rows(revision_history_page_details %>%
            select(Site, rh_n_edits) %>%
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl %>%
            select(Site, rh_n_edits) %>%
            mutate(Site = "rand")) %>%
  ggplot(aes(rh_n_edits,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Number of edits per page",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_edits_per_page.png")
```

## Edits per 1k words, as a measure of edit density

```{r}
revision_history_page_details_wordcount <-
  revision_history_page_details %>%
  bind_cols(page_data_for_all_pages %>% select(page_wordcount)) %>%
  mutate(edits_per_1k_words = rh_n_edits / (page_wordcount / 1000))

ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets <-
bind_cols(ten_k_random_wp_pages,
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl) %>%
  mutate(edits_per_1k_words = rh_n_edits / (page_wordcount / 1000))

bind_rows(revision_history_page_details_wordcount %>%
            select(Site, edits_per_1k_words) %>%
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets %>%
            select(Site, edits_per_1k_words) %>%
            mutate(Site = "rand")) %>%
  ggplot(aes(edits_per_1k_words,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  #xlim(0, 100) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Number of edits per 1k words per page",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_edits_density_page.png")
```

## Number of unique editors per page

```{r}
# plot both samples, number of edits per page
bind_rows(revision_history_page_details %>%
            select(Site, rh_n_editors) %>%
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl %>%
            select(Site, rh_n_editors) %>%
            mutate(Site = "rand")) %>%
  ggplot(aes(rh_n_editors,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Number of editors per page",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_editors_per_page.png")
```

## Number of unique editors per 1k words per page

```{r}
revision_history_page_details_wordcount <-
  revision_history_page_details %>%
  bind_cols(page_data_for_all_pages %>% select(page_wordcount)) %>%
  mutate(editors_per_1k_words = rh_n_editors / (page_wordcount / 1000))

ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets <-
bind_cols(ten_k_random_wp_pages,
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl) %>%
  mutate(editors_per_1k_words = rh_n_editors / (page_wordcount / 1000))

bind_rows(revision_history_page_details_wordcount %>%
            select(Site, editors_per_1k_words) %>%
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets %>%
            select(Site, editors_per_1k_words) %>%
            mutate(Site = "rand")) %>%
  ggplot(aes(editors_per_1k_words,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Number of editors per 1k words per page",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_editors_density_page.png")
```

## Size of edits, absolute and raw

```{r}
page_data_for_all_pages_rh_tbl <-
map_df(page_data_for_all_pages$page_info_t,
      ~.x$revision_history_page_details, .id = "Site")

label_names <- list(
  "mean_abs_diff"="Absolute edit sizes",
  "mean_diff"="Raw edit sizes"
)

labeller <- function(variable,value){
  return(label_names[value])
}

bind_rows(page_data_for_all_pages_rh_tbl %>%
            select(Site, rh_diff_size) %>%
            group_by(Site) %>%
            summarise(mean_diff = mean((rh_diff_size)),
                      mean_abs_diff = mean(abs(rh_diff_size))) %>%
            mutate(Site = "wh"),
          ten_k_random_wp_pages_revision_history_page_details %>%
            select(Site, rh_diff_size) %>%
              group_by(Site) %>%
            summarise(mean_diff = mean((rh_diff_size)),
                      mean_abs_diff = mean(abs(rh_diff_size))) %>%
            mutate(Site = "rand")) %>%
  gather(variable, value, -Site) %>%
  ggplot(aes(value,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  #xlim(0, 100) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Average size of edits per article (bytes)",
       fill = "Wikipedia pages") +
  facet_wrap( ~ variable, labeller = labeller) +
  theme_minimal()

ggsave("figures/wh_wikpedia_edit_sizes.png")
```

## How many edits made by bots? Proportion of edits per page made by bots

```{r}
bind_rows(

page_data_for_all_pages_rh_tbl %>%
  group_by(Site) %>%
  summarise( n_bot_edits = sum(bot),
             n_edits = n()) %>%
  mutate(prop_bot_edits = n_bot_edits / n_edits,
           Site = "wh"),

ten_k_random_wp_pages_revision_history_page_details %>%  
  group_by(Site) %>%
summarise( n_bot_edits = sum(bot),
           n_edits = n()) %>%
  mutate(prop_bot_edits = n_bot_edits / n_edits,
         Site = "rand")
) %>%

  ggplot(aes(prop_bot_edits,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  #xlim(0, 100) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Proportion of edits made by bots per article",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_edits_by_bots.png")
```

## Which WH pages are most edited by bots?

```{r}
library(ggrepel)

wh_bots <-
 tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t,
      ~.x$revision_history_page_details))  %>%
  mutate(Site = page_data_for_all_pages$Site) %>%
  mutate(n_bot_edits = map_dbl(revision_history_page_details, ~sum(.x$bot)),
         n_edits = map_int(revision_history_page_details, ~nrow(.))) %>%
  mutate(prop_bot_edits = n_bot_edits / n_edits) %>%
  arrange(desc(prop_bot_edits))

  ggplot(wh_bots,
         aes(n_bot_edits,
             n_edits,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size =   prop_bot_edits,
                 colour = prop_bot_edits)) +
    geom_text_repel(
    data            = wh_bots %>%  
                      filter(prop_bot_edits > 0.36),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\nedits by bots",
                        labels = c(0, 0.1, 0.2, 0.3, 0.4),
                        breaks = c(0, 0.1, 0.2, 0.3, 0.4)) +
  scale_size_continuous(name = "Proportion of\nedits by bots",
                        labels = c(0, 0.1, 0.2, 0.3, 0.4),
                        breaks = c(0, 0.1, 0.2, 0.3, 0.4)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits by bots",
       y = "Total number of edits") +
    ggtitle("Bot activity on Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_bot_edits_scatterplot.png")
```

## which bots are most active on WH pages vs random pages?
Cydebot: category edits
Smackbot: dates in templates
ClueBot NG: vandalism

```{r}
bind_rows(
page_data_for_all_pages_rh_tbl %>%
  filter(bot == 1) %>%
  group_by(rh_user) %>%
  tally(sort = TRUE) %>%
  slice(1:10) %>%
  mutate( Site = "World Heritage Sites"),

ten_k_random_wp_pages_revision_history_page_details %>%
  filter(bot == 1) %>%
  group_by(rh_user) %>%
  tally(sort = TRUE) %>%
    slice(1:10) %>%
   mutate( Site = "Random pages")) %>%

  ggplot(aes(reorder(rh_user, n),
             n)) +
  geom_col() +
  theme_minimal() +
  coord_flip() +
  facet_wrap( ~ Site, scales = "free") +
  xlab("")

ggsave("figures/wh_wikpedia_what_bots.png")
```

## So about vandalism? do WH sites get more than random ones?

```{r}
bind_rows(
page_data_for_all_pages_rh_tbl %>%
  mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
  group_by(Site) %>%
  summarise( n_vandal_edits = sum(vandalism),
             n_edits = n()) %>%
  mutate(prop_vandal_edits = n_vandal_edits / n_edits,
           Site = "World Heritage Sites"),

ten_k_random_wp_pages_revision_history_page_details %>%
  mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
  group_by(Site) %>%
  summarise( n_vandal_edits = sum(vandalism),
             n_edits = n()) %>%
  mutate(prop_vandal_edits = n_vandal_edits / n_edits,
         Site = "Random pages")
) %>%

   ggplot(aes(prop_vandal_edits,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Proportion of edits relating to vandalism per article",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_vandalism_edits.png")

```

## Which WH pages have the most vandalism?

```{r}

vandal_edits <-
 tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t,
      ~.x$revision_history_page_details))  %>%
  mutate(Site = page_data_for_all_pages$Site) %>%
  mutate(n_vandal_edits = map_dbl(revision_history_page_details,
                                  ~sum(ifelse(str_detect(.x$rh_comment, "vandalism"), 1, 0))),
         n_edits = map_int(revision_history_page_details, ~nrow(.))) %>%
  mutate(prop_vandal_edits = n_vandal_edits / n_edits) %>%
  arrange(desc(prop_vandal_edits))

ggplot(vandal_edits,
         aes(n_vandal_edits,
             n_edits,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.2,
             aes(size =   prop_vandal_edits,
                 colour = prop_vandal_edits)) +
    geom_text_repel(
    data            = vandal_edits %>%  
                      filter(prop_vandal_edits > 0.05),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\nedits about vandalism",
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
  scale_size_continuous(name = "Proportion of\nedits about vandalism",
                        labels = c(0, 0.025, 0.05, 0.075),
                        breaks = c(0, 0.025, 0.05, 0.075)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits about vandalism",
       y = "Total number of edits") +
    ggtitle("Editing about vandalism on Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_vandal_edits_scatterplot.png")

```

## Reverts

```{r}

bind_rows(
page_data_for_all_pages_rh_tbl %>%
  mutate(revert = ifelse(revert, 1, 0)) %>%
  group_by(Site) %>%
  summarise( n_revert_edits = sum(revert),
             n_edits = n()) %>%
  mutate(prop_revert_edits = n_revert_edits / n_edits,
           Site = "World Heritage Sites"),

ten_k_random_wp_pages_revision_history_page_details %>%
  mutate(revert = ifelse(revert, 1, 0)) %>%
  group_by(Site) %>%
  summarise( n_revert_edits = sum(revert),
             n_edits = n()) %>%
  mutate(prop_revert_edits = n_revert_edits / n_edits,
         Site = "Random pages")
) %>%

   ggplot(aes(prop_revert_edits,
             fill = Site)) +
  geom_density(alpha = 0.3) +
  scale_x_log10() +
  scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Proportion of reverting edits per article",
       fill = "Wikipedia pages") +
  theme_minimal()

ggsave("figures/wh_wikpedia_pages_revert_edits.png")

```

## Which articles have the most reverts?

```{r}

ggplot(revision_history_page_details,
         aes(rh_user_bot_prop,
             rh_n_edits,
             label = str_wrap(Site, 15))) +
  geom_point(alpha = 0.2,
             aes(size =   rh_revert_prop,
                 colour = rh_revert_prop)) +
    geom_text_repel(
    data            = revision_history_page_details %>%  
                      filter(rh_revert_prop > 0.12),
    segment.size  = 0.2,
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(0.5) +
  scale_color_viridis_c(name = "Proportion of\n edits reverted",
                        labels = c(0, 0.04, 0.08, 0.12, 0.16),
                        breaks = c(0, 0.04, 0.08, 0.12, 0.16)) +
  scale_size_continuous(name = "Proportion of\n edits reverted",
                        labels = c(0, 0.04, 0.08, 0.12, 0.16),
                        breaks = c(0, 0.04, 0.08, 0.12, 0.16)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 12) +
  labs(x = "Proportion of bots",
       y = "Total number of edits") +
    ggtitle("Reverted edits on Wikipedia articles")

ggsave("figures/wh_wikpedia_pages_reverts_edits_scatterplot.png")
```

## Is there a correlation between reverts and vandalism?

```{r}
left_join(page_data_for_all_pages, vandal_edits) %>%
  ggplot(aes(rh_revert_prop,
             prop_vandal_edits,
             size = n_edits)) +
  geom_point() +
  theme_minimal(base_size = 12) +
  labs(x = "Proportion of edits reverted",
       y = "Proportion of edits responding to vandalism") +
    coord_fixed(1)

ggsave("figures/wh_wikpedia_pages_reverts_vandal_edits_scatterplot.png")

```

## What's the typical distribution of talk page length?

```{r}
bind_rows(

ten_k_random_wp_pages %>%
  select(talk_page_wordcount) %>%
  mutate(Site = "Random pages"),

page_data_for_all_pages %>%
  select(talk_page_wordcount) %>%
  mutate(Site = "World Heritage pages")
) %>%

  ggplot(aes(talk_page_wordcount,
             fill = Site)) +
  geom_density(alpha = 0.3) +
   scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  labs(x = "Talk page word count",
       fill = "Wikipedia pages") +
  theme_minimal() +
  scale_x_log10(labels = scales::comma_format(accuracy = 1))

ggsave("figures/wh_wikpedia_pages_talk_page_worcount.png")
```

## which WH pages have the longest talk pages?

```{r}

wh_pages_talk_page_length <-
left_join(page_data_for_all_pages,
          revision_history_page_details_wordcount)

ggplot(wh_pages_talk_page_length,
         aes(rh_n_edits,
             rh_revert_prop,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.5,
             aes(size =   (talk_page_wordcount),
                 colour = (talk_page_wordcount))) +
    geom_text_repel(
    data            = wh_pages_talk_page_length %>%  
                      filter(talk_page_wordcount > 8000),
    segment.size  = 0.2,
    colour = "black",
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
  coord_fixed(1) +
  scale_color_viridis_c(name = "Talk page word count",
                        labels = c(5000, 10000, 15000, 20000),
                        breaks = c(5000, 10000, 15000, 20000)) +
  scale_size_continuous(name = "Talk page word count",
                        labels = c(5000, 10000, 15000, 20000),
                        breaks = c(5000, 10000, 15000, 20000)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits",
       y = "Proportion of edits that are reverts") +
    ggtitle("")

ggsave("figures/wh_wikpedia_pages_talk_page_wordcount_reverts_scatterplot.png")

```

## Talk page topic modelling

```{r}
library(tidytext)

tidy_talk_raw <-
enframe(unlist(wh_wiki_talk_pages)) %>%
  bind_cols(wh_wiki_table)

write.csv(tidy_talk_raw$value , "data/wh_wiki_talk_page_text.txt")

tidy_talk <-
  tidy_talk_raw %>%
    mutate(clean_text = str_remove_all(value, "\n|\t")) %>%
  unnest_tokens(word, clean_text) %>%
  anti_join(stop_words) %>%
  filter(!word %in% c("article", "page", "talk", "utc",
                      "class", "edit", "project's",
                      "importance", "rated", "wikiproject",
                      "project", "article", "articles", "article's",
                      "wikipedia", "start", "scale",
                      "world", "heritage", "sites",
                      "links", "http", "parser",
                      "output", "mw", "https",
                      "unsigned", "comment")) %>%
  filter(!str_detect(word, "[[:digit:]]+")) %>%
  filter(!str_detect(word, ":")) %>%
  filter(!str_detect(word, "articles")) %>%
  filter(!str_detect(word, "jump")) %>%
  filter(!str_detect(word, "\\."))

# check which sites have some words
tidy_talk %>%
  filter(word == "unesco") %>%
  group_by(Site) %>%
  tally(sort = T)

# top words
tidy_talk %>%
  count(word, sort = TRUE)

# biggest documents
tidy_talk %>%
  group_by(name) %>%
  tally(sort = TRUE)
```

The held-out likelihood is highest between 60 and 80, and the residuals are lowest around 50,

```{r}
library(quanteda)
library(stm)

talk_dfm <- tidy_talk %>%
  count(name, word, sort = TRUE) %>%
  cast_dfm(name, word, n)

# library(slam)
# talk_dfm_stm <- convert(talk_dfm, to = "stm")

# very time consuming
# k_search_output <-
# searchK(talk_dfm_stm$documents,
#         talk_dfm_stm$vocab,
#         K = seq(10, 100, 20),
#         cores = 1)
#
# plot(k_search_output)

# takes a few minutes
topic_model <- stm(talk_dfm, K = 60,
                   verbose = FALSE,
                   init.type = "Spectral")

png(filename = "figures/wh_talk_pages_top_topics.png", width = 1800, height = 2600, res = 300)
par(bty="n",col="grey40",lwd=10)
plot(topic_model,  text.cex = 0.75)
dev.off()

td_beta <- tidy(topic_model)

library(drlib) # devtools::install_github("dgrtwo/drlib")

td_beta %>%
    group_by(topic) %>%
    top_n(10, beta) %>%
    ungroup() %>%
    mutate(topic = paste0("Topic ", topic),
           term = reorder_within(term, beta, topic)) %>%
    ggplot(aes(term, beta, fill = as.factor(topic))) +
    geom_col(alpha = 0.8, show.legend = FALSE) +
    facet_wrap(~ topic, scales = "free_y") +
    coord_flip() +
    scale_x_reordered() +
    theme_minimal(base_size = 6) +
    labs(x = NULL, y = expression(beta),
         title = "Highest word probabilities for each topic",
         subtitle = "Different words are associated with different topics")

ggsave("figures/wh_wikpedia_pages_talk_page_topics.png")
```

## The probability that each document is generated from each topic.

```{r}
td_gamma <- tidy(topic_model, matrix = "gamma",                    
                 document_names = rownames(talk_dfm))

ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
  geom_histogram(alpha = 0.8, show.legend = FALSE) +
  facet_wrap(~ topic, ncol = 3) +
  labs(title = "Distribution of document probabilities for each topic",
       y = "Number of stories", x = expression(gamma)) +
      theme_minimal(base_size = 6)

```

## we may want to know which topics are associated with each talk page?

```{r}
topic_model_gamma <- tidy(topic_model, matrix = "gamma")

topic_model_gamma %>%
  filter(document %in% 1:10) %>%
  mutate(title = reorder(document, gamma * topic)) %>%
  ggplot(aes(factor(topic), gamma)) +
  geom_boxplot() +
  facet_wrap(~ title)
```

## Topic correlations

```{r}
mod.out.corr <- topicCorr(topic_model)

topic_labels <- labelTopics(topic_model)

topic_tag <- NULL
for(i in 1:nrow(topic_labels$score)){
  topic_tag[[i]] <-  paste0(as_tibble(topic_labels$score)[i, 1:3], collapse = "\n")
}

library(igraph)
g <- graph.adjacency(mod.out.corr$posadj)
V(g)$Degree <- degree(g, mode = 'in') # CALCULATE DEGREE
V(g)$Name <- topic_tag # ADD NAMES
E(g)$weight <- edge.betweenness(g)

library(ggraph)

ggraph(g, layout = "lgl") +
  geom_edge_link0(aes(width = weight), alpha = 0.1) +
  geom_edge_diagonal(label_colour = "blue", alpha = 0.1) +
    geom_node_point(aes(size = Degree), alpha = 0.6, colour = "steelblue") +
    geom_node_text(aes(label = Name), size = 3) +
    theme_graph(foreground = 'steelblue', fg_text_colour = 'white')

ggsave("figures/wh_talk_page_topic_correlation_network.png")
```

## Spatial patterns

## IP addresses

```{r}

ip_regex <- "(?(?=.*?(\\d+\\.\\d+\\.\\d+\\.\\d+).*?)(\\1|))"

get_ip_addresses <- function(x){
  re <- regexpr(
  ip_regex,
  x, perl = TRUE)
regmatches(x, re)
}

# get locations from IP addresses
library(rgeolocate)
ip_db <- system.file("extdata","GeoLite2-Country.mmdb", package = "rgeolocate")

```

Do WH sites have more geographically diverse contributions?

Get locations for random pages.

## How many IP edits on each page?

```{r}
randoms_revision_history_page_details <-
  map_df(ten_k_random_wp_pages_lst,
         ~.x$revision_history_page_details,
         .id = "page")

randoms_revision_history_page_details_ip <-
randoms_revision_history_page_details %>%
    mutate(is_ip_address = ifelse(get_ip_addresses(rh_user) != "", TRUE, FALSE),
         page = as.numeric(page))

randoms_revision_history_page_details_ip_prop <-
  randoms_revision_history_page_details_ip %>%
  group_by(page) %>%
  summarise(prop_ip_addresses = sum(is_ip_address) / n() )

both_ip_props <-
bind_rows(
revision_history_page_details_ip_addresses_countries %>%
  ungroup %>%
  select(prop_anon_of_all_edits) %>%
  mutate(source = "World Heritage Sites",
         prop_ip_addresses = prop_anon_of_all_edits),

randoms_revision_history_page_details_ip_prop %>%
    ungroup %>%
  select(prop_ip_addresses) %>%
    mutate(source = "Random pages"))

ggplot(both_ip_props,
       aes(fill = source,
           prop_ip_addresses)) +
  geom_density(alpha = 0.3) +
   scale_fill_viridis_d(labels = c("Random",
                               "World Heritage")) +
  theme_minimal() +
  xlab("Proportion of all edits that are anonymous")

ggsave("figures/proportion_of_IP_edits.png")
```

## Overall location of IP edits for all random pages

```{r}
randoms_revision_history_page_details_ip_location <-
randoms_revision_history_page_details_ip %>%
  filter(is_ip_address) %>%
  mutate(ip_location = map(rh_user, ~maxmind(.x, ip_db)))  %>%
  unnest(ip_location)

randoms_revision_history_page_details_ip_location_tally <-
randoms_revision_history_page_details_ip_location %>%
  filter(!is.na(country_name)) %>%
  mutate(country_name = fct_rev(fct_infreq(country_name))) %>%
  group_by(country_name) %>%
  tally(sort = TRUE) %>%
  filter(n > 100)

ggplot(randoms_revision_history_page_details_ip_location_tally,
       aes(country_name, n)) +
  geom_col() +
  coord_flip()   +
  theme_minimal() +
  scale_y_continuous(labels = scales::comma)
```

## What's the geographic diversity of edits per random page?

```{r}
randoms_revision_history_page_details_ip_location_props_per_page <-
randoms_revision_history_page_details_ip_location %>%
  filter(!is.na(country_name)) %>%
  mutate(country_name = fct_rev(fct_infreq(country_name))) %>%
  group_by(page, country_name) %>%
  tally() %>%
  mutate(prop = n / sum(n)) %>%
  filter(country_name %in% randoms_revision_history_page_details_ip_location_tally$country_name)

ggplot(randoms_revision_history_page_details_ip_location_props_per_page,
       aes(country_name,
           prop)) +
  geom_boxplot() +
  coord_flip()

randoms_revision_history_page_details_ip_location_props_per_page_div <-
  randoms_revision_history_page_details_ip_location_props_per_page %>%
  group_by(page) %>%
  summarise(shannon = vegan::diversity(n))

ggplot(randoms_revision_history_page_details_ip_location_props_per_page_div,
       aes( shannon)) +
  geom_histogram()
```

```{r}
# analyse the countries of IP address vs country of WH site
revision_history_page_details_ip_addresses <-
revision_history_page_details %>%
  mutate(edits_from_ip_addresses = map(revision_history_page_details,
                          ~.x %>%
                            filter(get_ip_addresses(rh_user) != "") %>%
                            mutate(ip_location = map(rh_user,
                                                     ~maxmind(.x, ip_db)))  %>%
                            unnest(ip_location)))

revision_history_page_details_ip_addresses_df <-
revision_history_page_details_ip_addresses %>%
  unnest(edits_from_ip_addresses)

revision_history_page_details_ip_addresses_countries <-
revision_history_page_details_ip_addresses_df %>%
  select(Site, Country, country_name, rh_n_edits ) %>%
  filter_all(all_vars(!is.na(.))) %>%
  group_by(Site, Country, rh_n_edits) %>%
  count(country_name) %>%
  mutate(prop_anon_of_all_edits = n / rh_n_edits) %>%
  mutate(internal_edits = ifelse(Country ==  country_name,
                                 TRUE, FALSE),
         n_anon_edits_total = n) %>%
  left_join(revision_history_page_details_ip_addresses_df) %>%
  distinct(Site,  
           Country,
           prop_anon_of_all_edits,
           internal_edits,
           .keep_all = TRUE) %>%
  group_by(Site,  Country) %>%
  summarise(sum_prop_internal = sum(n_anon_edits_total[internal_edits]) / sum(n_anon_edits_total),
            sum_prop_external = 1 - sum_prop_internal,
            rh_n_edits = unique(rh_n_edits),
            rh_n_edits_anon = sum(n_anon_edits_total),
            prop_anon_of_all_edits = sum(n) / rh_n_edits)
```

```{r}
# Histogram of proportion of anonymous edits
# TODO and random sites
ggplot(revision_history_page_details_ip_addresses_countries,
       aes(prop_anon_of_all_edits)) +
  geom_histogram() +
  theme_minimal(base_size = 12) +
  xlab("Proportion of all edits that are anonymous")

ggsave("figures/wh_wikipedia_pages_anon_edits_prop.png")
```

```{r}
# Histogram of proportion of all anonymous edits that come from same country as WH site
ggplot(revision_history_page_details_ip_addresses_countries,
       aes(sum_prop_internal)) +
  geom_histogram() +
  theme_minimal()
```

```{r}
ggplot(revision_history_page_details_ip_addresses_countries,
       aes(sum_prop_internal,
           prop_anon_of_all_edits)) +
  geom_point() +
  theme_minimal() +
  coord_equal()

```

## Circular chord plot

```{r}
adjacency_list_3_cols <-
revision_history_page_details_ip_addresses_df %>%
  filter(!is.na(Country),
         !is.na(country_name)) %>%
  group_by(Country, country_name) %>%
  count() %>%
  rename(to = Country,
         from = country_name,
         value = n) %>%
  ungroup() %>%
  mutate(from = ifelse(from == "Hashemite Kingdom of Jordan", "Jordan", from)) %>%
  select(from, to , value) %>%
  filter(value > 100) %>%
  left_join( revision_history_page_details_ip_addresses_df %>%
               select(country_name, continent_name) %>%
               distinct(),
             by = c('from' = 'country_name')) %>%
  arrange(continent_name,  from, to)

adjacency_list <-
adjacency_list_3_cols%>%
  select(-continent_name)

get_countries_in_continent <- function(x) {

  xx <-
  revision_history_page_details_ip_addresses_df %>%
    select(country_name, continent_name) %>%
    filter(continent_name == x) %>%
    pull(country_name) %>%
    unique()

  xx[
 unique( c(adjacency_list$from,
           adjacency_list$to))
 ]
}

africa   <- get_countries_in_continent("Africa")        
asia    <- get_countries_in_continent("Asia")       
europe  <-get_countries_in_continent("Europe")  
north_america  <- get_countries_in_continent("North America")         
oceania <-  get_countries_in_continent("Oceania")
south_america  <-  get_countries_in_continent("South America")

library(circlize)
circos.clear()
png("figures/chord_fig.png", res = 300, width = 2500, height = 2500)
chordDiagram(adjacency_list,
             directional = 1,
             direction.type = c("diffHeight", "arrows"),
             link.arr.type = "big.arrow",
             diffHeight = -uh(2, "mm"),
             annotationTrack = "grid",
             preAllocateTracks = list(track.height = max(0.4)))

# we go back to the first track and customize sector labels
circos.track(track.index = 1, panel.fun = function(x, y) {
    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index,
        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
}, bg.border = NA) # here set bg.border to NA is important

dev.off()

```

```{r eval=FALSE}

# stuff that doesn't work

highlight.sector(africa, track.index = 1, col = "#00FF0040",
    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(asia, track.index = 1, col = "#0000FF40",
    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(europe, track.index = 1, col = "blue",
    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(north_america, track.index = 1, col = "orange",
    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(oceania, track.index = 1, col = "purple",
    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(south_america, track.index = 1, col = "brown",
    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)

#--
circos.track(track.index = 2, panel.fun = function(x, y) {
    sector.index = get.cell.meta.data("sector.index")
    xlim = get.cell.meta.data("xlim")
    ylim = get.cell.meta.data("ylim")
    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
}, bg.border = NA)

#--
circos.clear()
circos.par(gap.after = rep(c(rep(1, 4), 8), 3))

chordDiagram(adjacency_list, annotationTrack = c("grid", "axis"),
    preAllocateTracks = list(
        track.height = uh(4, "mm"),
        track.margin = c(uh(4, "mm"), 0)
))

circos.track(track.index = 2, panel.fun = function(x, y) {
    sector.index = get.cell.meta.data("sector.index")
    xlim = get.cell.meta.data("xlim")
    ylim = get.cell.meta.data("ylim")
    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
}, bg.border = NA)

highlight.sector(africa, track.index = 1, col = "red",
    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(asia, track.index = 1, col = "green",
    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(europe, track.index = 1, col = "blue",
    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(north_america, track.index = 1, col = "orange",
    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(oceania, track.index = 1, col = "purple",
    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)

highlight.sector(south_america, track.index = 1, col = "brown",
    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)

```

## Networks

editors

## Controversies

Look at distributions of variables, then say 2sd is extreme, and match those to the WH pages to find out what they are

Can we detect -ve sentiment on the talk pages? Perhaps as distributions, over every 100 words per page

What's the typical distribution of the proportion of edits that are reverts?

```{r}
ggplot(ten_k_random_wp_pages,
       aes(rh_revert_prop)) +
  geom_histogram() +
  scale_x_log10()

```

What are the keywords for controversy in edit messages? And how common are these warring messages?

```{r}
randoms_revision_history_page_details_ip_warring_words <-
randoms_revision_history_page_details_ip %>%
  mutate(warring_words = (str_detect(rh_comment, 'undid|vandalism|why|inaccurate|wrong|warning|blocked|warring|disputed|neutral|unacceptable' )))

# distribution of edits with warring words
randoms_revision_history_page_details_ip_warring_words_prop <-
randoms_revision_history_page_details_ip_warring_words %>%
  group_by(page) %>%
  summarise(prop_warring_edits = sum(warring_words) / n())

ggplot(randoms_revision_history_page_details_ip_warring_words_prop,
         aes(prop_warring_edits)) +
  geom_histogram() +
  scale_x_log10()
```

Is there are correlation between the proportion of warring words and talk page length?

```{r}
# some interesting groupings
randoms_revision_history_page_details_ip_warring_words_prop %>%
  left_join(ten_k_random_wp_pages %>%
  mutate(page = 1:nrow(.))) %>%
  filter(prop_warring_edits > 0) %>%
  ggplot(aes(prop_warring_edits,
             talk_page_wordcount ,
             size = page_wordcount)) +
  geom_point(alpha = 0.2)
```

Is there are correlation between the proportion of warring words and revert frequency?

```{r}
randoms_revision_history_page_details_ip_warring_words_prop_revert_prop <-
randoms_revision_history_page_details_ip_warring_words_prop %>%
  left_join(ten_k_random_wp_pages %>%
  mutate(page = 1:nrow(.))) %>%
  filter(prop_warring_edits != 0,
         rh_revert_prop != 0)

lm(rh_revert_prop ~ prop_warring_edits,
   data = randoms_revision_history_page_details_ip_warring_words_prop_revert_prop) %>% summary

ggplot(randoms_revision_history_page_details_ip_warring_words_prop_revert_prop,
         aes(prop_warring_edits,
             rh_revert_prop)) +
  geom_point()
```

## time between edits

```{r}
library(lubridate)
randoms_revision_history_page_details_ip_time_diffs <-
randoms_revision_history_page_details_ip %>%
  group_nest(page) %>%
  mutate(time_diff = map(data, ~lag(.x$rh_date) - .x$rh_date)) %>%
  unnest(time_diff) %>%
  mutate(time_diff_days = as.numeric(time_diff / 60 / 60 / 24)) %>%
  mutate(time_diff_hours = as.numeric(time_diff / 60 / 60 )) %>%
  mutate(less_than_one_month = ifelse(time_diff_hours < 744, TRUE, FALSE)) %>%
  mutate(less_than_one_week = ifelse(time_diff_hours < 168, TRUE, FALSE)) %>%
  bind_cols(randoms_revision_history_page_details_ip)

rle_tbl <-
tibble(lths = rle(randoms_revision_history_page_details_ip_time_diffs$rh_user)$lengths,
vals = rle(randoms_revision_history_page_details_ip_time_diffs$rh_user)$values)

rle_tbl2 <- tibble(
  rh_user = rep(rle_tbl$vals, rle_tbl$lths),
  lths2 = rep(rle_tbl$lths, rle_tbl$lths)
)

randoms_revision_history_page_details_ip_time_diffs %>%
  filter(!is.na(time_diff_hours)) %>%
  mutate(quick_three_edits = time_diff_hours + lag(time_diff_hours) + lag(time_diff_hours, 2) + lag(time_diff_hours, 3))

randoms_revision_history_page_details_ip_time_diffs_quick <-
randoms_revision_history_page_details_ip_time_diffs %>%
 nest(-page) %>%  
 mutate(edits_3 = map(data, ~.x %>%
                              filter(less_than_one_week) %>%
                              filter(n() > 4 ))) %>%
  unnest(edits_3)

randoms_revision_history_page_details_ip_time_diffs %>%
  bind_cols(rle_tbl2) %>%
  filter(lths2 == 1) %>%
  filter(time_diff_hours < 24)

ggplot(randoms_revision_history_page_details_ip_time_diffs,
       aes(time_diff_days)) +
  geom_histogram()

```

## Temporal patterns

## Page ages: are WH pages younger than the typical WP page? What's their relationship to their inscription year?

```{r}
# get first and last edit, and inscription year
library(lubridate)
page_data_for_all_pages_rh_tbl_edit_start_end_span <-
page_data_for_all_pages_rh_tbl %>%
  group_by(Site) %>%
  summarise(first_edit_date = min(rh_date),
            last_edit_date = max(rh_date),
            edit_span = last_edit_date - first_edit_date) %>%
  mutate(Site = as.numeric(Site)) %>%
  arrange(Site) %>%
  bind_cols(page_data_for_all_pages) %>%
  mutate(inscription_year = as.Date(ISOdate(Year_num, 1, 1))) %>%
  mutate(diff_first_edit_inscription_year = as.numeric( as.POSIXlt(inscription_year) - ymd_hms(first_edit_date) ) / 365 )

page_data_for_random_rh_tbl_edit_start_end_span <-
randoms_revision_history_page_details %>%
  group_by(page) %>%
  summarise(first_edit_date = min(rh_date),
            last_edit_date = max(rh_date),
            edit_span = last_edit_date - first_edit_date) %>%
  mutate(page = as.numeric(page)) %>%
  arrange(page)

bind_rows(

  page_data_for_all_pages_rh_tbl_edit_start_end_span %>%
    select(edit_span) %>%
    mutate(source = "World Heritage"),

  page_data_for_random_rh_tbl_edit_start_end_span %>%
     select(edit_span) %>%
    mutate(source = "Random")

) %>%
  ggplot() +
geom_density(aes(as.numeric(edit_span / 365),
                 fill = source),
                 alpha = 0.3) +
  geom_vline(xintercept = year(Sys.Date()) - 2001,
             colour = "red") +
  annotate("text", x = 15, y = 0.2, label = "start of Wikipedia → ") +
  scale_fill_viridis_d() +  
  theme_minimal(base_size = 12) +
  xlab("Age of Wikipedia page (years)")

ggsave("figures/wh_wikpedia_pages_ages.png")
```

## Time between inscription year and first edit

```{r}

ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span,
       aes(Year_num,
           diff_first_edit_inscription_year)) +
  geom_jitter(alpha =  0.1, size = 3)  +
  geom_vline(xintercept = 2001, colour = "red") +
  geom_hline(yintercept = 0, colour = "red") +
  theme_minimal(base_size = 12) +
  xlab("Year of inscription on World Heritage list") +
  ylab("Difference between year of\ninscriptionand first edit on Wikipedia")

ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span,
       aes(Year_num,
           first_edit_date)) +
  geom_jitter(alpha =  0.1, size = 3) +
  theme_minimal(base_size = 12) +
  xlab("Year of inscription on World Heritage list") +
  ylab("first edit on Wikipedia")

ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span,
       aes(Year_num)) +
  geom_histogram() +
  theme_minimal(base_size = 12) +
  scale_x_continuous(breaks = seq(1975, 2019, 1)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  xlab("Year of inscription on World Heritage list")

ggsave("figures/wh_wikpedia_pages_inscription_year_hist.png")

ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span,
       aes(diff_first_edit_inscription_year)) +
  geom_histogram() +
  theme_minimal(base_size = 12)  +
  geom_segment(x = 0, xend = 0, y = 0, yend = 50, colour = "red") +
   geom_segment(x = -10, xend = -10, y = 0, yend = 50, colour = "blue") +
   geom_segment(x = -22, xend = -22, y = 0, yend = 50, colour = "blue") +
  ylim(0, 70) +
  annotate("text", x = 10, y = 59, label = "Page appeared\nbefore inscription\n→", size =8) +
  annotate("text", x =-10,  y = 59, label = "Page appeared\nafter inscription\n←", size = 8) +
  annotate("text", x =-22,  y = 5, label = "Inscribed in 1983→",
           size = 3, colour = "white", hjust = 1  ) +
  annotate("text", x =-10,  y = 5, label = "Inscribed in 1994→",
           size = 3, colour = "white", hjust = 1 ) +
  annotate("text", x =0,  y = 5, label = "Inscribed in 2001→",
           size = 3, colour = "white", hjust = 1 ) +
  xlab("Difference between year of inscription on World Heritage list and first edit on Wikipedia")

ggsave("figures/wh_wikpedia_pages_diff_time_inscription.png")

```

# reload data

`all_the_data_to_load_quickly.RData` is up to here

```{r}
load("data/all_the_data_to_load_quickly.RData")

# remove some big items
rm(list = ls(pattern = "random"))
library(tidyverse)
library(lubridate)
```

## time series of edits: breakouts relating to events? monthly seems like a good level of aggregation. What can we do for spike detection?

```{r}
wh_pages_edit_time_series <-
wh_pages_talk_page_length %>%
  unnest(revision_history_page_details) %>%
  filter(Year_num >= 2001) %>% # only sites inscribed after WP started
  group_by(Site) %>%
  mutate(the_d = floor_date(rh_date, "day")) %>%
    mutate(the_m = floor_date(rh_date, "month")) %>%
  group_by(Site, the_m) %>%
  tally() %>%
  filter(n() > 100) %>% # explore this value
  left_join(wh_pages_talk_page_length) %>%
  mutate(vline_year = ifelse(Year_num >= 2001, Year_num, NA)) %>%
  mutate(vline_year = ymd_hms(ISOdatetime(vline_year, 1, 1, 1, 0, 0)))

ggplot(wh_pages_edit_time_series) +
  geom_vline(aes(xintercept = vline_year), colour = "red") +
  geom_line(aes(the_m,
             n)) +
  facet_wrap( ~ str_wrap(Site, 30), scales = "free") +
  theme_minimal(base_size = 6)

ggsave("figures/wh_wikpedia_pages_edit_time_series.png", h = 9, w = 12)
```

## Spike detection

for randoms, what even is an anomaly?

```{r}
# devtools::install_github("hrbrmstr/AnomalyDetection")
library(AnomalyDetection)
randoms_revision_history_page_details_ip_location_monthly <-
randoms_revision_history_page_details_ip_location %>%
  group_by(page) %>%
  mutate(the_d = floor_date(rh_date, "day")) %>%
    mutate(the_m = floor_date(rh_date, "month")) %>%
  group_by(page, the_m) %>%
  tally() %>%
  filter(n() > 200) # explore this value

randoms_revision_history_page_details_ip_location_monthly_anom <-
  randoms_revision_history_page_details_ip_location_monthly %>%
  ungroup %>%
  group_nest(page) %>%
  mutate(anomalies = map(data, ~ad_ts(.x,
                                      max_anoms = 0.2,
                                      alpha = 0.005,
                                      threshold = "p95"))) %>%
  unnest(anomalies)

ggplot() +
  geom_line(
    data=randoms_revision_history_page_details_ip_location_monthly %>%
      filter(page %in% randoms_revision_history_page_details_ip_location_monthly_anom$page),
    aes(the_m, n),
    size=0.125, color="lightslategray")  +
  geom_point(
    data=randoms_revision_history_page_details_ip_location_monthly_anom,
    aes(timestamp, anoms),
    color="#cb181d", alpha=1/3) +
  scale_x_datetime(date_labels="%b\n%Y") +
  facet_wrap( ~ page, scales = "free_y")

```

for WH sites, look for editing anomalies using all editors, put a line on for inscpription year so we can see if there are peaks in activity around inscription.

```{r}

n <- 12 # months of edit data
revision_history_page_details_ip_addresses_df_monthly_edits <-
revision_history_page_details_ip_addresses_df  %>%
  mutate(the_d = floor_date(rh_date, "day")) %>%
    mutate(the_m = floor_date(rh_date, "month")) %>%
  group_by(Site, the_m) %>%
  tally() %>%
  filter(n() >  n ) # n months worth of data - explore this value

# distribution of edits per month
ggplot(revision_history_page_details_ip_addresses_df_monthly_edits,
       aes(n)) +
  geom_histogram() +
  scale_x_log10()

# subset so we get only sites with > n1 edits/month, and at least 3 months worth of edits

n1 <- 10  # edits per month
n2 <- 12 # months worth of edits
revision_history_page_details_ip_addresses_df_monthly_edits_10 <-
revision_history_page_details_ip_addresses_df_monthly_edits %>%
  filter(max(n) >= n1) %>%
  group_by(Site) %>%
  filter(n() >= n2)
```

Anomalies in editing activity

```{r}

# detect anomalies
revision_history_page_details_ip_addresses_df_monthly_edits_anoms <-
  revision_history_page_details_ip_addresses_df_monthly_edits_10 %>%
  ungroup %>%
  group_nest(Site) %>%
  mutate(anomalies = map(data, ~ad_ts(.x,
                                      max_anoms = 0.2,
                                      alpha = 0.005,
                                      threshold = "p95"))) %>%
  unnest(anomalies) %>%
  group_by(Site) %>%
  filter(max(anoms) >= 50) # where the anomaly is n edits/month or more

ggplot() +
  geom_line(
    data=revision_history_page_details_ip_addresses_df_monthly_edits_10 %>%
      filter(Site %in% revision_history_page_details_ip_addresses_df_monthly_edits_anoms$Site),
    aes(the_m, n),
    size=0.125, color="lightslategray")  +
  geom_point(
    data=revision_history_page_details_ip_addresses_df_monthly_edits_anoms,
    aes(timestamp, anoms),
    color="#cb181d", alpha=1/3) +
  scale_x_datetime(date_labels="%b\n%Y") +
  facet_wrap( ~ Site, scales = "free") +
  theme_minimal()
```

  - length of articles http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.451.4208&rep=rep1&type=pdf
  - edit history to identify: diversity of contributions,
  - reverts in edits for spotting contentious topics https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0038869 http://www.contropedia.net/  http://wwm.phy.bme.hu/
    - vandalism traces in edit history
  - talk page length
  - number of links in each page
  - page views: https://www.sciencedirect.com/science/article/abs/pii/S0006320716301240
  - timing of edits: political events? Brexit?
    - citations in articles: https://arxiv.org/abs/0705.2106
  - are the citations scholarly? Archaeological? Meskell?
    - citations to these articles: https://www.tandfonline.com/doi/full/10.1080/0194262X.2016.1206052
  - network analysis of editors, clusters of editors
  - sentiment analysis of talk pages
  - geolocation of anon editors by IP address
  - bots and technicity https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0171774 but see https://dl.acm.org/citation.cfm?id=3134684

  - Compare to 10000 random Wikipedia sites
  - Compare to WH sites in media & academic literature

### 2020-05-24 analysis/paper/paper.Rmd
more writing abotu WHL

@@
 output:
-    bookdown::html_document2:
+    bookdown::word_document2:
       fig_caption: yes
@@
   comment = "#>",
+  dpi = 300,
   fig.path = "../figures/"
@@
 
+## Wikipedia as a Context of Heritage Production
+
 Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, Wikipedia.
-This is a highly influential, with 11 billion page views per month (https://stats.wikimedia.org/#/en.wikipedia.org), and well-known online encyclopedia that anyone can edit.
+Originating in 2001, this is a highly influential and well-known online encyclopedia, currently with 11 billion page views per month (https://stats.wikimedia.org/#/en.wikipedia.org), that anyone can edit.
 Although anyone can edit, most internet users do not, and the characteristics of people who do edit are important to understand to identify biases in the encyclopedia's content.
@@
 
-In addition to the human users and the technological system that enables and constrains their activities on Wikipedia, there is an important third element of the ecosystem that contributes to Wikipedia's uniqeness: the bots.
-While bots are not unique to Wikipedia, they are important contributors, responsible for a large proportion of edits, and shape the human experience in signficant ways [@niederer2010wisdom' @geiger2009social].
+```{r bot-table}
+library(tidyverse)
+
+bot_table <- 
+  tribble(~"Role", ~"Function", ~"Example",
+          "Generator", "Generate article pages based on predefined templates.", "Rambot, RussBot",
+          "Fixer", "Fix errors in article pages in order to keep the information neat and correct.", "CmdrObot, Yobot",
+          "Connector", "Connect Wikipedia with other sites and databases", "KasparBot",
+          "Tagger", "Tag articles with different templates and categories", "AnomieBot, Smackbot, Cydebot",
+          "Clerk", "A variety of tasks including updating statistical information, documenting user status, updating maintenance pages", "AnomieBot, Smackbot",
+          "Archiver", "Archive closed discussions and maintain the archived content by assigning an index and sorting them alphabetically", "AnomieBot, Cyberbot_I",
+          "Protector", "Detect and regulate destructive behaviors", "ClueBot NG",
+          "Advisor", "Provide editors with suggestions about articles that they might want to contribute to.", "SuggestBot",
+          "Notifier", "Deliver messages to editors.", "NoomBot"
+          )
+
+knitr::kable(bot_table, caption = "Summary of Wikipedia bot types and functions, from Zheng et al. (2019)")
+```
+
+In addition to the human users and the technological system that enables and constrains their activities on Wikipedia, there is an important third element of the ecosystem that contributes to Wikipedia's uniqueness: the bots.
 Wikipedia bots are computer scripts that automatically handle repetitive and mundane tasks to develop, improve, and maintain the encyclopedia.
-@zheng2019roles
+While bots are not unique to Wikipedia, they are important contributors, responsible for a large proportion of edits, and shape the human experience in significant ways [@niederer2010wisdom' @geiger2009social; @geiger2014bots].
+They also evolve and autonomously engage in complex interactions with other bots to modify the encyclopedia [@tsvetkova2017even; @geiger2017operationalizing].
+@zheng2019roles studied all 1,601 bots that were registered at the time of their study, and classified them into 9 bot roles and 25 associated bot functions.
+Table \@ref(tab:bot-table) shows the bots that were identified in our study and their categories and functions according to @zheng2019roles.
 
-@tsvetkova2017even  @geiger2017operationalizing
+##  UNESCO World Heritage Cultural Sites as foci of Conflict
 
-An incredible sociotechnical system of content production and maintenance with human and non-human actors: people, bots: https://www.makeuseof.com/tag/bots-edit-wikipedia-humans-made/  (eg.
-rambot) and “software-assisted human editors” https://journals.sagepub.com/doi/pdf/10.1177/1461444810365297 (good figs here)
-Editing mechanics (http://www.contropedia.net/ ), bots (fighting https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0171774 but see https://dl.acm.org/citation.cfm?id=3134684),
+```{r wh-unesco-count}
+# all WH sites according to UNESCO
+# from https://whc.unesco.org/en/syndication on 22 May 2020
+wh_unesco <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+  filter(category %in% c("Cultural"))
+```
 
-Specifically we investigate how people interact with Wikipedia articles about cultural sites inscribed on the WHL.
-We chose the CS-WHL as a bounded set of cultural heritage elements with near-global distribution, broad public interest, a wide temporal distribution in both the age of the cultural sites, and the age of inscription on the WHL, and the high intensity of cultural and political discussions that often surround the inscription of site on the WHL.
-These qualities make it an ideal data set as an entry point for digital heritage studies of online peer production communities, which are typically goal-driven (e.g.
-'write quality articles') compared to social media activity where activity is more event-driven analysis (e.g.
+We investigate how the unique technicity of Wikipedia shapes interactions between people and the past with a case study on the processes of constructing knowledge about cultural sites inscribed on the WHL.
+We chose the CS-WHL as a bounded set of cultural heritage elements with several characteristics that make it of general interest.
+It has a global geographic distribution, broad public interest at local and international scales, in both online and face-to-face communities; a wide temporal distribution in both the age of the cultural sites, the ages of inscription on the WHL, and the ages of their appearance on Wikipedia; and finally many CS-WHL have a high intensity of cultural and political discussions that surround events affecting these sites, such as their inscription on the WHL.
+These qualities make it an ideal data set as an entry point for case studies of digital heritage in online peer production communities, where activities are typically goal-driven (e.g.
+'write quality articles') compared to social media activity where user activities are more often event-driven (e.g.
 'share reactions to Brexit').
+
+```{r wh-unesco-map, fig.cap="Cultural Sites on the UNESCO World Heritage List.
+Countried coloured black currently have no listed cultural sites.
+Inset shows the distribution of sites per country.
+Map data from naturalearthdata.com", fig.width=15}
+source(here::here("analysis/paper/001-UNESCO-CS-WHL-world-map-counts.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_country_unesco_count_map.png"))
+```
+
+UNESCO was established in 1945, shortly after the end of the Second World War, for the purpose of helping to rebuild after the war, and preserve peace by promoting the international exchange of ideas.
+In 1975 the UNESCO-drafted "Convention Concerning the Protection of the World Cultural and Natural Heritage" came into force and established the World Heritage List (WHL) to protect natural and cultural sites and landscapes around the world that have outstanding universal value.
+Currently there are `r nrow(wh_unesco)` cultural properties on the UNESCO WHL, with the first sites inscribed in `r min(wh_unesco$date_inscribed)`.
+On average, most countries have 2-3 sites, with most sites located in Italy and western Europe, and several countries having no sites at all, for example, several central African countries, Taiwan, and New Zealand (Figure \@ref(fig:wh-unesco-map)).
+
+In her institutional ethnography of UNESCO's role in protecting world heritage, @meskell2018future argues that the WHL is less about preserving heritage than about political and economic transactions between states and state-like actors.
+Sites that are listed, or candidates for listing, are often foci of disputes and negotiations about territory, sovereignty, and security, as well as international corporate activity [@meskell2018future].
+This is because the process of selecting of sites to be inscribed on the WHL has become politicized and driven by countries’ political influence and national strategic interests [@bertacchini2016politicization].
+For example, the members of the World Heritage Committee are mostly career diplomats rather than heritage specialists, indicating that the processes and decisions of this committee may be motivated more by political trade-offs than by heritage expertise and judgment [@von2011concept].
+
+Several CS-WHL sites are notable for the conflicts and tensions that have surrounded their inscription.
+The 1992 inscription of Angkor (an ancient city and empire in Cambodia, prominent during the 9th to the 15th centuries AD) was supported by exiled supporters of the genocidal Khmer Rouge regime, hoping to strengthen territorial claims [@locard2015myth].
+They appropriated Western discourse on national cultural heritage to argue for the safeguarding of Angkor as part of their quest for national independence and international recognition.
+Early in the Khmer Rouge regime Angkor was declared a symbol of enslavement by a primitive culture, but when the Khmer Rouge adopted a new rhetoric of a supposedly civilizing mission, they presented it as the site one of the great world civilizations [@falser2015representing].
+The 2003 inscription of Mapungubwe (the site of the first indigenous kingdom in Southern Africa, 900-1,300 AD) was preceded by a recommendation from ICOMOS (International Council on Monuments and Sites, a professional association that is a key advisory body to the Wold Heritage Committee) not to inscribe because of the farming and mining activity in highly sensitive areas near the site, and the unclear ownership of the mining rights at the time [@meskell2011paris].
+Despite this negative recommendation, geopolitical machinations within the Committee, especially by the Indian and Russian delegates, lead to Mapungubwe being inscribed on the list, although without the typical prerequisites of an integrated management plan or complete buffer zone [@meskell2012rush].
+These examples of Angkor and Mapungubwe demonstrate the attention that the WHL inscription process can generate due to political activitsm, conflicts and intrigue.
+
+Physical conflict at or near CS-WHL are also major events that galvanise public interest in these locations.
+World Heritage sites in Palestine, Mali, Syria, Congo and Cambodia have recently been sites of violence, in many cases the violence is specifically linked to their potential WHL nomination, listing or management.
+In 1998 anti-government and mostly Hindu Tamil groups bombed the holy Buddhist site of the Temple of the Tooth at the WHL site of Kandy (the last capital of the ancient kings of Sri Lanka), killing 17 people and substantially damaging the temple [@coningham1999paradise].
+In Mali during 2012, fighting between government and rebel groups lead to the damage and destruction of tombs at the CS-WHL sites of Gao and Timbuktu [@brioschi2017discourses].
+The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are currently among the 53 sites on the List of World Heritage in Danger (https://whc.unesco.org/en/danger/).
+In 2015 ISIS militants destroyed the Temple of Bel in Palmyra, Syria (a CS-WML site of monumental ruins, once great city at the crossroads between east and west in the ancient world) [@gornik2015can]
+
+in Kandy (Sri Lanka) ,
+Palmyra (Syria), etc.
+• Preah Vihear (2008) on a disputed
+part of Thai-Cambodia border,
+WikiLeaks documents the
+hyperconnectivity of international
+actors
 

### 2020-05-24 analysis/paper/000-scrape-wikipedia-random-pages.R

@@ -6,7 +6,7 @@ library(vegan)
 rando <- "https://en.wikipedia.org/wiki/Special:Random"
 
 # gets data about n WP pages
-n <- 10000
+n <- 100000
 random_page_data <- rerun(n, get_data_about_page_safe(rando) )
 
 # drops the pages that returned an error
@@ -15,20 +15,20 @@ random_page_data_lst <- transpose(random_page_data)[["result"]]
 random_page_data_lst <- discard(random_page_data_lst, ~.x[1] == "some_problem")
 
 # put page data into a table
-random_page_data_tbl <- 
+random_page_data_tbl <-
   tibble(page_wordcount =      map_int(random_page_data_lst, ~.x$page_wordcount),
          page_wikilinks_out =  map_int(random_page_data_lst, ~.x$page_wikilinks_out),
          page_wikilinks_in =   map_int(random_page_data_lst, ~.x$page_wikilinks_in),
          page_cited_items_on = map_int(random_page_data_lst, ~.x$page_cited_items_on),
          rh_user_simpson_idx = map_dbl(random_page_data_lst, ~.x$rh_user_simpson_idx),
-         rh_user_bot_prop =    map_dbl(random_page_data_lst, ~.x$rh_user_bot_prop), 
-         rh_revert_prop =      map_dbl(random_page_data_lst, ~.x$rh_revert_prop), 
+         rh_user_bot_prop =    map_dbl(random_page_data_lst, ~.x$rh_user_bot_prop),
+         rh_revert_prop =      map_dbl(random_page_data_lst, ~.x$rh_revert_prop),
          talk_page_wordcount = map_dbl(random_page_data_lst, ~.x$talk_page_wordcount),
          page_views_last_n_days_total = map_int(random_page_data_lst, ~.x$page_views_last_n_days_total)
   )
 
-random_page_data_tbl %>% 
-  gather(variable, value) %>% 
+random_page_data_tbl %>%
+  gather(variable, value) %>%
   ggplot(aes(value)) +
   geom_histogram() +
   facet_wrap( ~ variable, scales = "free")

### 2020-05-24 analysis/paper/001-EDA.R

@@ -1,6 +1,8 @@
 library(tidyverse)
 
-page_data_for_all_pages <- readRDS("data/page_data_for_all_pages.rds")
+# stored at https://drive.google.com/drive/u/1/folders/1TI7JpQHZpMFqxJvNwUPSJhoVCduarCcm
+page_data_for_all_pages <-
+  readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
 
 names(page_data_for_all_pages)
 
@@ -8,26 +10,26 @@ normalize = function(x) (x-min(x))/(max(x)-min(x))
 
 #--------------------------------------------------------------------------
 # take a look at the distribution of page variables
-some_page_variables <- 
-  page_data_for_all_pages %>% 
-  select(page_wordcount, 
+some_page_variables <-
+  page_data_for_all_pages %>%
+  select(page_wordcount,
          page_wikilinks_out,
          page_wikilinks_in,
-         page_cited_items_on) %>% 
+         page_cited_items_on) %>%
   mutate(page_wikilinks_out_per_word = page_wikilinks_out / page_wordcount,
-         page_cited_items_on_per_word = page_cited_items_on / page_wordcount) 
-  
-some_page_variables %>% 
-  gather(variable, value) %>% 
+         page_cited_items_on_per_word = page_cited_items_on / page_wordcount)
+
+some_page_variables %>%
+  gather(variable, value) %>%
 ggplot(aes(value)) +
   geom_histogram() +
-  facet_wrap( ~ variable, 
+  facet_wrap( ~ variable,
               scales = "free") +
   scale_x_log10() +
   theme_minimal()
 
 library(GGally)
-ggpairs( some_page_variables %>% 
+ggpairs( some_page_variables %>%
            mutate_all(log)) +
   theme_minimal()
 
@@ -36,50 +38,50 @@ library(uwot)
 library("tmap")
 data("World")
 
-pages_umap_input <- 
-  some_page_variables  %>% 
+pages_umap_input <-
+  some_page_variables  %>%
   mutate(page_wordcount_norm = normalize(page_wordcount),
          page_wikilinks_in_norm= normalize(page_wikilinks_in),
          page_wikilinks_out_per_word_norm = normalize(page_wikilinks_out_per_word),
-         page_cited_items_on_per_word_norm = normalize(page_cited_items_on_per_word)) %>% 
[…]

### 2020-05-24 analysis/paper/001-UNESCO-CS-WHL-world-map-counts.R

@@ -1,0 +1,97 @@
+library(tidyverse)
+
+wh_unesco <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+  filter(category %in% c("Cultural"))
+
+estimate_mode <- function(x) {
+  d <- density(x)
+  d$x[which.max(d$y)]
+}
+
+theme_nogrid <- function (base_size = 12, base_family = "") {
+  theme_bw(base_size = base_size,
+           base_family = base_family) %+replace%
+    theme(panel.grid = element_blank() )
+}
+
+
+wh_unesco_countries <-
+  wh_unesco %>%
+  separate_rows(states_name_en, convert = TRUE, sep = ",") %>%
+  mutate(country = case_when(
+    states_name_en == "Bolivia (Plurinational State of)"  ~ "Bolivia",
+    states_name_en == "Cabo Verde"  ~ "Republic of Cabo Verde",
+    states_name_en == "Czechia"  ~ "Czech Republic",
+    states_name_en == "Democratic People's Republic of Korea"  ~ "Republic of Korea",
+    states_name_en == "Gambia (the)"  ~ "The Gambia",
+    states_name_en == "Holy See"  ~ "Vatican",
+    states_name_en == "Iran (Islamic Republic of)"  ~ "Iran",
+    states_name_en == "Lao People's Democratic Republic"  ~ "Lao PDR",
+    states_name_en == "Micronesia (Federated States of)"  ~ "Federated States of Micronesia",
+    states_name_en == "Syrian Arab Republic"  ~ "Syria",
+    states_name_en == "the former Yugoslav Republic of Macedonia"  ~ "Macedonia",
+    states_name_en == "United Kingdom of Great Britain and Northern Ireland"  ~ "United Kingdom",
+    states_name_en == "United Republic of Tanzania"  ~ "Tanzania",
+    states_name_en == "United States of America"  ~ "United States",
+    states_name_en == "Venezuela (Bolivarian Republic of)"  ~ "Venezuela",
+    states_name_en == "United States of America"  ~ "United States",
+    states_name_en == "Viet Nam"  ~ "Vietnam",
+    states_name_en == "Republic of Moldova"  ~ "Moldova",
+    TRUE ~ as.character(states_name_en)
+  ))
+
+wh_unesco_countries_count <-
+  wh_unesco_countries %>%
+  count(country)
+
+median_number_unesco_sites_per_country <-
[…]

### 2020-05-26 analysis/paper/999-code-for-the-Stirling-ppt.Rmd
start to write results

@@
 # load the random pages
-ten_k_random_wp_pages <- readRDS(here::here("data", "random_page_data_tbl.rds"))
+ten_k_random_wp_pages <- readRDS(here::here("analysis/data/raw_data/random_page_data_tbl.rds"))
 
 # load the random pages revision histories
-ten_k_random_wp_pages_lst <- readRDS(here::here("data", "random_page_data_lst.rds"))
+ten_k_random_wp_pages_lst <- readRDS(here::here("analysis/data/raw_data/random_page_data_lst.rds"))
 
@@
 page_data_for_all_pages <-
-  readRDS(here::here("data",
-                     "page_data_for_all_pages.rds"))
+  readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
 
@@
 wh_wiki_table <-
-  read_csv(here::here("data",
-                      "wh_wiki_table.csv"))
+  readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls"))
 
 # the talk pages for all WH sites, with WP pages (n = 846)
-wh_wiki_talk_pages <-  readRDS(here::here("data",
-                     "wh_wiki_table_talk_page_content.rds"))
+wh_wiki_talk_pages <-  readRDS(here::here("analysis/data/raw_data/wh_wiki_table_talk_page_content.rds"))
 
@@
 # from https://whc.unesco.org/en/syndication
-wh_unesco <- readxl::read_excel(here::here("data",
-                                           "whc-sites-2018.xls")) %>%
+wh_unesco <- wh_wiki_table %>%
   filter(category %in% c("Cultural"))

### 2020-05-26 analysis/paper/paper.Rmd
start to write results

@@
 # from https://whc.unesco.org/en/syndication on 22 May 2020
-wh_unesco <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+wh_unesco <- 
+  readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
   filter(category %in% c("Cultural"))
@@
 Early in the Khmer Rouge regime Angkor was declared a symbol of enslavement by a primitive culture, but when the Khmer Rouge adopted a new rhetoric of a supposedly civilizing mission, they presented it as the site one of the great world civilizations [@falser2015representing].
-The 2003 inscription of Mapungubwe (the site of the first indigenous kingdom in Southern Africa, 900-1,300 AD) was preceded by a recommendation from ICOMOS (International Council on Monuments and Sites, a professional association that is a key advisory body to the Wold Heritage Committee) not to inscribe because of the farming and mining activity in highly sensitive areas near the site, and the unclear ownership of the mining rights at the time [@meskell2011paris].
-Despite this negative recommendation, geopolitical machinations within the Committee, especially by the Indian and Russian delegates, lead to Mapungubwe being inscribed on the list, although without the typical prerequisites of an integrated management plan or complete buffer zone [@meskell2012rush].
+The 2003 inscription of Mapungubwe (the site of the first indigenous kingdom in Southern Africa, 900-1,300 AD) was preceded by a recommendation from ICOMOS (International Council on Monuments and Sites, a professional association that is a key advisory body to the World Heritage Committee) not to inscribe because of the farming and mining activity in highly sensitive areas near the site, and the unclear ownership of the mining rights at the time [@meskell2011paris].
+Despite this negative recommendation, geopolitical machinations within the Committee, especially by the Indian and Russian delegates, led to Mapungubwe being inscribed on the list, although without the typical prerequisites of an integrated management plan or complete buffer zone [@meskell2012rush].
 These examples of Angkor and Mapungubwe demonstrate the attention that the WHL inscription process can generate due to political activitsm, conflicts and intrigue.
@@
 The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are currently among the 53 sites on the List of World Heritage in Danger (https://whc.unesco.org/en/danger/).
-In 2015 ISIS militants destroyed the Temple of Bel in Palmyra, Syria (a CS-WML site of monumental ruins, once great city at the crossroads between east and west in the ancient world) [@gornik2015can]
-
-in Kandy (Sri Lanka) ,
-Palmyra (Syria), etc.
-• Preah Vihear (2008) on a disputed
-part of Thai-Cambodia border,
-WikiLeaks documents the
-hyperconnectivity of international
-actors
+In 2015, ISIS militants destroyed the Temple of Bel in Palmyra, Syria (a CS-WML site of monumental ruins, once great city at the crossroads between east and west in the ancient world) [@gornik2015can].
+Preah Vihear, inscribed in 2008, is a CS-WHL located on a long-disputed section of the Thai-Cambodia border that has been a site of both violent military clashes and international political intrigue.
+Although both Thailand and Cambodia supported the nomination of the site to the WHL, the Thai government objected to maps in the nomination package that showed Cambodia as the owner of disputed land next to the temple, leading to protests and military clashes [@sothirak2013cambodia].
+@meskell2020world's analysis of US diplomatic cables released by WikiLeaks further reveals that settlement of disputes over Preah Vihear were intricately tied to broader issues of foreign policy and US and Chinese investment, especially access to natural gas reserves in the Gulf of Thailand.
+For example, the cables reveal negotiations for Cambodia to retain their temple, leading to the enhancement of Thailand's underwater assets, and the United States negotiating for extended contracts with both countries.
 
@@
 
-We survey the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics) to answer the question: how does engagement with the past compare on Wikipedia compare to engagement with other topics?
-We use a random sample of 10,000 Wikipedia articles as a random sample to compare with articles about cultural sites on the UNESCO World Heritage List.
-We investigate spatial patterns of behaviour on these Wikipedia articles to answer the question:  are the editors of CS-WHL located near the sites they edit, indicating local community interest in the online representation of their heritage, or in other countries, impling a digital colonalism of world heritage information on Wikipedia where one community's heritage is interpreted and communicated by another?
-Finally we investigate temporal patterns of activity on CS-WHL Wikipedia pages to answer the question of how correlated editing activity is with events outside of Wikipedia relating to the CS-WHL sites, such as their inscription on the WHL.
+Our brief review of controversial cultural sites on the WHL shows the intensity and diversity of conflicts and tensions that surround these sites.
+Many CS-WHL are symbols of national, cultural, political, and religious identity, and the extent of political involvement in negotiations of WHL inscriptions indicates they are of great public interest among local and diasporic communities.
+Our goal in this study is answer the question of how this interest is expressed within the socio-technical constraints of Wikipedia.
+How are conflicts over CS-WHL enacted in the canalized interactions of the world's largest encyclopedia?
+We attempt to answer this question by studying all the CS-WHL that have Wikipedia articles.
+We surveyed the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics).
+By comparing these basic characteristics of Wikipedia articles about CS-WHL to 10,000 random Wikipedia articles we will answer the question: how does engagement with the past compare via CS-WHL on Wikipedia compare to engagement with other topics?
+Do Wikipedia articles about controversial CS-WHL sites, such as those discussed above, get more attention than random Wikipedia articles?
+Can we detect conflict in the edit histories, bot activity, and talk pages for Wikipedia articles about CS-WHL sites, and how does this conflict relate to the types of controversies noted above?
 
-In this paper we contribute to digital heritage studies into a new online domain
+The highly detailed edit histories that Wikipedia keeps for every article allow us to further investigate spatial and temporal questions relating to engagement with the past and conflicts surrounding CS-WHL sites.
+For example, when an article is edited by a user who does not have a Wikipedia user account (or is not logged into their account), their edit is identified by that person's IP address.
+This IP address can be used to geo-locate the user to the city they were in when the made the edit.
+We geo-located all edits with IP addresses for all Wikipedia articles CS-WHL sites to determine the country of origin of those edits.
+This helps us to answer the question: are the editors of articles about CS-WHL located near the sites they edit, indicating local community interest in the online representation of their heritage?
+Or are editors located in other countries, implying a digital colonialism of world heritage information on Wikipedia where one community's heritage is interpreted and communicated by another?
+The time and date stamps attached to every edit on every article allows us to investigate temporal patterns of activity on CS-WHL Wikipedia articles.
+Analyses of these data help us to answer the question: is Wikipedia editing activity correlated with events outside of Wikipedia relating to the CS-WHL sites, such as conflict events, or their inscription on the WHL?
+
+We obtained data about Wikipedia articles by scraping the HTML pages with the rvest package for R [@rvest].
+We used the SelectorGadget [@cantino2017selectorgadget] extension for the Chrome web browser to identify specific elements of interest, or nodes, on the HTML pages, and wrote custom R functions to extract data from these nodes.
+The highly structured nature of most Wikipedia pages afforded us much efficiency during data collection, however, a not insignificant number of pages had minor irregularities, for example, exotic table formatting or minor deviations from widely used templates, that necessitated more complex programming.
+An especially challenging issue was minor irregularities in spelling place names, for example, "Saint Kitts and Nevis" and "St.
+Kitts and Nevis", which can confound programmatic joining and summarizing of data by failing to recognize as the same place and leading to under-counting.
+We attempted to correct these manually in our code.
+We collected data during May 2019, and due to the dynamic nature of Wikipedia, it is highly likely that articles in our study have subtly changed since our data collection as users and bots continue their activity.
+It is unlikely that articles in our sample have been deleted from Wikipedia since our data collection, because of the high notability of CS-WHL, but it is possible that new articles have since appeared about sites that were not represented on Wikipedia since we collected the data.
+
+# Reproducibility and Open Source Materials for This Study
+
+To enable reuse of our materials and improve reproducibility and transparency [@marwick2017computational], we include the entire R code [@rprogram] used for all the analysis and visualizations contained in this article in our compendium at http://doi.org/10.17605/OSF.IO/AY27G.
+Also in this version-controlled compendium are the raw data for all the results reported here.
+All of the figures and quantitative results presented here can be independently reproduced with the code and data in this repository.
+In our compendium our code is released under the MIT license, our data as CC-0, and our figures as CC-BY, to enable maximum reuse (for more details, see @marwick2018packaging).
 
 # Results
+
+```{r wh-wiki-map, fig.cap="Wikipedia articles for Cultural Sites on the UNESCO World Heritage List.
+Countries coloured black currently have no Wikipedia articles for CS-WHL sites.
+Inset shows the distribution of articles per country.
+Map data from naturalearthdata.com", fig.width=15}
+source(here::here("analysis/paper/002-Wikipedia-CS-WHL-world-map-counts.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_country_wikipedia_count_map.png"))
+```
+
+Of the `r nrow(wh_unesco)` cultural sites on the World Heritage List at the time of writing, we found Wikipedia articles for `r sum(wh_wk_country_counts$n)`.
+To characterize the overall variability of article according to the basic characteristics described above, we applied a Uniform Manifold Approximation and Projection (UMAP) to reduce the dimensionality of our data.
+After a two-dimensional projection was obtained, we used Hierarchical Density-Based Spatial Clustering of Applications with Noise (HDBSCAN) to identify clusters, and Random Forests to identify variable loadings so we could determine which of the basic characteristics were most important in driving variability between the articles.
+
+Figure \@ref(fig:wh-wiki-map) shows that most countries have between 2-3 CS-WHL on Wikipedia, with Germany, India, China, France and Spain being the countries with the most articles about their CS-WHL.
 
@@
 
-<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
-##### pagebreak
+Thanks to Chiara Bonacchi, Rodney Harrison, and Daniel Pett for inviting BM to present this work at the "Digital Heritage in a World of Big Data" conference at the University of Stirling, Scotland, May 2019.
+This conference was part of the AHRC-funded project 'Ancient Identities in Modern Britain' and the AHRC Heritage Priority Area Leadership Fellowship.
 
@@
 <div id="refs"></div>
-
-Kristiansen, K. 2014. “Towards a New Paradigm? the Third Science Revolution and Its Possible Consequences in Archaeology.” Current Swedish Archaeology 22: 11–34.
-
-##### pagebreak
 

### 2020-05-26 analysis/paper/002-Wikipedia-CS-WHL-world-map-counts.R

@@ -1,0 +1,137 @@
+library(tidyverse)
+
+## Here's a map of countries showing which has the most WP pages for WH sites
+library("rnaturalearth")
+library("rnaturalearthdata")
+world <-
+  ne_countries(scale = "medium", returnclass = "sf")
+
+page_data_for_all_pages <-
+  read_rds(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+
+# all WH sites, with and without WP pages (n = 846)
+wh_wiki_table <-
+  readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls"))
+
+# get country of site from location text
+# Laos, Czech Republic, Micronesia, Zimbabwe, South Sudan, Chad,
+# Central African Republic, Congo, Gabon, Cameroon, Nigeria, Bosnia and Herzegovina
+#  Cote d'Ivoire, Sierra Leone, Guyana, Belize,
+country_names <-  paste(c(world$name,
+                          "United States",
+                          "Czech Republic",
+                          "Antigua & Barbuda",
+                          "Saint Kitts and Nevis",
+                          "Lao"
+),
+collapse="|")
+
+page_data_for_all_pages_location <-
+  page_data_for_all_pages %>%
+  mutate(country = str_extract(Location,
+                               regex(country_names,
+                                     ignore.case=TRUE))) %>%
+  mutate(country = case_when(
+    country == "United States" ~ "United States of America",
+    country == "Czech Republic" ~ "Czechia",
+    country == "Antigua & Barbuda" ~ "Antigua and Barb.",
+    country == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
+    country == "Lao" ~ "Lao People's Democratic Republic",
+    TRUE ~ as.character(country)))
+
+
+wh_wiki_table_location <-
+  wh_wiki_table %>%
+  mutate(country = str_extract(states_name_en,
+                               regex(country_names,
+                                     ignore.case=TRUE))) %>%
+  mutate(country = case_when(
+    country == "United States" ~ "United States of America",
+    country == "Czech Republic" ~ "Czechia",
+    country == "Antigua & Barbuda" ~ "Antigua and Barb.",
+    country == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
+    country == "Lao" ~ "Lao PDR",
[…]

### 2020-05-28 analysis/paper/paper.Rmd
results section - talk pages

@@
 These studies indicate that inequalities on a range of variables mean that participation in online peer production communities often exacerbates existing patterns of social exclusion.
+@graham2014uneven examined the global distribution of 3.4 million geotagged Wikipedia articles and find a pattern of places in the Global North being represented in local languages, while articles about places in the Global South are largely being written by others.
+They find that most of the variation in the spatial distribution of geotagged articles could be explained by three variables: the population of the country, the number of fixed broadband connections, and the number of edits emanating from that country.
 
@@
 In Mali during 2012, fighting between government and rebel groups lead to the damage and destruction of tombs at the CS-WHL sites of Gao and Timbuktu [@brioschi2017discourses].
-The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are currently among the 53 sites on the List of World Heritage in Danger (https://whc.unesco.org/en/danger/).
+The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are currently among the 36 cultural sites on the List of World Heritage in Danger (https://whc.unesco.org/en/danger/).
 In 2015, ISIS militants destroyed the Temple of Bel in Palmyra, Syria (a CS-WML site of monumental ruins, once great city at the crossroads between east and west in the ancient world) [@gornik2015can].
@@
 We surveyed the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics).
+There are great many additional metrics available for Wikipedia articles, an we have limited ourselves to the most basic for this initial investigation.
 By comparing these basic characteristics of Wikipedia articles about CS-WHL to 10,000 random Wikipedia articles we will answer the question: how does engagement with the past compare via CS-WHL on Wikipedia compare to engagement with other topics?
@@
 We attempted to correct these manually in our code.
+Another challenge was in the formatting of tables, for example a merged cell in a table introduced an irregularity that made parsing and scraping complicated and fragile.
 We collected data during May 2019, and due to the dynamic nature of Wikipedia, it is highly likely that articles in our study have subtly changed since our data collection as users and bots continue their activity.
 It is unlikely that articles in our sample have been deleted from Wikipedia since our data collection, because of the high notability of CS-WHL, but it is possible that new articles have since appeared about sites that were not represented on Wikipedia since we collected the data.
+Our original scraping code may no longer work as the tables on Wikipedia articles continue to be modified.
 
@@
 
+```{r wh-wiki-cluster, fig.cap="Results of UMAP and HDBSCAN analysis to identify clusters of articles.
+Point colour indicates cluster membership.
+Inset plot shows variable loadings to show variables most influential on cluster membership", fig.width=15}
+rrtools:::quietly(source(here::here("analysis/paper/002-Wikipedia-umap-hdbscan.R")))
+knitr::include_graphics(here::here("analysis/figures/wh_country_umap_hdbscan.png"))
+```
+
+Of the `r nrow(wh_unesco)` cultural sites on the World Heritage List at the time of writing, we found Wikipedia articles for `r nrow(some_page_variables)`.
+To characterize the overall variability of article according to the basic characteristics described above, we applied a Uniform Manifold Approximation and Projection (UMAP) to reduce the dimensionality of our data [@mcinnes2018umap].
+After a two-dimensional projection was obtained, we used Hierarchical Density-Based Spatial Clustering of Applications with Noise (HDBSCAN) to identify clusters [@campello2013density], and Random Forests to identify variable loadings [@breiman2001random] so we could determine which of the basic characteristics were most important in driving variability between the articles.
+This revealed `r n_clusters` clusters, with the most important variables for determining cluster membership being the number of items in the reference list at the end of the article, the number of words in the article, and the number of Wikilinks out from the target article to other Wikipedia articles.
+That said, `r n_no_cluster` (`r round(prop_no_cluster) * 100`%) articles were not assigned to a cluster by the HDBSCAN algorithm, indicating that the basic characteristics of CS-WHL articles do not partition the articles in highly structured and discrete groups.
+
+```{r wh-wiki-content-and-consumption, fig.cap="Content and consumption of Wikipedia articles about CS-WHL.
+The top row of density plots show the distributions of basic content characteristics of Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey).
+The density plots on the lower left show basic characterstics of consumption.
+The lower right shows a scatterplot of consumption metrics for Wikipedia articles about CS-WHL and labels on the most intensively consumed articles", fig.width=15}
+source(here::here("analysis/paper/003-Wikipedia-random-basic-content.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic.png"))
+```
+
+As a group, the basic details of content for Wikipedia articles for CS-WHL differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+The scholarly nature of the articles, measured by the number of sources cited in the reference list per thousand words in the article body, is similar for CS-WHL articles and random articles.
+The number of Wikilinks out from the target article to other Wikipedia articles is also similar for CS-WHL articles and random articles.
+However, the total number of words in a CS-WHL article is typically much higher than a random article.
+
+The basic metrics of consumption of CS-WHL articles show substantial differences from our sample of random articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+We measure consumption by counting the total number of views of the article over the 100 days prior to our data collection date, and the the number of Wikilinks from other articles into the target article.
+Wikipedia article view counts are popular widely-used measures of cultural interest or salience [@roll2016using; @cao2020analysis; @mciver2014wikipedia].
+Wikilinks from other articles are a measure of the centrality of an article, if many other articles link to it, then the article is well-integrated into the encyclopedia and viewed as important for supporting information presented in other articles.
+CS-WHL articles are typically viewed far more frequently than other Wikipedia articles, reflecting high consumption by internet users generally.
+They are also much more often linked to by other Wikipedia articles than our random sample of other articles, indicating consumption by other Wikipedia articles and Wikipedia users in their editing work (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+This indicates that consumption of CS-WHL articles is generally very high.
+But is this attention evenly distributed across all CS-WHL articles?
+
+```{r}
+timbuktu_talk_page_word_count <- 
+  page_data_for_all_pages %>%  
+  filter(str_detect(Site, "Timb")) %>% 
+  pull(talk_page_wordcount)
+```
+
+The scatterplot on the lower right of Figure \@ref(fig:wh-wiki-content-and-consumption) shows the values of inward Wikilinks, article views and article word count for all CS-WHL articles.
+The labeled points in the upper right quadrant are the articles that receive most of the attention.
+Of the CS-WHL notable for conflict discussed above, only Timbuktu is visible among these highly popular articles.
+It is also the only site on the List of World Heritage in Danger that is among these highly popular articles.
+We reviewed the talk page for the Timbuktu article to determine if the attention received by the article might relate to the issues leading to armed conflict at the site.
+Of the `r timbuktu_talk_page_word_count` word on the talk page, only 168 are on the topic of conflict and destruction, with the editors discussing how to describe the scale of the damage to the temples.
+The majority of talk page content is about filling in missing detail, suggestions for or notifications of minor corrections.
+This is also the case for the talk page for Auschwitz, another very popular CS-WHL article.
+Although Wikipedia articles on this site in other languages have different points of emphasis [@wolniewicz2016framing], the discussion among editors is generally technical and precise, and provocative comments usually ignored rather than directly disputed.
+This can be contrasted with the talk page for the Holocaust, where @pfanzelter2015crossroads found abundant evidence of conflict among editors.
+
+```{r wh-wiki-production, fig.cap="Production of Wikipedia articles about CS-WHL.
+The top row of density plots show the distributions of basic article production characteristics of Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey).
+The density plots on the lower left show the distribution of edits made by bots.
+The lower right shows a scatterplot of production-by-bot metrics for Wikipedia articles about CS-WHL and includes labels on the articles where bots were responsible for >30% of edits.
+Inset on the scatterplot shows the number of edits for the top ten bots in our sample.", fig.width=15}
+source(here::here("analysis/paper/004-Wikipedia-random-production.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_production.png"))
+```
+
+Basic variables related to the production of Wikipedia articles on CS-WHL differ in key ways from other articles (Figure \@ref(fig:wh-wiki-production)).
+The number of edits per thousand words, or edit density, and the number of unique editors per thousand words, or editor density, are substantially higher for CS-WHL articles.
+CS-WHL articles are intensively word-smithed by a more diverse community of editors than usual.
+The absolute size of edits (i.e.
+additions or removals of text) is about the same for CS-WHL articles as other articles.
+The involvement of bots in producing CS-WHL articles is also about the same as for other articles.
+Bot activity is most intense on shorter, low-profile CS-WHL articles, in Figure \@ref(fig:wh-wiki-production) the labeled points are sites where bots have done >30% of edits.
+Most of these bot edits are in the fixer, tagger, connector, and clerk roles.
+None of these articles with intensive bot activity are CS-WHL sites of conflict or on the List of World Heritage in Danger.
+The most active bot on CS-WHL articles is Cluebot NG (vandalism detection and reverting), compared to Cydebot (automatic implementation of category deletions) for the random articles.
+The AnomieBOT is very active on CS-WHL articles compared to random articles, this bot performs clerical duties in an article's reference list.
+
+```{r wh-wiki-vandal-revert, fig.cap="Reverted edits and edits about vandalism in Wikipedia articles about CS-WHL.
+The top row of density plots show the distributions of proportions of edits relating to vandalism, and the proportion of revert edits in Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey).
+The scatterplots below show reverted edits and edits about vandalism metrics for Wikipedia articles about CS-WHL, and includes labels on the articles with high proportions of these types of edits.", fig.width=15}
+source(here::here("analysis/paper/005-Wikipedia-WHL-reverts-vandalism.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_vandals_reverts.png"))
+```
+
+For the special 'revert' edit type, we see that the proportion of all edits per  CS-WHL articles is similar to other articles, but has a left-skewed distribution indicating a higher number of articles that have very few revert edits (Figure \@ref(fig:wh-wiki-vandal-revert)).
+We also identified edits with the string 'vandal' in the edit summary as a similar type of edit to the revert edit, e.g.
+"Edits by 72.49.241.71 identified as vandalism".
+CS-WHL articles generally have fewer edits about vandalism than our random sample.
+The shape of the distribution of edits about vandalism has a smaller second mode to the left of the peak, indicating that a large number of CS-WHL articles have very few edits about vandalism (Figure \@ref(fig:wh-wiki-vandal-revert)).
+Among the CS-WHL articles that have high proportions of reverts and edits about vandalism are highly iconic sites in the Western canon of culture history, e.g.
+the Sydney Opera House, the Tower of London, and the Statue of Liberty.
+In reviewing a sample of several hundred reverted edits for each of these, we found that nearly all of them are undoing the addition of short strings of text (e.g.
+profanities, spam, nonsense).
+Much of this vandalism is playful, in the spirit of "'I am', a statement that one is present and alive", as @baker2003red described historical graffiti on the Reichstag in Germany by Russian soldiers in WW2.
+Once again, of the CS-WHL sites with a history of conflict or on the in-danger list, only Timbuktu appears here as having high proportions of revert and vandalism-reversing edits.
+
+```{r wh-wiki-talk-pages, fig.cap="Scatterplot showing the length of each CS-WHL article and the length of each article's talk page.
+Labelled points are articles where the talk page is longer than the article.
+Inset shows the distribution of talk page lengths for CS-WHL articles and 10,000 random articles", fig.width=15}
+source(here::here("analysis/paper/006-Wikipedia-WHL-talk-pages.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_talk_pages.png"))
+```
+
+Talk pages are another location where we may see conflicts and debates unfold on Wikipedia.
+Wikipedia talk pages are a popular subject of investigations to understand the collaborative generation of knowledge and online conflict management [@ho2016french; @ho2017exploring; @schneider2012content; @kittur2007he].
+The length of an article's talk page is correlated with the controversality of the article, and thus an effective simple proxy for conflict [@yasseri2012dynamics].
+We counted the words on all talk pages of the CS-WHL articles to identify conflict (Figure  \@ref(fig:wh-wiki-talk-pages)).
+Talk pages for CS-WHL articles tend to be much longer than other articles, which we expect due to the CS-WHL articles themselves being generally longer than other articles.
+However, the distribution of talk page lengths for CS-WHL articles has a long right tail, indicating that a higher number of articles have very long talk pages, compared to other articles.
+While it is true that some of these articles with long talk pages, such as Cologne Cathedral and Troy, have clear evidence of conflict among the editors, close reading of the discussions reveals that the debates are dominated by technical issues.
+For example, the Cologne Cathedral talk page includes some debate about the correct calculation of the interior volume of the structure, and on the Troy talk page there is a heated comments by one editor about another editor removing of some of their text containing unsourced claims and unencyclopedic writing style.
+
+Only one of the controversial sites discussed above is in the group of articles where the talk page is longer than the article itself, and none of the site on the UNESCO heritage in danger list are in this group.
+The talk page for Mapungubwe is lengthy with expressions of concern about the accuracy of information in the article.
+In particular, editors were concerned about the depiction of Indigenous people, especially the degree to which early European colonists were aware of Indigenous communities, and the correct cultural affiliation of the Indigenous groups that originally occupied the site.
+Although not notable for the length of its talk page, the discussions among editors of the article about Preah Vihear Temple
+
 ```{r wh-wiki-map, fig.cap="Wikipedia articles for Cultural Sites on the UNESCO World Heritage List.
@@
 
-Of the `r nrow(wh_unesco)` cultural sites on the World Heritage List at the time of writing, we found Wikipedia articles for `r sum(wh_wk_country_counts$n)`.
-To characterize the overall variability of article according to the basic characteristics described above, we applied a Uniform Manifold Approximation and Projection (UMAP) to reduce the dimensionality of our data.
-After a two-dimensional projection was obtained, we used Hierarchical Density-Based Spatial Clustering of Applications with Noise (HDBSCAN) to identify clusters, and Random Forests to identify variable loadings so we could determine which of the basic characteristics were most important in driving variability between the articles.
-
 Figure \@ref(fig:wh-wiki-map) shows that most countries have between 2-3 CS-WHL on Wikipedia, with Germany, India, China, France and Spain being the countries with the most articles about their CS-WHL.
@@
 # Discussion
+
+Come back to danger list [@brown2019politics; @holleland2019naming]
+
+Sites where the conflict is international have it show on WP
 

### 2020-05-28 analysis/paper/002-Wikipedia-umap-hdbscan.R

@@ -1,0 +1,164 @@
+library(tidyverse)
+
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+  page_data_for_all_pages <-
+    readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
+
+theme_nogrid <- function (base_size = 12, base_family = "") {
+  theme_bw(base_size = base_size,
+           base_family = base_family) %+replace%
+    theme(panel.grid = element_blank() )
+}
+
+
+## Overall clusters
+
+normalize = function(x) (x-min(x))/(max(x)-min(x))
+
+#--------------------------------------------------------------------------
+# take a look at the distribution of page variables
+some_page_variables <-
+  page_data_for_all_pages %>%
+  select(page_wordcount,
+         page_wikilinks_out,
+         page_wikilinks_in,
+         page_cited_items_on) %>%
+  mutate(page_wikilinks_out_per_word = page_wikilinks_out / page_wordcount,
+         page_cited_items_on_per_word = page_cited_items_on / page_wordcount)
+
+
+
+# umap
+library(uwot)
+library("tmap")
+data("World")
+
+pages_umap_input <-
+  some_page_variables  %>%
+  mutate(page_wordcount_norm = normalize(page_wordcount),
+         page_wikilinks_in_norm= normalize(page_wikilinks_in),
+         page_wikilinks_out_per_word_norm = normalize(page_wikilinks_out_per_word),
+         page_cited_items_on_per_word_norm = normalize(page_cited_items_on_per_word)) %>%
+  select(-page_wordcount,
+         -page_cited_items_on,
+         -page_wikilinks_out,
+         -page_wikilinks_in,
+         -page_wikilinks_out_per_word,
+         -page_cited_items_on_per_word) %>%
+  bind_cols(., page_data_for_all_pages[ , 'country'] ) %>%
+  filter_all(all_vars(!is.na(.))) %>%
+  left_join(World %>%
+              select(name, continent),
+            by = c('country' = 'name'))
+
+# compute umap
+
+pages_umap_input_selected <-
+  pages_umap_input %>%
+  select(-country,
+         -continent,
+         -geometry
+  )
+
+pages_umap_output <-
+  pages_umap_input_selected %>%
+  umap(.,
+       n_neighbors = 60,
+       min_dist = 0.7,
[…]

### 2020-05-28 analysis/paper/003-Wikipedia-random-basic-content.R

@@ -1,0 +1,211 @@
+## Basic qualities of the content of WP articles about WH sites
+
+# load the random pages
+if(!exists("ten_k_random_wp_pages")){
+ten_k_random_wp_pages <-
+  readRDS(here::here("analysis/data/raw_data/random_page_data_tbl.rds"))
+}
+
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+  page_data_for_all_pages <-
+    readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
+
+# load the random pages revision histories
+if(!exists("ten_k_random_wp_pages_lst")){
+  ten_k_random_wp_pages_lst <-
+    readRDS(here::here("analysis/data/raw_data/random_page_data_lst.rds"))
+}
+
+if(!exists("wh_unesco_danger")){
+  wh_unesco_danger <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+    filter(category %in% c("Cultural")) %>%
+    filter(danger == 1)
+}
+
+ten_k_random_wp_pages_basic_qualities <-
+  ten_k_random_wp_pages %>%
+  select(page_wordcount,
+         page_wikilinks_out,
+         page_cited_items_on) %>%
+  mutate(rnd_page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
+         rnd_page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000,
+         rnd_page_wordcount = page_wordcount) %>%
+  select(-page_wikilinks_out,
+         -page_cited_items_on,
+         -page_wordcount)
+
+ten_k_random_wp_pages_basic_qualities_long <-
+  ten_k_random_wp_pages_basic_qualities %>%
+  gather(variable, value)
+
+page_data_for_all_pages_basic_qualities <-
+  page_data_for_all_pages %>%
+  select(page_wordcount,
+         page_wikilinks_out,
+         page_cited_items_on) %>%
+  mutate(page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
+         page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000) %>%
+  select(-page_wikilinks_out,
+         -page_cited_items_on)
+
+page_data_for_all_pages_basic_qualities_long <-
[…]

### 2020-05-28 analysis/paper/004-Wikipedia-random-production.R

@@ -1,0 +1,369 @@
+## Basic qualities of the editing process of WP articles about WH sites
+
+# number of edits, total, edit density (prop/words), size of edits
+# how many bot edits, how many reverts per page
+# diversity of editors
+
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+  page_data_for_all_pages <-
+    readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
+
+# load the random pages revision histories
+if(!exists("ten_k_random_wp_pages_lst")){
+  ten_k_random_wp_pages_lst <-
+    readRDS(here::here("analysis/data/raw_data/random_page_data_lst.rds"))
+}
+
+if(!exists("wh_unesco_danger")){
+  wh_unesco_danger <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+    filter(category %in% c("Cultural")) %>%
+    filter(danger == 1)
+}
+
+
+# wh sites on wp
+revision_history_page_details <-
+  tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t,
+                                             ~.x$revision_history_page_details)) %>%
+  mutate(Site =         page_data_for_all_pages$Site,
+         Country =      page_data_for_all_pages$country,
+         rh_n_editors = map_int(revision_history_page_details, ~n_distinct(.x$rh_user)),
+         rh_n_edits =   map_int(revision_history_page_details, ~nrow(.x)),
+         rh_user_simpson_idx = page_data_for_all_pages$rh_user_simpson_idx,
+         rh_user_bot_prop = page_data_for_all_pages$rh_user_bot_prop,
+         rh_revert_prop = page_data_for_all_pages$rh_revert_prop)
+
+# random sites
+
+ten_k_random_wp_pages_revision_history_page_details <-
+  map_df(ten_k_random_wp_pages_lst,
+         ~.x$revision_history_page_details,
+         .id = 'Site')
+
+# very slow!
+ten_k_random_wp_pages_revision_history_page_details_summary_tbl <-
+  ten_k_random_wp_pages_revision_history_page_details %>%
+  mutate(Site = as.numeric(Site)) %>%
+  group_by(Site) %>%
+  summarise(
+    rh_n_editors = n_distinct(rh_user),
+    rh_n_edits =   n(),
+    rh_n_bot_edits = sum(bot),
[…]

### 2020-05-28 analysis/paper/005-Wikipedia-WHL-reverts-vandalism.R

@@ -1,0 +1,220 @@
+
+## So about vandalism? do WH sites get more than random ones?
+
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+page_data_for_all_pages <-
+  readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
+
+# load the random pages revision histories
+if(!exists("ten_k_random_wp_pages_lst")){
+ten_k_random_wp_pages_lst <-
+  readRDS(here::here("analysis/data/raw_data/random_page_data_lst.rds"))
+}
+
+if(!exists("wh_unesco_danger")){
+wh_unesco_danger <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+  filter(category %in% c("Cultural")) %>%
+  filter(danger == 1)
+}
+
+page_data_for_all_pages_rh_tbl <-
+  map_df(page_data_for_all_pages$page_info_t,
+         ~.x$revision_history_page_details, .id = "Site")
+
+ten_k_random_wp_pages_revision_history_page_details <-
+  map_df(ten_k_random_wp_pages_lst,
+         ~.x$revision_history_page_details,
+         .id = 'Site')
+
+# edits containing the word 'vandal'
+edits_with_vandal_plot <-
+bind_rows(
+  page_data_for_all_pages_rh_tbl %>%
+    mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
+    group_by(Site) %>%
+    summarise( n_vandal_edits = sum(vandalism),
+               n_edits = n()) %>%
+    mutate(prop_vandal_edits = n_vandal_edits / n_edits,
+           Site = "World Heritage Sites"),
+
+  ten_k_random_wp_pages_revision_history_page_details %>%
+    mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
+    group_by(Site) %>%
+    summarise( n_vandal_edits = sum(vandalism),
+               n_edits = n()) %>%
+    mutate(prop_vandal_edits = n_vandal_edits / n_edits,
+           Site = "Random pages")
+) %>%
+
+  ggplot(aes(prop_vandal_edits,
+             fill = Site)) +
+  geom_density(alpha = 0.4) +
+  scale_x_log10() +
+  guides(fill = FALSE) +
+  scale_fill_viridis_d(labels = c("Random",
+                                  "World Heritage"),
+                       option = "A") +
[…]

### 2020-05-28 analysis/paper/006-Wikipedia-WHL-talk-pages.R

@@ -1,0 +1,333 @@
+## What's the typical distribution of talk page length?
+
+
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+  page_data_for_all_pages <-
+    readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
+
+# load the random pages revision histories
+if(!exists("ten_k_random_wp_pages_lst")){
+  ten_k_random_wp_pages_lst <-
+    readRDS(here::here("analysis/data/raw_data/random_page_data_lst.rds"))
+}
+
+# load the random pages
+if(!exists("ten_k_random_wp_pages")){
+  ten_k_random_wp_pages <-
+    readRDS(here::here("analysis/data/raw_data/random_page_data_tbl.rds"))
+}
+
+# the talk pages for all WH sites, with WP pages
+if(!exists("wh_wiki_talk_pages")){
+wh_wiki_talk_pages <-
+  readRDS(here::here("analysis/data/raw_data/wh_wiki_table_talk_page_content.rds"))
+}
+
+if(!exists("wh_wiki_table")){
+wh_wiki_table <-
+  readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+  filter(category %in% c("Cultural"))
+}
+
+if(!exists("wh_unesco_danger")){
+  wh_unesco_danger <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+    filter(category %in% c("Cultural")) %>%
+    filter(danger == 1)
+}
+
+talk_page_word_count_distribution_plot <-
+bind_rows(
+
+  ten_k_random_wp_pages %>%
+    select(talk_page_wordcount) %>%
+    mutate(Site = "Random pages"),
+
+  page_data_for_all_pages %>%
+    select(talk_page_wordcount) %>%
+    mutate(Site = "World Heritage pages")
+) %>%
+
+  ggplot(aes(talk_page_wordcount,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  labs(title = "Talk page word count",
+       x = "",
+       y = "") +
+  guides(fill = FALSE) +
+  scale_x_log10(label = scales::label_number_si()) +
+  scale_fill_viridis_d(labels = c("Random",
+                                  "World Heritage"),
+                       option = "A") +
+  theme_bw(base_size = 6) +
+  theme(plot.title = element_text(hjust = 0.5)) +
+  NULL
+
+
[…]

### 2020-05-30 analysis/paper/paper.Rmd
starting discussion

@@
 In particular, editors were concerned about the depiction of Indigenous people, especially the degree to which early European colonists were aware of Indigenous communities, and the correct cultural affiliation of the Indigenous groups that originally occupied the site.
-Although not notable for the length of its talk page, the discussions among editors of the article about Preah Vihear Temple
+Although not notable for the length of its talk page, the discussions among editors of the article about Preah Vihear Temple include a strongly worded disagreement among seven editors about the legitimacy of the ownership claims by Thailand and Cambodia of the territory that includes the temple.
+The debate among Wikipedia editors mirrors very closely the political tensions surrounding the nomination of Preah Vihear.
+The talk page also has a much longer argument, mostly between two editors, about whether or not the Thai name of the site should be included in the text of the article.
+This debate also recapitiulates issues of which country has the stronger claim for ownership of the temple.
+Amid accusations of nationalism among the editors, one of them asks "Can we put aside politics and be more collaborative on the encyclopedia project?" and appeals to Wikipedia policies 'Third opinion' and 'Dispute resolution' to diffuse the tensions and refocus attention on the common goal.
+Beyond these two pages we found that the majority of content on CS-WHL article talk pages is about highly local topics, mostly article administration, editing processes, and quality control.
 
@@
 
+```{r wh-wiki-circle, fig.cap="Flow of edits by location on Wikipedia for articles about Cultural Sites on the UNESCO World Heritage List.
+The arrows indicate the country where the editor is location (arrow nock or start) and the location of the CS-WHL site that they are editing the article of (arrow point or end).
+Editor locations were determined by geo-locating the IP addresses associated with anonymous edits.
+Inset shows the distribution of proportions of edits per article that are anonymous.
+Non-anonymous edits are identitifed by Wikipedia usernames, rather than IP addresses, and cannot be geo-located.", fig.width=15}
+source(here::here("analysis/paper/007-Wikipedia-WHL-spatial-circle-plot.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_countries_circle_chord_fig.png"))
+```
+
+Spatial patterns in the coverage of CS-WHL sites on Wikipedia closely resemble the physical distribution of sites.
 Figure \@ref(fig:wh-wiki-map) shows that most countries have between 2-3 CS-WHL on Wikipedia, with Germany, India, China, France and Spain being the countries with the most articles about their CS-WHL.
+This pattern is consistent with @graham2014uneven's observations that places in the Global North tend to be over-represented on Wikipedia.
+More surprising is the distribution of editor locations shown in figure \@ref(fig:wh-wiki-circle), which we determined by geo-locating the IP addresses attached to each anonymous edit on all CS-WHL articles.
+This figure shows the flow of edits, with the arrows starting at the country where the editor was located when they made their edit, and ending at the country where the CS-WHL site that they are editing is located.
+The inset plot on figure \@ref(fig:wh-wiki-circle) shows that this visualisation only accounts for a relatively small proportion of all edits to CS-WHL articles.
+Around 20% of edits of most CS-WHL articles are anonymous, a higher proportion than our random sample.
+Nevertheless, there are `r prettyNum(nrow(revision_history_page_details_ip_addresses_df), big.mark=",")` anonymous edits, and so this sample likely contains a non-random signal.
+The most striking detail in figure \@ref(fig:wh-wiki-circle) is the large proportion of edits that originate in the United States, and that the vast majority of these are edits of articles about CS-WHL sites located elsewhere in the world.
+The country with the next largest proportion, the United Kingdom, is less than half of the United States, and a much greater proportion of edits originating in the UK are on articles about CS-WHL sites located in the UK, compared to the US.
+The country with the next highest proportion of editors is India, and nearly half of those edits are on CS-WHL sites located India.
+The majority of countries in this chord diagram indicate that articles about CS-WHL sites in those countries receive edits from editors located elsewhere, mostly the US and other English-speaking countries.
+
+```{r wh-wiki-time1, fig.cap="...", fig.width=15}
+source(here::here("analysis/paper/008-Wikipedia-WHL-time-series.R"))
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_time_inscription.png"))
+```
+
+```{r wh-wiki-time2, fig.cap="...", fig.width=15}
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_time_series_facet.png"))
+```
+
+Time series analysis of edits on articles about CS-WHL sites can help us identify relationships between activity on Wikipedia articles and external events related to the sites.
+Figure \@ref(fig:wh-wiki-time1) shows that most articles about CS-WHL sites are much older than articles in our random sample, with most CS-WHL articles created 5-10 years after Wikipedia first appeared in 2001.
+This rapid addition of articles early in the life of Wikipedia supports the observation from the in-bound Wikilinks data that articles about CS-WHL sites are more central to the encyclopedia and considered worthy of inclusion than many other types of articles.
+The distribution of years between the date of a site's inscription on the WHL and the date of the creation of that site's Wikipedia article has a distinctive trimodal shape.
+The first two modes reflect the relatively large number of sites inscribed on the WHL in 1983 and the early 1990s.
+The third mode at the zero point on the horizontal axis corresponds to articles that were created in or around the year the CS-WHL site was inscribed on the list.
+These are sites inscribed after the creation of Wikipedia in 2001.
+Only a relatively small proportion of CS-WHL sites had Wikipedia articles created about them before they were inscribed on the WHL, because the majority of sites were inscribed before Wikipedia was created.
+The time series of editing activity at individual sites are highly variable and show display complex patterns (Figure \@ref(fig:wh-wiki-time2)).
+Timbuktu shows spikes of activity right after attacks in mid June 2012, with descriptions of the attacks added to the text of the article.
+However the tallest peak in editing activity on the Timbuktu occurs earlier, in April 2012 that  concentrated on expanding .
+A detailed analysis of these is beyond the scope of this paper, but we can see several patterns that suggestion interesting relationships between editorial activity and WHL listing.
+For example, editing activity spiking sharply at the time of WHL inscription (e.g.
+Tyre, Masada), editorial activity spiking at the time of WHL inscription and slowly decaying to a baseline level (e.g.
+Carthage), editorial activity that peaks shortly after the time of WHL inscription (e.g.
+Troy, Masada), and many sites where editorial activity that shows no signal at all at the time of WHL inscription (Figure \@ref(fig:wh-wiki-time2)).
 
@@
 Sites where the conflict is international have it show on WP
+
+https://en.wikipedia.org/wiki/Wikipedia:Geopolitical,_ethnic,_and_religious_conflicts_noticeboard now defunct
 

### 2020-05-30 analysis/paper/002-Wikipedia-CS-WHL-world-map-counts.R

@@ -6,12 +6,17 @@ library("rnaturalearthdata")
 world <-
   ne_countries(scale = "medium", returnclass = "sf")
 
-page_data_for_all_pages <-
-  read_rds(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+  page_data_for_all_pages <-
+    readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
 
 # all WH sites, with and without WP pages (n = 846)
+if(!exists("wh_wiki_table")){
 wh_wiki_table <-
   readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls"))
+}
 
 # get country of site from location text
 # Laos, Czech Republic, Micronesia, Zimbabwe, South Sudan, Chad,
@@ -80,8 +85,9 @@ wh_wk_country_counts_hist <-
          aes(n)) +
   geom_histogram() +
   annotate("text", x = 15, y = 30,
-           label = str_glue('Median = {median_number_wp_pages_per_country} WP pages/country\nMode = {mode_number_wp_pages_per_country} WP pages/country'),
+           label = str_glue('Median = {median_number_wp_pages_per_country} WP articles/country\nMode = {mode_number_wp_pages_per_country} WP articles/country'),
            size = 2) +
+  labs(x = "Number of CS-WHL articles") +
   theme_nogrid(12)
 
 wh_wk_country_counts_bar <-

### 2020-05-30 analysis/paper/007-Wikipedia-WHL-spatial-circle-plot.R

@@ -1,0 +1,233 @@
+
+# Spatial patterns
+
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+  page_data_for_all_pages <-
+    readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
+
+# load the random pages revision histories
+if(!exists("ten_k_random_wp_pages_lst")){
+  ten_k_random_wp_pages_lst <-
+    readRDS(here::here("analysis/data/raw_data/random_page_data_lst.rds"))
+}
+
+if(!exists("wh_unesco_danger")){
+  wh_unesco_danger <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+    filter(category %in% c("Cultural")) %>%
+    filter(danger == 1)
+}
+
+# all WH sites, with and without WP pages (n = 846)
+if(!exists("wh_wiki_table")){
+  wh_wiki_table <-
+    readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls"))
+}
+
+## IP addresses
+
+
+ip_regex <- "(?(?=.*?(\\d+\\.\\d+\\.\\d+\\.\\d+).*?)(\\1|))"
+
+get_ip_addresses <- function(x){
+  re <- regexpr(
+    ip_regex,
+    x, perl = TRUE)
+  regmatches(x, re)
+}
+
+# get locations from IP addresses
+library(rgeolocate)
+ip_db <- system.file("extdata","GeoLite2-Country.mmdb", package = "rgeolocate")
+
+# How many IP edits on each page?
+
+# analyse the countries of IP address vs country of WH site
+# wh sites on wp
+revision_history_page_details <-
+  tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t,
+                                             ~.x$revision_history_page_details)) %>%
+  mutate(Site =         page_data_for_all_pages$Site,
+         Country =      page_data_for_all_pages$country,
+         rh_n_editors = map_int(revision_history_page_details, ~n_distinct(.x$rh_user)),
+         rh_n_edits =   map_int(revision_history_page_details, ~nrow(.x)),
+         rh_user_simpson_idx = page_data_for_all_pages$rh_user_simpson_idx,
+         rh_user_bot_prop = page_data_for_all_pages$rh_user_bot_prop,
+         rh_revert_prop = page_data_for_all_pages$rh_revert_prop)
+
[…]

### 2020-05-30 analysis/paper/008-Wikipedia-WHL-time-series.R

@@ -1,0 +1,218 @@
+library(tidyverse)
+## Temporal patterns
+
+# all WH sites with WP pages (n = 584)
+if(!exists("page_data_for_all_pages")){
+  page_data_for_all_pages <-
+    readRDS(here::here("analysis/data/raw_data/page_data_for_all_pages.rds"))
+}
+
+# load the random pages revision histories
+if(!exists("ten_k_random_wp_pages_lst")){
+  ten_k_random_wp_pages_lst <-
+    readRDS(here::here("analysis/data/raw_data/random_page_data_lst.rds"))
+}
+
+if(!exists("wh_unesco_danger")){
+  wh_unesco_danger <- readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls")) %>%
+    filter(category %in% c("Cultural")) %>%
+    filter(danger == 1)
+}
+
+# all WH sites, with and without WP pages (n = 846)
+if(!exists("wh_wiki_table")){
+  wh_wiki_table <-
+    readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls"))
+}
+
+## Page ages: are WH pages younger than the typical WP page? What's their relationship to their inscription year?
+
+page_data_for_all_pages_rh_tbl <-
+  map_df(page_data_for_all_pages$page_info_t,
+         ~.x$revision_history_page_details, .id = "Site")
+
+randoms_revision_history_page_details <-
+  map_df(ten_k_random_wp_pages_lst,
+         ~.x$revision_history_page_details,
+         .id = "page")
+
+# get first and last edit, and inscription year
+library(lubridate)
+page_data_for_all_pages_rh_tbl_edit_start_end_span <-
+  page_data_for_all_pages_rh_tbl %>%
+  group_by(Site) %>%
+  summarise(first_edit_date = min(rh_date),
+            last_edit_date = max(rh_date),
+            edit_span = last_edit_date - first_edit_date) %>%
+  mutate(Site = as.numeric(Site)) %>%
+  arrange(Site) %>%
+  bind_cols(page_data_for_all_pages) %>%
+  mutate(inscription_year = as.Date(ISOdate(Year_num, 1, 1))) %>%
+  mutate(diff_first_edit_inscription_year = as.numeric( as.POSIXlt(inscription_year) - ymd_hms(first_edit_date) ) / 365 )
+
+page_data_for_random_rh_tbl_edit_start_end_span <-
[…]

### 2020-05-31 analysis/paper/999-code-for-the-Stirling-ppt.Rmd
results section - talk pages
finished conclusion

@@
 
-# all WH sites, with and without WP pages (n = 846)
 wh_wiki_table <-
@@
   wh_wiki_table %>%
-  mutate(country = str_extract(Location,
+  mutate(country = str_extract(states_name_en, # Location,
                                  regex(country_names,

### 2020-05-31 analysis/paper/paper.Rmd
finished conclusion

@@
 ---
-title: "World Heritage Sites on Wikipedia: Inscription Controversies in a Context of Constrained Agency for Cultural Heritage Activism"
+title: "World Heritage Sites on Wikipedia: Controversies in a Context of Constrained Agency for Cultural Heritage Activism"
 author:
@@
 On the other hand, they constrain and limit the agency of the user, canalizing their behaviour into a small number of possible actions and acceptable modes of discourse and engagement with other users [@iba2010analyzing].
-While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity, resulting in very specific types of relationships between human users and the technical elements of the Wikipedia project [@niederer2010wisdom].
+While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity, resulting in very specific types of relationships between human users and the technical elements of the Wikipedia project [@niederer2010wisdom; @weltevrede2016platform].
 For example, every edit to an article is tracked in a publicly accessible version control system attached to that article.
@@
 Wikipedia bots are computer scripts that automatically handle repetitive and mundane tasks to develop, improve, and maintain the encyclopedia.
-While bots are not unique to Wikipedia, they are important contributors, responsible for a large proportion of edits, and shape the human experience in significant ways [@niederer2010wisdom' @geiger2009social; @geiger2014bots].
+While bots are not unique to Wikipedia, they are important contributors, responsible for a large proportion of edits, and shape the human experience in significant ways [@niederer2010wisdom; @geiger2009social; @geiger2014bots].
 They also evolve and autonomously engage in complex interactions with other bots to modify the encyclopedia [@tsvetkova2017even; @geiger2017operationalizing].
@@
 We used the SelectorGadget [@cantino2017selectorgadget] extension for the Chrome web browser to identify specific elements of interest, or nodes, on the HTML pages, and wrote custom R functions to extract data from these nodes.
+Our entry points were the Wikipedia articles that are lists of World Heritage regions in major geographical regions of the globe.
+We found fifteen of these, and scraped the CS-WHL site names from the tables on these pages, and followed the links to scrape the article text, edit history and talk page text for each CS-WHL site included on those tables.
+A small number of CS-WHL sites have Wikipedia articles that are not included on these tables, we did not include these in our sample.
+We chose this approach because the Wikipedia article titles for CS-WHL sites often differ from the official site name on the UNESCO list, making manual look-ups very inefficient.
+
 The highly structured nature of most Wikipedia pages afforded us much efficiency during data collection, however, a not insignificant number of pages had minor irregularities, for example, exotic table formatting or minor deviations from widely used templates, that necessitated more complex programming.
@@
 In particular, editors were concerned about the depiction of Indigenous people, especially the degree to which early European colonists were aware of Indigenous communities, and the correct cultural affiliation of the Indigenous groups that originally occupied the site.
+These issues closely echo the themes identified by @meskell2011paris in her analysis of the WHC process.
 Although not notable for the length of its talk page, the discussions among editors of the article about Preah Vihear Temple include a strongly worded disagreement among seven editors about the legitimacy of the ownership claims by Thailand and Cambodia of the territory that includes the temple.
@@
 ```{r wh-wiki-map, fig.cap="Wikipedia articles for Cultural Sites on the UNESCO World Heritage List.
-Countries coloured black currently have no Wikipedia articles for CS-WHL sites.
-Inset shows the distribution of articles per country.
+Upper panel shows the total number of Wikipedia articles for CS-WHL sites per country.
+Lower panel is the proportion of all CS-WHL sites that have Wikipedia articles per country.
+Inset shows the distribution of numbers of CS-WHL articles per country.
 Map data from naturalearthdata.com", fig.width=15}
 source(here::here("analysis/paper/002-Wikipedia-CS-WHL-world-map-counts.R"))
-knitr::include_graphics(here::here("analysis/figures/wh_country_wikipedia_count_map.png"))
+knitr::include_graphics(here::here("analysis/figures/wh_country_wikipedia_count_prop_map.png"))
 ```
@@
 This pattern is consistent with @graham2014uneven's observations that places in the Global North tend to be over-represented on Wikipedia.
+The lower panel of figure \@ref(fig:wh-wiki-map) further demontrates this with South American countries having low proportions of their CS-WHL sites represented on Wikipedia.
+The pattern in African countries is that they either have a very small number of sites that are all on Wikipedia (indicated by yellow on the figure), or they do not have any CS-WHL at all.
 More surprising is the distribution of editor locations shown in figure \@ref(fig:wh-wiki-circle), which we determined by geo-locating the IP addresses attached to each anonymous edit on all CS-WHL articles.
@@
 
-```{r wh-wiki-time1, fig.cap="...", fig.width=15}
+```{r wh-wiki-time1, fig.cap="Article editing relative to WHL inscription date.
+Upper panel is a histogram of WHL inscription years.
+Lower panel is a histogram of duration between inscription and the appearance of the Wikipedia article.
+Inset shows the distribution of CS-WHL article ages and ages of random sites.", fig.width=15}
 source(here::here("analysis/paper/008-Wikipedia-WHL-time-series.R"))
@@
 
-```{r wh-wiki-time2, fig.cap="...", fig.width=15}
+```{r wh-wiki-time2, fig.cap="Time series of editing activity for CS-WHL articles for all sites inscribed after Wikipedia began in 2001, and with a minimum of 150 edits in total", fig.width=15}
 knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_time_series_facet.png"))
@@
 The time series of editing activity at individual sites are highly variable and show display complex patterns (Figure \@ref(fig:wh-wiki-time2)).
-Timbuktu shows spikes of activity right after attacks in mid June 2012, with descriptions of the attacks added to the text of the article.
-However the tallest peak in editing activity on the Timbuktu occurs earlier, in April 2012 that  concentrated on expanding .
-A detailed analysis of these is beyond the scope of this paper, but we can see several patterns that suggestion interesting relationships between editorial activity and WHL listing.
+Timbuktu shows spikes of editing activity right after the rebel attacks in mid June 2012, with descriptions of the attacks added to the text of the article at that time.
+However the tallest peak in editing activity on the Timbuktu occurs earlier, in April 2012, those edits concentrated on expanding the sections on local prehistory.
+A detailed analysis of all the article-specific time series is beyond the scope of this paper, but we can see several patterns that suggestion interesting relationships between editorial activity and WHL listing.
 For example, editing activity spiking sharply at the time of WHL inscription (e.g.
@@
 
-Come back to danger list [@brown2019politics; @holleland2019naming]
+Our results establish Wikipedia as site and community demonstrating active engagement with cultural heritage [@pentzold2017digging], especially cultural sites on the UNESCO World Heritage List.
+We have defined Wikipedia as an online peer production community with technical and cultural qualities that separate it from social media such as Twitter and Facebook.
+Editing mechanics, bots, reverts, and talk pages work together to enable and limit discourse and debate about CS-WHL on Wikipedia.
+The goal-driven culture of Wikipedia editors, and the organisation's policies that guide the production of articles strongly constrain heritage discourse, such that the exchange of different perspectives are rarely found in articles themselves, but buried in technical and highly specific discussions on article talk pages.
+Our results show how these distinctive qualities generate a technicity that shapes how people engage with elements of the past and attribute social and cultural meanings on Wikipedia.
+These resemble the "contingent collaborations" and "productive frictions" described by @tsing2011friction where local, individual actions of knowledge creation are circumscribed by forces and structures that encompass their expression, but also give meaning to their interactions.
 
-Sites where the conflict is international have it show on WP
+We found that many of the Wikipedia articles about CS-WHL are central to the encyclopedia project.
+Many of them were among the first articles written for the encyclopedia, are more frequently viewed, are more frequently linked to by other articles, are longer, and more intensively edited by a greater variety of editors, than the average article.
+These results indicate the high value that Wikipedia users place on CS-WHL, consistent with the goal of the UNESCO World Heritage Committee to maintain a list reflects the world's cultural diversity of outstanding universal value.
+However, we found that sites are unequally valued, in predictable ways, given prior work on the demographics of Wikipedia users and editors, and the Eurocentric value system of the World Heritage Committee [@cleere2003uneasy; @smith2006uses p.
+98].
+CS-WHL in countries in the Global South are under-represented on Wikipedia, a geographical tension that is also evident in the World Heritage List [@brumann2014shifting].
+They are also shorter and received less attention in the form of page views and inward Wikilinks.
 
-https://en.wikipedia.org/wiki/Wikipedia:Geopolitical,_ethnic,_and_religious_conflicts_noticeboard now defunct
+Perhaps the most striking spatial pattern in our results is how much of the edits to CS-WHL articles in any part of the world come from the United States.
+The anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing.
+This suggests a digital colonialism of world heritage information on Wikipedia, where heritage is interpreted and communicated by people who are not part of the descendant community traditionally associated with the site.
+This is an important observation because it is these editors that control the production of knowledge about CS-WHL articles, and the ability to control information about heritage has several implications.
+First is that the choices of these editors define community identity, that is, the community of Wikipedia editors, and also the broader community of Internet users that read Wikipedia, by indicating which sites are important and visible, and which are not by contributing to a digital 'authorized heritage discourse' [@smith2012constrained] that prioritizes their own self-interests.
+Second is that traditional communities associated with CS-WHL have little control over how their own heritage is represented on Wikipedia.
+We see this spatial pattern on Wikipedia as part of a trend of globalization of heritage, where places that had traditionally contributed to local or regional identities are turned into sanitized playgrounds for rich tourists [@bernbeck2004political].
+Wikipedia may be seen as virtual playground for Americans to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities.
+In this way, the representation of heritage on Wikipedia recapitulates a long-standing tradition of colonial subordination of one group's heritage and identity by a more powerful and dominant group.
+
+This colonial logic may help to explain our findings of minimal conflicts surrounding the production of Wikipedia articles about CS-WHL.
+We found that bot activity, numbers of revert edits, and edits relating to vandalism for CS-WHL articles were comparable to or less than other sites.
+Most of this activity relates to playful vandalism and occurred on uncontroversial CS-WHL sites such as the Sydney Opera House and the Tower of London.
+Controversial sites, identified by the presence of military or diplomatic conflicts, were not prominent in these metrics.
+Our analysis of the talk pages of CS-WHL articles shows that they are often longer than a typical Wikipedia article, and are the location where conflict is most evidence.
+While much of the conflict is highly technical and local about the policies and processes of editing Wikipedia, we did observe signs of the political and military conflict at CS-WHL played out on some of the talk pages, such as Mapungubwe and Preah Vihear.
+We interpret this as editors exploiting the talk pages for behind-the-scenes heritage activism.
+The technical and cultural constraints of writing directly on the article page mean that the talk page is the only suitable location for negotiating disputes whose eventual trace in the edit history of the article might be negligible.
+We found that some CS-WHL talk pages referenced a 'Geopolitical, ethnic, and religious conflicts noticeboard' elsewhere on Wikipedia, as a forum for arbitration of disputes created in 2008 following a recommendation by an investigation into edit wars on articles about Northern Ireland (The Troubles), Palestine-Israel and other locations with ethnic or cultural based conflicts.
+However the noticeboard was closed in 2012 due to an absence of activity.
+Overall we find that editors of CS-WHL articles appear conflict-averse, probably because many of them come from similar cultural, socio-economic and educational backgrounds, and so share similar values about heritage that align with their shared goal of making an encyclopedia.
+The low levels of conflict reflect the continuity between the printed encyclopedia project as a compendium of universal knowledge, and the World Heritage List as universal heritage.
+These projects share origins in the cultural elites of Western European, and their distinctive sense of what is universal that is linked to nineteenth-century nationalism and liberal modernity [@smith2006uses].
+
+The results of our time series analyses reveal complex patterns in how heritage-related concerns are realized on Wikipedia.
+Some sites show spikes in Wikipedia editing activity that are directly related to the inscription of the site on the WHL, or conflict events at the site.
+However at other sites the rhythms of editing activity seem unrelated to events directly related to the site.
+Like the talk pages, which have unrealised potential for close reading of heritage activism and disputes, close study individual edit histories of CS-WHL articles may reveal further patterns of how people engage with heritage on Wikipedia.
 
 # Conclusion
+
+The agency of people participating in heritage-related activities on Wikipedia is highly constrained by the technical characteristics of editing, bots, and consensus-valuing culture.
+Although there are some niches where editors can debate, concerns about state-like actors, violence & destruction, deal-making, etc.
+are poorly represented.
+Typical conflicts about Wikipedia CS-WHL articles are hyper-local, and process-centered.
+Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the United States.
+Because of these technical and cultural characteristics of Wikipedia, its articles present a discourse that actively obscures the power relations that give rise to them, and makes opaque debates about how heritage is involved in the production of identity and power [cf.@harvey2001heritage].
+
+That said, Wikipedia is valuable and important as a Big Data source of social information on heritage for several reasons.
+Although it lacks the velocity of other social media, such as Twitter, it preserves a distinctively complex record of human interactions with the past at simultaneously high scales, high resolution, and in highly structured ways, afforded by no other platform.
+As a non-profit entity, Wikipedia's data are freely available to researchers, unlike Twitter and Facebook.
+This has important ethical implications because it eliminates the need for academic collaboration with commercial platforms, whose business interests may not align with the researchers' ethics [@schroeder2014big].
+As a context of heritage production, a resource of information on heritage, and an artefact of contemporary digital heritage, Wikipedia is remarkable and holds substantial research potential.
+Given the tremendous popularity of Wikipedia, is it important that future work on digital heritage in this context continue to critically examine what is absent from, and uncontested in, Wikipedia, and who benefits and suffers from these absences.
 

### 2020-05-31 analysis/paper/001-UNESCO-CS-WHL-world-map-counts.R

@@ -42,6 +42,7 @@ wh_unesco_countries <-
 
 wh_unesco_countries_count <-
   wh_unesco_countries %>%
+  separate_rows(states_name_en, sep = ",") %>%
   count(country)
 
 median_number_unesco_sites_per_country <-
@@ -69,7 +70,7 @@ sf_map_data_unesco <-
   left_join(wh_unesco_countries_count,
             by = c( 'name_long' = 'country')) %>%
   select(name, n, geometry) %>%
-  # mutate(n = ifelse(is.na(n), 0, n)) %>%
+  mutate(n = ifelse(is.na(n), 0, n)) %>%
   filter(name != "Antartica")
 
 wh_country_unesco_count_map <-

### 2020-05-31 analysis/paper/002-Wikipedia-CS-WHL-world-map-counts.R

@@ -18,35 +18,48 @@ wh_wiki_table <-
   readxl::read_excel(here::here("analysis/data/raw_data/whc-sites-2019.xls"))
 }
 
+# expand sites that are in multiple countries
+wh_wiki_table_exp <-
+wh_wiki_table %>%
+  filter(category == "Cultural") %>%
+  separate_rows(states_name_en, sep = ",")
+
 # get country of site from location text
 # Laos, Czech Republic, Micronesia, Zimbabwe, South Sudan, Chad,
 # Central African Republic, Congo, Gabon, Cameroon, Nigeria, Bosnia and Herzegovina
 #  Cote d'Ivoire, Sierra Leone, Guyana, Belize,
-country_names <-  paste(c(world$name,
+country_names <-  paste0(c(world$name,
                           "United States",
                           "Czech Republic",
                           "Antigua & Barbuda",
                           "Saint Kitts and Nevis",
-                          "Lao"
-),
+                          "Lao"),
 collapse="|")
 
-page_data_for_all_pages_location <-
+page_data_for_all_pages_location <- # wp data
   page_data_for_all_pages %>%
   mutate(country = str_extract(Location,
                                regex(country_names,
                                      ignore.case=TRUE))) %>%
-  mutate(country = case_when(
-    country == "United States" ~ "United States of America",
-    country == "Czech Republic" ~ "Czechia",
-    country == "Antigua & Barbuda" ~ "Antigua and Barb.",
-    country == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
-    country == "Lao" ~ "Lao People's Democratic Republic",
-    TRUE ~ as.character(country)))
+  mutate(country2 = ifelse(str_detect(Location, "Nigeria"),
+                          "Nigeria", # Niger/ier
+                          country)) %>%
+  mutate(country2 = case_when(
+    country2 == "United States" ~ "United States of America",
+    country2 == "Czech Republic" ~ "Czechia",
+    country2 == "Antigua & Barbuda" ~ "Antigua and Barb.",
+    country2 == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
+    country2 == "Lao" ~ "Lao People's Democratic Republic",
+    is.na(country2) ~ "Russia",
+    TRUE ~ as.character(country2)))
 
 
-wh_wiki_table_location <-
[…]

### 2020-05-31 analysis/paper/002-Wikipedia-umap-hdbscan.R

@@ -91,7 +91,8 @@ main_plot <-
   geom_point(
     aes(colour = factor(hdbscan_out$cluster),
       #  size =  pages_umap_input_selected$page_wordcount_norm  ,
-        shape = pages_umap_input$continent
+        shape = pages_umap_input$continent,
+      size = 3
     )) +
  # scale_size(range = c(2,7), guide = FALSE) +
   scale_shape(name = "Continent") +

### 2020-06-01 analysis/paper/paper.Rmd
submission to BD&S

@@
 This special revert action, combined with a 'talk' page attached to each encyclopedia article for threaded discussion among editors, allows us to detect and study the dynamics of conflicts arising from the creation and editing of articles [@suh2007us].
-For example, a high proportion of 'revert' type edits, and a high word count on the talk page can indicate the controversiality of an article [@yasseri2012dynamics].
+While articles themselves must be written to conform to the fundamental Wikipedia policy of NPOV (Neutral Point Of View), the talk page is where different views are expressed and negotiated among editors in detail.
+Taken together, a high proportion of 'revert' type edits, and a high word count on the talk page can indicate the controversiality of an article [@yasseri2012dynamics].
 
@@
 This revealed `r n_clusters` clusters, with the most important variables for determining cluster membership being the number of items in the reference list at the end of the article, the number of words in the article, and the number of Wikilinks out from the target article to other Wikipedia articles.
-That said, `r n_no_cluster` (`r round(prop_no_cluster) * 100`%) articles were not assigned to a cluster by the HDBSCAN algorithm, indicating that the basic characteristics of CS-WHL articles do not partition the articles in highly structured and discrete groups.
+That said, `r n_no_cluster` (`r round(prop_no_cluster * 100)`%) articles were not assigned to a cluster by the HDBSCAN algorithm, indicating that the basic characteristics of CS-WHL articles do not partition the articles in highly structured and discrete groups.
 
@@
 We reviewed the talk page for the Timbuktu article to determine if the attention received by the article might relate to the issues leading to armed conflict at the site.
-Of the `r timbuktu_talk_page_word_count` word on the talk page, only 168 are on the topic of conflict and destruction, with the editors discussing how to describe the scale of the damage to the temples.
+Of the `r timbuktu_talk_page_word_count` words on the talk page, only 168 are on the topic of conflict and destruction, with the editors discussing how to describe the scale of the damage to the temples.
 The majority of talk page content is about filling in missing detail, suggestions for or notifications of minor corrections.
@@
 Among the CS-WHL articles that have high proportions of reverts and edits about vandalism are highly iconic sites in the Western canon of culture history, e.g.
-the Sydney Opera House, the Tower of London, and the Statue of Liberty.
+the Sydney Opera House, the Tower of London, and the Statue of Liberty [cf.
+@harrison2013forgetting].
 In reviewing a sample of several hundred reverted edits for each of these, we found that nearly all of them are undoing the addition of short strings of text (e.g.
@@
 We see this spatial pattern on Wikipedia as part of a trend of globalization of heritage, where places that had traditionally contributed to local or regional identities are turned into sanitized playgrounds for rich tourists [@bernbeck2004political].
-Wikipedia may be seen as virtual playground for Americans to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities.
+Wikipedia may be seen as virtual playground for Americans to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities, perhaps reflecting a cultural rhetorcic 'heritage populism' [@reynie2016specter].
 In this way, the representation of heritage on Wikipedia recapitulates a long-standing tradition of colonial subordination of one group's heritage and identity by a more powerful and dominant group.
@@
 Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the United States.
-Because of these technical and cultural characteristics of Wikipedia, its articles present a discourse that actively obscures the power relations that give rise to them, and makes opaque debates about how heritage is involved in the production of identity and power [cf.@harvey2001heritage].
+Because of these technical and cultural characteristics of Wikipedia, its articles present a discourse that actively obscures the power relations that give rise to them, and makes opaque debates about how heritage is involved in the production of identity and power [cf.
+@harvey2001heritage].
 
@@
 This has important ethical implications because it eliminates the need for academic collaboration with commercial platforms, whose business interests may not align with the researchers' ethics [@schroeder2014big].
+ALthough free of these commercial interests, a different set of ethics is implied by the exquisite administrative and technical complexity of Wikipedia.
+These structures serve to normalize and historize inequalities, and manage threats to models of control and expertise about heritage [@harrison2015beyond].
 As a context of heritage production, a resource of information on heritage, and an artefact of contemporary digital heritage, Wikipedia is remarkable and holds substantial research potential.
-Given the tremendous popularity of Wikipedia, is it important that future work on digital heritage in this context continue to critically examine what is absent from, and uncontested in, Wikipedia, and who benefits and suffers from these absences.
+While the Neutral Point of View is a central policy for Wikipedia articles, representations and definitions of cultural heritage are never neutral in any discourse, because it always comes from some perspective [@lahdesmaki2019conflicts].
+Given the tremendous popularity and visibility of Wikipedia, is it important that future work on digital heritage in this context continue to critically examine what is absent from, and uncontested in, Wikipedia, and who benefits and suffers from these absences.
 

### 2020-06-01 analysis/paper/002-Wikipedia-umap-hdbscan.R

@@ -82,8 +82,8 @@ tibble(clus = names(table(hdbscan_out$cluster)),
 
 n_clusters <- nrow(clus_tbl) -1
 
-n_no_cluster <- clus_tbl %>% filter(clus == 0) %>% pull(n)
-prop_no_cluster <- n_no_cluster / sum(clus_tbl$n)
+n_no_cluster <- clus_tbl %>% filter(clus == 0) %>% pull(n) %>% unname
+prop_no_cluster <- (n_no_cluster / sum(clus_tbl$n)) %>% unname
 
 main_plot <-
   ggplot(pages_umap_output,
@@ -94,7 +94,7 @@ main_plot <-
         shape = pages_umap_input$continent,
       size = 3
     )) +
- # scale_size(range = c(2,7), guide = FALSE) +
+  scale_size(guide = FALSE) +
   scale_shape(name = "Continent") +
   scale_color_viridis_d(guide = FALSE) +
   theme_minimal() +
@@ -153,10 +153,10 @@ sub_plot <-
 # plot plus subplot
 main_plot +
   annotation_custom(ggplotGrob(sub_plot),
-                    xmin = -8,
-                    xmax = -4,
-                    ymin= -5,
-                    ymax= -2.5)
+                    xmin = 6,
+                    xmax = 4,
+                    ymin= 5.5,
+                    ymax= 3.5)
 
 ggsave(here::here("analysis/figures/wh_country_umap_hdbscan.png"),
                   width = 10,

### 2020-06-08 analysis/paper/paper.Rmd
fix typos in the paper

@@
 The talk page also has a much longer argument, mostly between two editors, about whether or not the Thai name of the site should be included in the text of the article.
-This debate also recapitiulates issues of which country has the stronger claim for ownership of the temple.
+This debate also recapitulates issues of which country has the stronger claim for ownership of the temple.
 Amid accusations of nationalism among the editors, one of them asks "Can we put aside politics and be more collaborative on the encyclopedia project?" and appeals to Wikipedia policies 'Third opinion' and 'Dispute resolution' to diffuse the tensions and refocus attention on the common goal.
@@
 We see this spatial pattern on Wikipedia as part of a trend of globalization of heritage, where places that had traditionally contributed to local or regional identities are turned into sanitized playgrounds for rich tourists [@bernbeck2004political].
-Wikipedia may be seen as virtual playground for Americans to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities, perhaps reflecting a cultural rhetorcic 'heritage populism' [@reynie2016specter].
+Wikipedia may be seen as virtual playground for Americans to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities, perhaps reflecting a cultural rhetoric of 'heritage populism' [@reynie2016specter].
 In this way, the representation of heritage on Wikipedia recapitulates a long-standing tradition of colonial subordination of one group's heritage and identity by a more powerful and dominant group.

### 2020-11-21 analysis/paper/paper.Rmd
finish editing results

@@
 
-Heritage is the processes and outcomes of people engaging with elements of the past – material and immaterial – and attributing social and cultural meanings to them in the present (Smith 2006; Harrison 2013).
+Heritage is the processes and outcomes of people engaging with elements of the past -- material and immaterial -- and attributing social and cultural meanings to them in the present (Smith 2006; Harrison 2013).
 These are important to understand because they shape peoples' identities and influence how they think and behave towards other people.
@@
 [-@Krzyzanska_2018; -@bonacchi2019digital] have sketched out the new digital heritage research program with their combination of data-intensive and qualitative investigations of 1.4m Facebook posts in Brexit-related community groups.
-They found recurring parallels – both pro- and anti-Brexit – made by Facebook users between the European Union, the Roman Empire and "barbarians" as they use heritage to support their political activism.
+They found recurring parallels -- both pro- and anti-Brexit -- made by Facebook users between the European Union, the Roman Empire and "barbarians" as they use heritage to support their political activism.
 They demonstrate the potential for understanding public perceptions and experiences of the past in contemporary society using big data obtained from social media.
-In this paper we extend the digital heritage research program in two important new directions.
+In this paper we extend the digital heritage research program in two substantial new directions.
 First, we introduce Wikipedia as an example of an online peer production community where people engage with elements of the past in measurable ways.
-Second, present a case study using data science methods to investigate the ways people create and consume Wikipedia articles on cultural sites inscribed on the UNESCO World Heritage List (hereafter CS-WHL).
+Second, we present a case study using data science methods to investigate the ways people create and consume Wikipedia articles on cultural sites inscribed on the UNESCO World Heritage List (hereafter CS-WHL).
 
 While social media is a vast and diverse online space that we are only just beginning to explore how people engage with the past, there are other contexts of online interactions where heritage is practiced in distinctive, if poorly understood, ways.
-We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with peer production communities, where online users participate in the collaborative, asynchronous creation, sharing, promoting, and classification of content in highly structured and goal-directed ways [@wilkinson2008strong].
+We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with online peer production communities, where users participate in the collaborative, asynchronous creation, sharing, promoting, and classification of content in highly structured and goal-directed ways [@wilkinson2008strong].
 Online peer production communities are comparable to more traditions kinds of voluntary associations where groups set and execute goals, with explicitly democratic organizational ideals.
 While the ideals of many online peer production communities emphasize non-hierarchical and non-bureaucratic organization, analysis of large amounts of user activity indicates that most of these communities are actually undemocratic and noninclusive, functioning as entrenched oligarchies [@shaw2014laboratories].
-This emphasis on governance and management of collective action is a key detail that distinguishes online communities on social media from online communities on peer production projects.
-It follows that user interactions in the process of generating context in online peer production communities includes technological and social mechanisms that enact the community's governance policies, for example, limiting a user's activity according to their status in the community's hierarchy, or managing conflict with highly structured procedures.
-These distinctive organizational and technical qualities of online peer production communities make them an intriguing novel context of heritage production to study digital traces of human activity resulting from engagement with the past
+This emphasis on governance and management of collective action is a key detail that distinguishes social media from online peer production.
+It follows that user interactions in the process of generating content in online peer production communities includes technological and social mechanisms that enact the community's governance policies, for example, limiting a user's activity according to their status in the community's hierarchy, or managing conflict with highly structured procedures.
+Here we show how the distinctive organizational and technical qualities of online peer production communities make them an intriguing novel context of heritage production to study digital traces of human activity resulting from engagement with the past.
+We show how these technological and social mechanisms constrain the representation of controversies about CS-WHL.
 
@@
 Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, Wikipedia.
-Originating in 2001, this is a highly influential and well-known online encyclopedia, currently with 11 billion page views per month (https://stats.wikimedia.org/#/en.wikipedia.org), that anyone can edit.
+Originating in 2001, this is a highly influential and well-known online encyclopedia, that anyone can edit, currently with 11 billion page views per month (<https://stats.wikimedia.org/#/en.wikipedia.org>).
 Although anyone can edit, most internet users do not, and the characteristics of people who do edit are important to understand to identify biases in the encyclopedia's content.
@@
 Wikipedia has a special category of edit called the 'revert' which allows a user to restore an article to an earlier state to remove recent vandalism (such as the addition of irrelevant or offensive material).
-This special revert action, combined with a 'talk' page attached to each encyclopedia article for threaded discussion among editors, allows us to detect and study the dynamics of conflicts arising from the creation and editing of articles [@suh2007us].
+This special revert action, combined with a 'talk' page attached to each encyclopedia article for threaded discussion among editors, allows us to detect and study the social dynamics arising from the creation and editing of articles, for example the controversiality of an article [@yasseri2012dynamics; \@suh2007us].
 While articles themselves must be written to conform to the fundamental Wikipedia policy of NPOV (Neutral Point Of View), the talk page is where different views are expressed and negotiated among editors in detail.
-Taken together, a high proportion of 'revert' type edits, and a high word count on the talk page can indicate the controversiality of an article [@yasseri2012dynamics].
 
@@
 
-##  UNESCO World Heritage Cultural Sites as foci of Conflict
+## UNESCO World Heritage Cultural Sites
 
@@
 Sites that are listed, or candidates for listing, are often foci of disputes and negotiations about territory, sovereignty, and security, as well as international corporate activity [@meskell2018future].
-This is because the process of selecting of sites to be inscribed on the WHL has become politicized and driven by countries’ political influence and national strategic interests [@bertacchini2016politicization].
+This is because the process of selecting of sites to be inscribed on the WHL has become politicized and driven by countries' political influence and national strategic interests [@bertacchini2016politicization].
 For example, the members of the World Heritage Committee are mostly career diplomats rather than heritage specialists, indicating that the processes and decisions of this committee may be motivated more by political trade-offs than by heritage expertise and judgment [@von2011concept].
@@
 They appropriated Western discourse on national cultural heritage to argue for the safeguarding of Angkor as part of their quest for national independence and international recognition.
-Early in the Khmer Rouge regime Angkor was declared a symbol of enslavement by a primitive culture, but when the Khmer Rouge adopted a new rhetoric of a supposedly civilizing mission, they presented it as the site one of the great world civilizations [@falser2015representing].
+Early in the Khmer Rouge regime, Angkor was declared a symbol of enslavement by a primitive culture, but when the Khmer Rouge adopted a new rhetoric of a supposedly civilizing mission, they presented it as the site one of the great world civilizations [@falser2015representing].
 The 2003 inscription of Mapungubwe (the site of the first indigenous kingdom in Southern Africa, 900-1,300 AD) was preceded by a recommendation from ICOMOS (International Council on Monuments and Sites, a professional association that is a key advisory body to the World Heritage Committee) not to inscribe because of the farming and mining activity in highly sensitive areas near the site, and the unclear ownership of the mining rights at the time [@meskell2011paris].
-Despite this negative recommendation, geopolitical machinations within the Committee, especially by the Indian and Russian delegates, led to Mapungubwe being inscribed on the list, although without the typical prerequisites of an integrated management plan or complete buffer zone [@meskell2012rush].
-These examples of Angkor and Mapungubwe demonstrate the attention that the WHL inscription process can generate due to political activitsm, conflicts and intrigue.
+Despite this negative recommendation, geopolitical machinations within the Committee, especially by the Indian and Russian delegates, led to Mapungubwe being inscribed on the list, although without the typical prerequisites of a management plan or complete buffer zone [@meskell2012rush].
+These examples of Angkor and Mapungubwe demonstrate the attention that the WHL inscription process can generate due to political activism, conflicts and intrigue.
 
-Physical conflict at or near CS-WHL are also major events that galvanise public interest in these locations.
-World Heritage sites in Palestine, Mali, Syria, Congo and Cambodia have recently been sites of violence, in many cases the violence is specifically linked to their potential WHL nomination, listing or management.
+Physical conflicts at or near CS-WHL are also major events that galvanize public interest in these locations.
+World Heritage sites in Palestine, Mali, Syria, Congo and Cambodia have recently been sites of violence, in many cases specifically linked to their potential WHL nomination, listing or management.
 In 1998 anti-government and mostly Hindu Tamil groups bombed the holy Buddhist site of the Temple of the Tooth at the WHL site of Kandy (the last capital of the ancient kings of Sri Lanka), killing 17 people and substantially damaging the temple [@coningham1999paradise].
 In Mali during 2012, fighting between government and rebel groups lead to the damage and destruction of tombs at the CS-WHL sites of Gao and Timbuktu [@brioschi2017discourses].
-The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are currently among the 36 cultural sites on the List of World Heritage in Danger (https://whc.unesco.org/en/danger/).
-In 2015, ISIS militants destroyed the Temple of Bel in Palmyra, Syria (a CS-WML site of monumental ruins, once great city at the crossroads between east and west in the ancient world) [@gornik2015can].
+The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are currently among the 36 cultural sites on the List of World Heritage in Danger (<https://whc.unesco.org/en/danger/>).
+In 2015, ISIS militants destroyed the Temple of Bel in Palmyra, Syria (a CS-WHL site of monumental ruins, once great city at the crossroads between east and west in the ancient world) [@gornik2015can].
 Preah Vihear, inscribed in 2008, is a CS-WHL located on a long-disputed section of the Thai-Cambodia border that has been a site of both violent military clashes and international political intrigue.
@@
 Many CS-WHL are symbols of national, cultural, political, and religious identity, and the extent of political involvement in negotiations of WHL inscriptions indicates they are of great public interest among local and diasporic communities.
-Our goal in this study is answer the question of how this interest is expressed within the socio-technical constraints of Wikipedia.
-How are conflicts over CS-WHL enacted in the canalized interactions of the world's largest encyclopedia?
+Our goal in this study is to answer the question of how this interest is expressed within the socio-technical constraints of Wikipedia.
 We attempt to answer this question by studying all the CS-WHL that have Wikipedia articles.
 We surveyed the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics).
-There are great many additional metrics available for Wikipedia articles, an we have limited ourselves to the most basic for this initial investigation.
-By comparing these basic characteristics of Wikipedia articles about CS-WHL to 10,000 random Wikipedia articles we will answer the question: how does engagement with the past compare via CS-WHL on Wikipedia compare to engagement with other topics?
-Do Wikipedia articles about controversial CS-WHL sites, such as those discussed above, get more attention than random Wikipedia articles?
+There are many other additional metrics available for Wikipedia articles, an we have limited ourselves to the most basic for this initial investigation to establish a baseline for future studies that might similarly investigate Wikipedias written in languages other than English.
+By comparing these basic characteristics of Wikipedia articles about CS-WHL to 10,000 random Wikipedia articles we can approach the question: can metrics of content, consumption, and production indicate engagement with the past via CS-WHL on Wikipedia?
 Can we detect conflict in the edit histories, bot activity, and talk pages for Wikipedia articles about CS-WHL sites, and how does this conflict relate to the types of controversies noted above?
+Random articles were obtained by sending GET requests to the 'random' module in the Wikimedia REST API (<https://en.wikipedia.org/api/rest_v1/>).
 
@@
 For example, when an article is edited by a user who does not have a Wikipedia user account (or is not logged into their account), their edit is identified by that person's IP address.
-This IP address can be used to geo-locate the user to the city they were in when the made the edit.
+This IP address can be used to geo-locate the user to the country they were in when the made the edit.
 We geo-located all edits with IP addresses for all Wikipedia articles CS-WHL sites to determine the country of origin of those edits.
@@
 We obtained data about Wikipedia articles by scraping the HTML pages with the rvest package for R [@rvest].
-We used the SelectorGadget [@cantino2017selectorgadget] extension for the Chrome web browser to identify specific elements of interest, or nodes, on the HTML pages, and wrote custom R functions to extract data from these nodes.
+We used the SelectorGadget [@cantino2017selectorgadget] extension for the Chrome web browser to identify specific page elements of interest, or nodes, on the HTML pages, and wrote custom R functions to extract data from these nodes.
 Our entry points were the Wikipedia articles that are lists of World Heritage regions in major geographical regions of the globe.
@@
 A small number of CS-WHL sites have Wikipedia articles that are not included on these tables, we did not include these in our sample.
-We chose this approach because the Wikipedia article titles for CS-WHL sites often differ from the official site name on the UNESCO list, making manual look-ups very inefficient.
+Starting at these regional lists of sites was a pragmatic choice because the individual Wikipedia article titles for CS-WHL sites often differ from the official site name on the UNESCO list.
+A limitation of this approach is that it excludes possible 'orphan' pages for CS-WHL that, while present in Wikipedia, have not been curated by editors into a table listing all the sites in a region.
+On the other hand, this approach ensures that our all sites in our sample are meaningful by sharing the essential quality of a taxonomic status of being categorized by Wikipedia editors as a CS-WHL in a certain region.
 
-The highly structured nature of most Wikipedia pages afforded us much efficiency during data collection, however, a not insignificant number of pages had minor irregularities, for example, exotic table formatting or minor deviations from widely used templates, that necessitated more complex programming.
-An especially challenging issue was minor irregularities in spelling place names, for example, "Saint Kitts and Nevis" and "St.
+The highly structured nature of most Wikipedia pages afforded us much efficiency during data collection, however, a not insignificant number of pages had technical irregularities, for example, exotic table formatting or minor deviations from widely used templates, that necessitated more complex programming for data collection.
+An especially challenging issue was irregularities in spelling place names, for example, "Saint Kitts and Nevis" and "St.
 Kitts and Nevis", which can confound programmatic joining and summarizing of data by failing to recognize as the same place and leading to under-counting.
 We attempted to correct these manually in our code.
-Another challenge was in the formatting of tables, for example a merged cell in a table introduced an irregularity that made parsing and scraping complicated and fragile.
+Another challenge was in the formatting of tables on Wikipedia pages, for example a merged cell in a table introduced an irregularity that made parsing and scraping complicated and fragile.
 We collected data during May 2019, and due to the dynamic nature of Wikipedia, it is highly likely that articles in our study have subtly changed since our data collection as users and bots continue their activity.
-It is unlikely that articles in our sample have been deleted from Wikipedia since our data collection, because of the high notability of CS-WHL, but it is possible that new articles have since appeared about sites that were not represented on Wikipedia since we collected the data.
-Our original scraping code may no longer work as the tables on Wikipedia articles continue to be modified.
+It is possible that new articles have since appeared about sites that were not represented on Wikipedia since we collected the data.
+Our original scraping code may no longer work on the most current version of Wikipedia without modification as the tables on Wikipedia articles continue to be modified by editors.
 
@@
 
-To enable reuse of our materials and improve reproducibility and transparency [@marwick2017computational], we include the entire R code [@rprogram] used for all the analysis and visualizations contained in this article in our compendium at http://doi.org/10.17605/OSF.IO/AY27G.
+Although we recognize that the fragility and temporally specific nature of our methods limits the reproducibility of our results, we include the entire R code [@rprogram] used for all the analysis and visualizations contained in this article in our compendium at <http://doi.org/10.17605/OSF.IO/AY27G> to enable reuse of our materials and improve reproducibility and transparency [@marwick2017computational].
 Also in this version-controlled compendium are the raw data for all the results reported here.
@@
 rrtools:::quietly(source(here::here("analysis/paper/002-Wikipedia-umap-hdbscan.R")))
-knitr::include_graphics(here::here("analysis/figures/wh_country_umap_hdbscan.png"))
+# knitr::include_graphics(here::here("analysis/figures/wh_country_umap_hdbscan.png"))
 ```
@@
 This revealed `r n_clusters` clusters, with the most important variables for determining cluster membership being the number of items in the reference list at the end of the article, the number of words in the article, and the number of Wikilinks out from the target article to other Wikipedia articles.
+Put simply, articles about CS-WHL vary the most in how detailed and researched they are.
 That said, `r n_no_cluster` (`r round(prop_no_cluster * 100)`%) articles were not assigned to a cluster by the HDBSCAN algorithm, indicating that the basic characteristics of CS-WHL articles do not partition the articles in highly structured and discrete groups.
@@
 
+## Article content
+
 As a group, the basic details of content for Wikipedia articles for CS-WHL differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
-The scholarly nature of the articles, measured by the number of sources cited in the reference list per thousand words in the article body, is similar for CS-WHL articles and random articles.
-The number of Wikilinks out from the target article to other Wikipedia articles is also similar for CS-WHL articles and random articles.
-However, the total number of words in a CS-WHL article is typically much higher than a random article.
-
-The basic metrics of consumption of CS-WHL articles show substantial differences from our sample of random articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
-We measure consumption by counting the total number of views of the article over the 100 days prior to our data collection date, and the the number of Wikilinks from other articles into the target article.
-Wikipedia article view counts are popular widely-used measures of cultural interest or salience [@roll2016using; @cao2020analysis; @mciver2014wikipedia].
-Wikilinks from other articles are a measure of the centrality of an article, if many other articles link to it, then the article is well-integrated into the encyclopedia and viewed as important for supporting information presented in other articles.
-CS-WHL articles are typically viewed far more frequently than other Wikipedia articles, reflecting high consumption by internet users generally.
-They are also much more often linked to by other Wikipedia articles than our random sample of other articles, indicating consumption by other Wikipedia articles and Wikipedia users in their editing work (Figure \@ref(fig:wh-wiki-content-and-consumption)).
-This indicates that consumption of CS-WHL articles is generally very high.
-But is this attention evenly distributed across all CS-WHL articles?
-
-```{r}
-timbuktu_talk_page_word_count <- 
-  page_data_for_all_pages %>%  
-  filter(str_detect(Site, "Timb")) %>% 
-  pull(talk_page_wordcount)
-```
-
-The scatterplot on the lower right of Figure \@ref(fig:wh-wiki-content-and-consumption) shows the values of inward Wikilinks, article views and article word count for all CS-WHL articles.
-The labeled points in the upper right quadrant are the articles that receive most of the attention.
-Of the CS-WHL notable for conflict discussed above, only Timbuktu is visible among these highly popular articles.
-It is also the only site on the List of World Heritage in Danger that is among these highly popular articles.
-We reviewed the talk page for the Timbuktu article to determine if the attention received by the article might relate to the issues leading to armed conflict at the site.
-Of the `r timbuktu_talk_page_word_count` words on the talk page, only 168 are on the topic of conflict and destruction, with the editors discussing how to describe the scale of the damage to the temples.
-The majority of talk page content is about filling in missing detail, suggestions for or notifications of minor corrections.
-This is also the case for the talk page for Auschwitz, another very popular CS-WHL article.
-Although Wikipedia articles on this site in other languages have different points of emphasis [@wolniewicz2016framing], the discussion among editors is generally technical and precise, and provocative comments usually ignored rather than directly disputed.
-This can be contrasted with the talk page for the Holocaust, where @pfanzelter2015crossroads found abundant evidence of conflict among editors.
+The scholarly nature of the articles, measured by the number of sources cited in the reference list per thousand words in the article body, have similarly distributions for CS-WHL articles and random articles.
+The number of Wikilinks out from the target article to other Wikipedia articles are also similarly distributed for CS-WHL articles and random articles.
+The total number of words in a CS-WHL article is typically much higher than a random article, indicating that they receive more generative effort from editors than other articles.
 
@@
 
-Basic variables related to the production of Wikipedia articles on CS-WHL differ in key ways from other articles (Figure \@ref(fig:wh-wiki-production)).
+## Article production
+
+Although details of content of CS-WHL articles are similar to our random sample, variables related to the production of Wikipedia articles on CS-WHL differ in important ways from other articles (Figure \@ref(fig:wh-wiki-production)).
 The number of edits per thousand words, or edit density, and the number of unique editors per thousand words, or editor density, are substantially higher for CS-WHL articles.
-CS-WHL articles are intensively word-smithed by a more diverse community of editors than usual.
+This tells us that CS-WHL articles are intensively word-smithed by a more diverse community of editors than for other articles.
 The absolute size of edits (i.e.
@@
 The involvement of bots in producing CS-WHL articles is also about the same as for other articles.
-Bot activity is most intense on shorter, low-profile CS-WHL articles, in Figure \@ref(fig:wh-wiki-production) the labeled points are sites where bots have done >30% of edits.
-Most of these bot edits are in the fixer, tagger, connector, and clerk roles.
-None of these articles with intensive bot activity are CS-WHL sites of conflict or on the List of World Heritage in Danger.
+Bot activity is most intense on shorter, low-profile CS-WHL articles, in Figure \@ref(fig:wh-wiki-production) the labeled points are sites where bots have done \>30% of edits.
 The most active bot on CS-WHL articles is Cluebot NG (vandalism detection and reverting), compared to Cydebot (automatic implementation of category deletions) for the random articles.
 The AnomieBOT is very active on CS-WHL articles compared to random articles, this bot performs clerical duties in an article's reference list.
+Most bot edits on on CS-WHL articles are in the fixer, tagger, connector, and clerk roles.
+None of these articles with intensive bot activity are CS-WHL sites of conflict or on the List of World Heritage in Danger, indicating that these sites receive little or no vandalism.
 
@@
 
-Talk pages are another location where we may see conflicts and debates unfold on Wikipedia.
+Talk pages are an important locus of article production activity where we expect to see conflicts and debates unfold on Wikipedia.
 Wikipedia talk pages are a popular subject of investigations to understand the collaborative generation of knowledge and online conflict management [@ho2016french; @ho2017exploring; @schneider2012content; @kittur2007he].
-The length of an article's talk page is correlated with the controversality of the article, and thus an effective simple proxy for conflict [@yasseri2012dynamics].
+@yasseri2012dynamics has shown that length of an article's talk page is correlated with the controversality of the article, and thus an effective simple proxy for conflict.
 We counted the words on all talk pages of the CS-WHL articles to identify conflict (Figure \@ref(fig:wh-wiki-talk-pages)).
@@
 However, the distribution of talk page lengths for CS-WHL articles has a long right tail, indicating that a higher number of articles have very long talk pages, compared to other articles.
-While it is true that some of these articles with long talk pages, such as Cologne Cathedral and Troy, have clear evidence of conflict among the editors, close reading of the discussions reveals that the debates are dominated by technical issues.
-For example, the Cologne Cathedral talk page includes some debate about the correct calculation of the interior volume of the structure, and on the Troy talk page there is a heated comments by one editor about another editor removing of some of their text containing unsourced claims and unencyclopedic writing style.
+Some of these articles with long talk pages, such as Cologne Cathedral and Troy, have clear evidence of conflict among the editors in the contents of the text.
+However, close reading of the discussions on these talk pages reveals that these debates are dominated by technical issues of article production, rather than conflicts and tensions at the CS-WHL or surrounding their inscription.
+For example, the Cologne Cathedral talk page includes some debate about the correct calculation of the interior volume of the structure, and on Troy talk page includes heated comments by one editor about another editor removing of some of their text containing unsourced claims and unencyclopedic writing style.
 
-Only one of the controversial sites discussed above is in the group of articles where the talk page is longer than the article itself, and none of the site on the UNESCO heritage in danger list are in this group.
-The talk page for Mapungubwe is lengthy with expressions of concern about the accuracy of information in the article.
+The talk page for Mapungubwe, which is longer than the article itself, is lengthy with expressions of concern about the accuracy of information in the article.
 In particular, editors were concerned about the depiction of Indigenous people, especially the degree to which early European colonists were aware of Indigenous communities, and the correct cultural affiliation of the Indigenous groups that originally occupied the site.
-These issues closely echo the themes identified by @meskell2011paris in her analysis of the WHC process.
+In this remarkable case we see the Wikipedia editors engaging conflicts that go beyond the typical technical details of article production.
+What is especially notable about these discussions on the talk page is how closely they echo the themes identified by @meskell2011paris in her analysis of the WHC process.
+The editors involved in this debate did not make any edits to the article itself which raises questions about their motivations for engaging in debate on the talk page, since they are not personally invested in the content of the article.
+Without directly interviewing these editors, we cannot be sure of their motives for participating in the talk page.
+
+A second important example of conflict on a talk page is the article about Preah Vihear Temple.
 Although not notable for the length of its talk page, the discussions among editors of the article about Preah Vihear Temple include a strongly worded disagreement among seven editors about the legitimacy of the ownership claims by Thailand and Cambodia of the territory that includes the temple.
-The debate among Wikipedia editors mirrors very closely the political tensions surrounding the nomination of Preah Vihear.
-The talk page also has a much longer argument, mostly between two editors, about whether or not the Thai name of the site should be included in the text of the article.
-This debate also recapitulates issues of which country has the stronger claim for ownership of the temple.
+As for Mapungubwe, the debate among Wikipedia editors mirrors very closely the political tensions surrounding the nomination of Preah Vihear.
+The talk page also has a lengthy argument from to 2008, involving several editors, about whether or not the Thai name of the site should be included in the text of the article.
+The editors appear to be people of Thai and Khmer heritage, with comments that personalise the national tensions such as "we invaded you", and references to contemporary political tensions such as the 2008 street demonstrations in Thailand that saw conflict between the royalist People's Alliance for Democracy and the populist People's Power Party.
+One editor indicates their likely Thai ethnicity here through their use of Thai language phrases (using the Thai alphabet).
+This debate also recapitulates broader substantive issues of whether Thailand or Cambodia country has the stronger claim for ownership of the temple.
 Amid accusations of nationalism among the editors, one of them asks "Can we put aside politics and be more collaborative on the encyclopedia project?" and appeals to Wikipedia policies 'Third opinion' and 'Dispute resolution' to diffuse the tensions and refocus attention on the common goal.
-Beyond these two pages we found that the majority of content on CS-WHL article talk pages is about highly local topics, mostly article administration, editing processes, and quality control.
+Unlike the Mapungubwe talk page, many of the editors involved in the Preah Vihear talk page debates have made contributions directly to the Preah Vihear article, and are deeply invested in how the article represents the site.
+
+## Article consumption
+
+The basic metrics of consumption of CS-WHL articles show substantial differences from our sample of random articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+We measure consumption by counting the total number of views of the article over the 100 days prior to our data collection date, and the the number of Wikilinks from other articles into the target article.
+Wikipedia article view counts are popular widely-used measures of cultural interest or salience [@roll2016using; @cao2020analysis; @mciver2014wikipedia].
+Wikilinks from other articles are a measure of the centrality of an article, if many other articles link to it, then the article is well-integrated into the encyclopedia and viewed as important for supporting information presented in other articles.
+CS-WHL articles are typically viewed far more frequently than other Wikipedia articles, reflecting high consumption by internet users generally.
+They are also much more often linked to by other Wikipedia articles than our random sample of other articles, indicating consumption by other Wikipedia articles and Wikipedia users in their editing work (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+This indicates that consumption of CS-WHL articles is generally very high, relative to other articles, and confirms our assertion of Wikipedia as an important source of heritage information.
+But is how is attention distributed across all CS-WHL articles, and how does it relate to sites with conflicts and tensions?
+
+```{r}
+timbuktu_talk_page_word_count <- 
+  page_data_for_all_pages %>%  
+  filter(str_detect(Site, "Timb")) %>% 
+  pull(talk_page_wordcount)
+```
+
+We can see an answer to this question in the scatterplot on the lower right of Figure \@ref(fig:wh-wiki-content-and-consumption), which shows the values of inward Wikilinks, article views, and article word count for all CS-WHL articles.
+The labeled points in the upper right quadrant are the articles that receive most of the attention.
+As noted above for sites with high proportions of reverts and edits, highly iconic sites in the Western canon of culture history are also the majority of sites that are highly consumed.
+Of the CS-WHL notable for conflict and tension, only Timbuktu is visible among these highly popular articles.
+It is also the only site on the List of World Heritage in Danger that is among these highly popular articles.
+We reviewed the talk page for the Timbuktu article to determine if the attention received by the article might relate to the issues leading to armed conflict at the site.
+Of the `r timbuktu_talk_page_word_count` words on the talk page, only 168 are on the topic of conflict and destruction, with the editors discussing how to describe the scale of the damage to the temples.
+The majority of talk page content for Timbuktu is about filling in missing detail, suggestions for or notifications of minor corrections.
+This is also the case for the talk page for Auschwitz, another very popular CS-WHL article with six archived talk pages including over 100,000 words.
+Although Wikipedia articles in other languages on Auschwitz have different points of emphasis [@wolniewicz2016framing], the majority of the discussion among editors on the talk pages is generally technical and precise.
+Provocative comments on the English language Auschwitz talk pages, for example by editors denying the Holocaust, usually end after brief exchanges with other editors requesting credible sources.
+The rarity of conflict on the Auschwitz talk page can be contrasted with the talk page for the Holocaust, where @pfanzelter2015crossroads found abundant evidence of conflict among editors.
+Generally, our results show that conflict and tension at a CS-WHL is not highly correlated with how much attention an article receives.
+
+## Spatial patterns
 
@@
 This pattern is consistent with @graham2014uneven's observations that places in the Global North tend to be over-represented on Wikipedia.
-The lower panel of figure \@ref(fig:wh-wiki-map) further demontrates this with South American countries having low proportions of their CS-WHL sites represented on Wikipedia.
+The lower panel of figure \@ref(fig:wh-wiki-map) further demonstrates this with South American countries having low proportions of their CS-WHL sites represented on Wikipedia.
 The pattern in African countries is that they either have a very small number of sites that are all on Wikipedia (indicated by yellow on the figure), or they do not have any CS-WHL at all.
-More surprising is the distribution of editor locations shown in figure \@ref(fig:wh-wiki-circle), which we determined by geo-locating the IP addresses attached to each anonymous edit on all CS-WHL articles.
+
+The distribution of editor locations shown in figure \@ref(fig:wh-wiki-circle) was determined by geo-locating the IP addresses attached to each anonymous edit on all CS-WHL articles.
 This figure shows the flow of edits, with the arrows starting at the country where the editor was located when they made their edit, and ending at the country where the CS-WHL site that they are editing is located.
@@
 Around 20% of edits of most CS-WHL articles are anonymous, a higher proportion than our random sample.
-Nevertheless, there are `r prettyNum(nrow(revision_history_page_details_ip_addresses_df), big.mark=",")` anonymous edits, and so this sample likely contains a non-random signal.
+Nevertheless, there are `r prettyNum(nrow(revision_history_page_details_ip_addresses_df), big.mark=",")` anonymous edits, and so this sample likely has some informational value in characterizing the spatial distribution of edits.
 The most striking detail in figure \@ref(fig:wh-wiki-circle) is the large proportion of edits that originate in the United States, and that the vast majority of these are edits of articles about CS-WHL sites located elsewhere in the world.
@@
 The majority of countries in this chord diagram indicate that articles about CS-WHL sites in those countries receive edits from editors located elsewhere, mostly the US and other English-speaking countries.
+
+## Temporal patterns
 
@@
 The distribution of years between the date of a site's inscription on the WHL and the date of the creation of that site's Wikipedia article has a distinctive trimodal shape.
-The first two modes reflect the relatively large number of sites inscribed on the WHL in 1983 and the early 1990s.
-The third mode at the zero point on the horizontal axis corresponds to articles that were created in or around the year the CS-WHL site was inscribed on the list.
-These are sites inscribed after the creation of Wikipedia in 2001.
+The first two modes reflect the relatively large number of sites inscribed on the WHL in 1983 and the early 1990s, before Wikipedia was created in 2001.
+The third mode at the zero point on the horizontal axis corresponds to CS-WHL sites that were inscribed after the creation of Wikipedia, and have Wikipedia articles that were created in or around the same year the CS-WHL site was inscribed on the list.
 Only a relatively small proportion of CS-WHL sites had Wikipedia articles created about them before they were inscribed on the WHL, because the majority of sites were inscribed before Wikipedia was created.
+
 The time series of editing activity at individual sites are highly variable and show display complex patterns (Figure \@ref(fig:wh-wiki-time2)).
 Timbuktu shows spikes of editing activity right after the rebel attacks in mid June 2012, with descriptions of the attacks added to the text of the article at that time.
-However the tallest peak in editing activity on the Timbuktu occurs earlier, in April 2012, those edits concentrated on expanding the sections on local prehistory.
-A detailed analysis of all the article-specific time series is beyond the scope of this paper, but we can see several patterns that suggestion interesting relationships between editorial activity and WHL listing.
-For example, editing activity spiking sharply at the time of WHL inscription (e.g.
-Tyre, Masada), editorial activity spiking at the time of WHL inscription and slowly decaying to a baseline level (e.g.
-Carthage), editorial activity that peaks shortly after the time of WHL inscription (e.g.
-Troy, Masada), and many sites where editorial activity that shows no signal at all at the time of WHL inscription (Figure \@ref(fig:wh-wiki-time2)).
+However the tallest peak in editing activity on the Timbuktu occurs slightly earlier, in April 2012, those edits concentrated on expanding the sections on local prehistory.
+A detailed analysis of all the article-specific time series is beyond the scope of this paper, but we can see several patterns indicating important relationships between editorial activities and WHL listing.
+For example, one pattern is of editing activity spiking sharply at the time of WHL inscription (e.g.
+Tyre, Masada), a second pattern is editorial activity spiking at the time of WHL inscription and slowly decaying to a baseline level (e.g.
+Carthage), a third pattern is editorial activity that peaks shortly after the time of WHL inscription (e.g.
+Troy, Masada), and finally many sites where editorial activity that shows no signal at all at the time of WHL inscription (Figure \@ref(fig:wh-wiki-time2)).
 
@@
 # References
+
 <!-- The following line ensures the references appear here for the MS Word or HTML output files, rather than right at the end of the document (this will not work for PDF files):  -->
-<div id="refs"></div>
+
+::: {#refs}
+:::
 

### 2020-11-22 analysis/paper/paper.Rmd
finished editing the text

@@
 This IP address can be used to geo-locate the user to the country they were in when the made the edit.
-We geo-located all edits with IP addresses for all Wikipedia articles CS-WHL sites to determine the country of origin of those edits.
+We geo-located all edits with IP addresses for all Wikipedia articles CS-WHL sites to determine the country of origin of those edits using the rgeolocate package for R [@rgeolocate].
 This helps us to answer the question: are the editors of articles about CS-WHL located near the sites they edit, indicating local community interest in the online representation of their heritage?
@@
 
-# Reproducibility and Open Source Materials for This Study
+# Reproducibility and Open Source Materials
 
@@
 
-Our results establish Wikipedia as site and community demonstrating active engagement with cultural heritage [@pentzold2017digging], especially cultural sites on the UNESCO World Heritage List.
-We have defined Wikipedia as an online peer production community with technical and cultural qualities that separate it from social media such as Twitter and Facebook.
-Editing mechanics, bots, reverts, and talk pages work together to enable and limit discourse and debate about CS-WHL on Wikipedia.
-The goal-driven culture of Wikipedia editors, and the organisation's policies that guide the production of articles strongly constrain heritage discourse, such that the exchange of different perspectives are rarely found in articles themselves, but buried in technical and highly specific discussions on article talk pages.
-Our results show how these distinctive qualities generate a technicity that shapes how people engage with elements of the past and attribute social and cultural meanings on Wikipedia.
-These resemble the "contingent collaborations" and "productive frictions" described by @tsing2011friction where local, individual actions of knowledge creation are circumscribed by forces and structures that encompass their expression, but also give meaning to their interactions.
+Our results establish Wikipedia as an online community actively engaging with cultural heritage [@pentzold2017digging], especially cultural sites on the UNESCO World Heritage List.
+We have defined Wikipedia as an online peer production community with technical and cultural qualities that make it distinct from social media services such as Twitter and Facebook.
+On Wikipedia, the editing mechanics, bots, reverts, and talk pages work together to enable and limit discourse and debate about CS-WHL.
+The goal-driven culture of Wikipedia editors, and the policies that guide the production of articles strongly constrain heritage discourse, such that the exchange of different perspectives are rarely found in articles themselves.
+However, we have identified conflict and tension on the article talk pages, sometimes in technical and highly specific discussions, and sometimes in overtly hostile exchanges between editors.
+Our results show how the technicity of Wikipedia shapes how people engage with elements of the past and attribute social and cultural meanings on Wikipedia.
+What we have found resembles the "contingent collaborations" and "productive frictions" described by @tsing2011friction where local, individual actions of knowledge creation are circumscribed by forces and structures that encompass their expression, but also give meaning to their interactions.
 
-We found that many of the Wikipedia articles about CS-WHL are central to the encyclopedia project.
-Many of them were among the first articles written for the encyclopedia, are more frequently viewed, are more frequently linked to by other articles, are longer, and more intensively edited by a greater variety of editors, than the average article.
+Predictably, many of the Wikipedia articles about CS-WHL are central to the encyclopedia project.
+Many of them were among the first articles written for the encyclopedia.
+They are more frequently viewed, are more frequently linked to by other articles, are longer, and more intensively edited by a greater variety of editors, than the average article.
 These results indicate the high value that Wikipedia users place on CS-WHL, consistent with the goal of the UNESCO World Heritage Committee to maintain a list reflects the world's cultural diversity of outstanding universal value.
-However, we found that sites are unequally valued, in predictable ways, given prior work on the demographics of Wikipedia users and editors, and the Eurocentric value system of the World Heritage Committee [@cleere2003uneasy; @smith2006uses p.
+Similarly, we found that the effort and attention sites receive on Wikipedia is highly unequal, reflecting the fairly narrow demographic traits of the majority of Wikipedia users and editors, which is further exacerbated by the Eurocentric value system of the World Heritage Committee [@cleere2003uneasy; @smith2006uses p.
 98].
-CS-WHL in countries in the Global South are under-represented on Wikipedia, a geographical tension that is also evident in the World Heritage List [@brumann2014shifting].
-They are also shorter and received less attention in the form of page views and inward Wikilinks.
+For example, CS-WHL in countries in the Global South are under-represented on Wikipedia, a geographical tension that is also evident in the World Heritage List [@brumann2014shifting].
+Articles about CS-WHL in the Global South are also shorter and have received less attention in the form of page views and inward Wikilinks.
 
-Perhaps the most striking spatial pattern in our results is how much of the edits to CS-WHL articles in any part of the world come from the United States.
-The anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing.
-This suggests a digital colonialism of world heritage information on Wikipedia, where heritage is interpreted and communicated by people who are not part of the descendant community traditionally associated with the site.
+The most striking spatial pattern in our results is the high proportion of anonymous edits of articles about CS-WHL sites, in any part of the world, that come from the United States.
+These anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing.
+Finding the United States at the first ranked location for anonymous edits is not surprising as it has the world's largest number of English speakers.
+We might similarly expect that the French language Wikipedia (2.3 m articles, 173 m edits, 3.9 m users) would have more edits originating in France or francophone on articles about CS-WHL sites in any part of the world.
+It is beyond the scope of this paper to analyze spatial patterns of edits in Wikipedias written in languages other than English; we focus on the English language Wikipedia because it is the largest by a considerable margin [6.2 m articles, 998 m edits, 40 m users, @wiki:listoflangs].
+
+Although the dominance of the United States in the spatial patterns is unsurprising, our data show some patterns that that language dominance cannot not fully explain.
+After the United States (297 m speakers), the top five countries for numbers of English speakers are India (238 m), Nigeria (104 m), United Kingdom (60 m), Philippines (50 m), and Germany (45 m) [@Ethnologue].
+However, our spatial data show that the countries that originate the largest numbers of edits to articles about foreign CS-WHL sites (ie.
+sites not located in the country where the edits where made) are the United States, United Kingdom, Australia and Canada.
+Although many edits originate from India, they are almost entirely of articles about CS-WHL sites also in India.
+
+The United States, United Kingdom, Australia and Canada, are an important group because they are collectively known as the core Anglosphere countries, sharing a common heritage as former colonies of the British empire [\@Richards_2019].
+\@vucetic2011anglosphere defines the Anglosphere as a 'distinct international, transnational, civilisational, and imperial entity within the global society.
+The dominance of editors of CS-WHL articles located in the Anglosphere indicates an extension of this imperial project into the organization of world heritage information on Wikipedia.
+The prominence of Anglosphere editors on CS-WHL articles articles represents a digital colonisation of world heritage information on Wikipedia, where heritage is interpreted and communicated by people who are not part of the descendant communities traditionally associated with the site.
+
 This is an important observation because it is these editors that control the production of knowledge about CS-WHL articles, and the ability to control information about heritage has several implications.
-First is that the choices of these editors define community identity, that is, the community of Wikipedia editors, and also the broader community of Internet users that read Wikipedia, by indicating which sites are important and visible, and which are not by contributing to a digital 'authorized heritage discourse' [@smith2012constrained] that prioritizes their own self-interests.
+First is that the choices of these editors define community identity, that is, the community of Wikipedia editors, and also the broader community of Internet users that read Wikipedia, by indicating which sites are important and visible, and which are not by contributing to a digital 'authorized heritage discourse' [@smith2012constrained] that prioritizes their own self-interests (cf.
+the poor representation of CS-WHL sites located in the Global South).
 Second is that traditional communities associated with CS-WHL have little control over how their own heritage is represented on Wikipedia.
 We see this spatial pattern on Wikipedia as part of a trend of globalization of heritage, where places that had traditionally contributed to local or regional identities are turned into sanitized playgrounds for rich tourists [@bernbeck2004political].
-Wikipedia may be seen as virtual playground for Americans to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities, perhaps reflecting a cultural rhetoric of 'heritage populism' [@reynie2016specter].
+Wikipedia may be seen as virtual playground for Anglosphere citizens to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities, perhaps reflecting a cultural rhetoric of 'heritage populism' [@reynie2016specter].
 In this way, the representation of heritage on Wikipedia recapitulates a long-standing tradition of colonial subordination of one group's heritage and identity by a more powerful and dominant group.
 
-This colonial logic may help to explain our findings of minimal conflicts surrounding the production of Wikipedia articles about CS-WHL.
+This colonial logic may help to explain our findings of minimal conflicts surrounding the production of CS-WHL articles.
 We found that bot activity, numbers of revert edits, and edits relating to vandalism for CS-WHL articles were comparable to or less than other sites.
@@
 Controversial sites, identified by the presence of military or diplomatic conflicts, were not prominent in these metrics.
-Our analysis of the talk pages of CS-WHL articles shows that they are often longer than a typical Wikipedia article, and are the location where conflict is most evidence.
+Our analysis of the talk pages of CS-WHL articles shows that they are often longer than a typical Wikipedia article, and are the location where conflict is most evident.
 While much of the conflict is highly technical and local about the policies and processes of editing Wikipedia, we did observe signs of the political and military conflict at CS-WHL played out on some of the talk pages, such as Mapungubwe and Preah Vihear.
@@
 The technical and cultural constraints of writing directly on the article page mean that the talk page is the only suitable location for negotiating disputes whose eventual trace in the edit history of the article might be negligible.
+
 We found that some CS-WHL talk pages referenced a 'Geopolitical, ethnic, and religious conflicts noticeboard' elsewhere on Wikipedia, as a forum for arbitration of disputes created in 2008 following a recommendation by an investigation into edit wars on articles about Northern Ireland (The Troubles), Palestine-Israel and other locations with ethnic or cultural based conflicts.
 However the noticeboard was closed in 2012 due to an absence of activity.
-Overall we find that editors of CS-WHL articles appear conflict-averse, probably because many of them come from similar cultural, socio-economic and educational backgrounds, and so share similar values about heritage that align with their shared goal of making an encyclopedia.
+Overall we find that editors of CS-WHL articles appear conflict-averse, probably because many of them come from similar cultural, socio-economic and educational backgrounds due to their Anglosphere origins.
+This means they share similar values about heritage that align with their shared goal of making an encyclopedia.
 The low levels of conflict reflect the continuity between the printed encyclopedia project as a compendium of universal knowledge, and the World Heritage List as universal heritage.
-These projects share origins in the cultural elites of Western European, and their distinctive sense of what is universal that is linked to nineteenth-century nationalism and liberal modernity [@smith2006uses].
+These projects share origins in the cultural elites of Western Europe, and their distinctive sense of what is universal that is linked to nineteenth-century nationalism and liberal modernity [@smith2006uses].
 
@@
 However at other sites the rhythms of editing activity seem unrelated to events directly related to the site.
-Like the talk pages, which have unrealised potential for close reading of heritage activism and disputes, close study individual edit histories of CS-WHL articles may reveal further patterns of how people engage with heritage on Wikipedia.
+Like the talk pages, which have potential for close reading of heritage activism and disputes, close study of individual edit histories of CS-WHL articles may reveal further patterns of how people engage with heritage on Wikipedia.
 
@@
 Although there are some niches where editors can debate, concerns about state-like actors, violence & destruction, deal-making, etc.
-are poorly represented.
-Typical conflicts about Wikipedia CS-WHL articles are hyper-local, and process-centered.
-Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the United States.
+are minor.
+Typical conflicts about Wikipedia CS-WHL articles are hyper-local, and process-centered, but there are also cases of editorial conflicts about substantive issues of specific CS-WHL.
+Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the Anglosphere, and poor coverage of CS-WHL in the Global South.
 Because of these technical and cultural characteristics of Wikipedia, its articles present a discourse that actively obscures the power relations that give rise to them, and makes opaque debates about how heritage is involved in the production of identity and power [cf.
@@
 This has important ethical implications because it eliminates the need for academic collaboration with commercial platforms, whose business interests may not align with the researchers' ethics [@schroeder2014big].
-ALthough free of these commercial interests, a different set of ethics is implied by the exquisite administrative and technical complexity of Wikipedia.
+Although free of these commercial interests, a different set of ethics is implied by the exquisite administrative and technical complexity of Wikipedia.
 These structures serve to normalize and historize inequalities, and manage threats to models of control and expertise about heritage [@harrison2015beyond].
 As a context of heritage production, a resource of information on heritage, and an artefact of contemporary digital heritage, Wikipedia is remarkable and holds substantial research potential.
-While the Neutral Point of View is a central policy for Wikipedia articles, representations and definitions of cultural heritage are never neutral in any discourse, because it always comes from some perspective [@lahdesmaki2019conflicts].
+While the Neutral Point of View is a central policy for Wikipedia articles, representations and definitions of cultural heritage are never neutral in any discourse, because they always come from some perspective [@lahdesmaki2019conflicts].
 Given the tremendous popularity and visibility of Wikipedia, is it important that future work on digital heritage in this context continue to critically examine what is absent from, and uncontested in, Wikipedia, and who benefits and suffers from these absences.

### 2020-11-24 analysis/paper/paper.Rmd
resubmit after revisions with peer reviews

@@
 ---
-title: "World Heritage Sites on Wikipedia: Controversies in a Context of Constrained Agency for Cultural Heritage Activism"
+title: "World Heritage Sites on Wikipedia: Cultural Heritage Activism in a Context of Constrained Agency"
 author:
@@
     bookdown::word_document2:
+      number_sections: false
       fig_caption: yes
@@
 Concerns about state-like actors, violence and destruction, deal-making, etc.
-in the World Heritage inscription process are poorly represented on Wikipedia’s World Heritage pages, instead hyper-local, and process issues dominate controversies on Wikipedia.
-We will consider how this kind of research, drawing on big data and data science methods, adds new dimensions to the debate on heritage controversies, especially its unique contributions, and also its limitations.
+in the World Heritage inscription process are present, but rare on Wikipedia’s World Heritage pages.
+Instead hyper-local, and process issues dominate controversies on Wikipedia.
+We describe how this kind of research, drawing on big data and data science methods, contributes to digital heritage studies, and also reveals its limitations.
 ---
@@
 
-# Introduction
+# Introduction {-}
 
@@
 
-## Wikipedia as a Context of Heritage Production
+## Wikipedia as a Context of Heritage Production {-}
 
@@
 Wikipedia has a special category of edit called the 'revert' which allows a user to restore an article to an earlier state to remove recent vandalism (such as the addition of irrelevant or offensive material).
-This special revert action, combined with a 'talk' page attached to each encyclopedia article for threaded discussion among editors, allows us to detect and study the social dynamics arising from the creation and editing of articles, for example the controversiality of an article [@yasseri2012dynamics; \@suh2007us].
+This special revert action, combined with a 'talk' page attached to each encyclopedia article for threaded discussion among editors, allows us to detect and study the social dynamics arising from the creation and editing of articles, for example the controversiality of an article [@yasseri2012dynamics; @suh2007us].
 While articles themselves must be written to conform to the fundamental Wikipedia policy of NPOV (Neutral Point Of View), the talk page is where different views are expressed and negotiated among editors in detail.
@@
 
-## UNESCO World Heritage Cultural Sites
+## UNESCO World Heritage Cultural Sites {-}
 
@@
 ```{r wh-unesco-map, fig.cap="Cultural Sites on the UNESCO World Heritage List.
-Countried coloured black currently have no listed cultural sites.
+Countries coloured black currently have no listed cultural sites.
 Inset shows the distribution of sites per country.
@@
 
-# Methods
+# Methods {-}
 
@@
 We used the SelectorGadget [@cantino2017selectorgadget] extension for the Chrome web browser to identify specific page elements of interest, or nodes, on the HTML pages, and wrote custom R functions to extract data from these nodes.
-Our entry points were the Wikipedia articles that are lists of World Heritage regions in major geographical regions of the globe.
+Our entry points were the Wikipedia articles that are lists of World Heritage sites in major geographical regions of the globe.
 We found fifteen of these, and scraped the CS-WHL site names from the tables on these pages, and followed the links to scrape the article text, edit history and talk page text for each CS-WHL site included on those tables.
 A small number of CS-WHL sites have Wikipedia articles that are not included on these tables, we did not include these in our sample.
-Starting at these regional lists of sites was a pragmatic choice because the individual Wikipedia article titles for CS-WHL sites often differ from the official site name on the UNESCO list.
-A limitation of this approach is that it excludes possible 'orphan' pages for CS-WHL that, while present in Wikipedia, have not been curated by editors into a table listing all the sites in a region.
-On the other hand, this approach ensures that our all sites in our sample are meaningful by sharing the essential quality of a taxonomic status of being categorized by Wikipedia editors as a CS-WHL in a certain region.
+Starting at these regional lists of sites was a pragmatic choice because the individual Wikipedia article titles for CS-WHL sites very frequently differ from the official site name on the UNESCO list.
+A limitation of this approach is that it excludes 'orphan' pages for CS-WHL that, while present in Wikipedia, have not been curated by editors into a table listing all the sites in a region.
+Thus our sample is not the complete set of articles about CS-WHL, but only those that have been curated into regional groups.
+This approach ensures that our all sites in our sample are meaningful by sharing the essential quality of a taxonomic status of being categorized by Wikipedia editors as a CS-WHL in a certain region.
 
@@
 
-# Reproducibility and Open Source Materials
+# Reproducibility and Open Source Materials {-}
 
@@
 
-# Results
+# Results {-}
 
@@
 
-## Article content
+## Article content {-}
 
@@
 
-## Article production
+## Article production {-}
 
@@
 
-## Article consumption
+## Article consumption {-}
 
@@
 
-## Spatial patterns
+## Spatial patterns {-}
 
@@
 Inset shows the distribution of numbers of CS-WHL articles per country.
+Countries coloured black currently have no CS-WHL with Wikipedia articles.
 Map data from naturalearthdata.com", fig.width=15}
@@
 
-## Temporal patterns
+## Temporal patterns {-}
 
@@
 
-# Discussion
+# Discussion {-}
 
@@
 
-The United States, United Kingdom, Australia and Canada, are an important group because they are collectively known as the core Anglosphere countries, sharing a common heritage as former colonies of the British empire [\@Richards_2019].
-\@vucetic2011anglosphere defines the Anglosphere as a 'distinct international, transnational, civilisational, and imperial entity within the global society.
+The United States, United Kingdom, Australia and Canada, are an important group because they are collectively known as the core Anglosphere countries, sharing a common heritage as former colonies of the British empire [@Richards2019].
+@vucetic2011anglosphere defines the Anglosphere as a 'distinct international, transnational, civilisational, and imperial entity within the global society.
 The dominance of editors of CS-WHL articles located in the Anglosphere indicates an extension of this imperial project into the organization of world heritage information on Wikipedia.
 The prominence of Anglosphere editors on CS-WHL articles articles represents a digital colonisation of world heritage information on Wikipedia, where heritage is interpreted and communicated by people who are not part of the descendant communities traditionally associated with the site.
+Although we could only geo-locate about 20% of edits, our spatial patterns resemble those found by @Mandiberg_2020 who examined 884 m edits to the English Wikipedia and found that at the country level, the 'five largest contributors were part of what once was the British Empire, and account for nearly 75 percent of all editors'.
 
@@
 The low levels of conflict reflect the continuity between the printed encyclopedia project as a compendium of universal knowledge, and the World Heritage List as universal heritage.
-These projects share origins in the cultural elites of Western Europe, and their distinctive sense of what is universal that is linked to nineteenth-century nationalism and liberal modernity [@smith2006uses].
+These projects share origins in the cultural elites of Western Europe, and their distinctive sense of what is universal that is linked to nineteenth-century nationalism and liberal modernity, vestiges of which are still evident in the modern political philosophy of the Anglosphere [@smith2006uses].
 
@@
 
-# Conclusion
+# Conclusion {-}
 
@@
 are minor.
-Typical conflicts about Wikipedia CS-WHL articles are hyper-local, and process-centered, but there are also cases of editorial conflicts about substantive issues of specific CS-WHL.
+Typical conflicts about Wikipedia CS-WHL articles are hyper-local, and process-centered.
+There are also cases of editorial conflicts about substantive issues of specific CS-WHL, such as Mapungubwe and Preah Vihear, that include editors with a personal investment in the debate, if not the article.
 Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the Anglosphere, and poor coverage of CS-WHL in the Global South.
@@
 These structures serve to normalize and historize inequalities, and manage threats to models of control and expertise about heritage [@harrison2015beyond].
-As a context of heritage production, a resource of information on heritage, and an artefact of contemporary digital heritage, Wikipedia is remarkable and holds substantial research potential.
+As a context of heritage production, a resource of information on heritage, and itself an artefact of contemporary digital heritage, Wikipedia is remarkable and holds substantial research potential.
 While the Neutral Point of View is a central policy for Wikipedia articles, representations and definitions of cultural heritage are never neutral in any discourse, because they always come from some perspective [@lahdesmaki2019conflicts].
@@
 
-# Acknowledgements
+# Acknowledgments {-}
 
@@
 This conference was part of the AHRC-funded project 'Ancient Identities in Modern Britain' and the AHRC Heritage Priority Area Leadership Fellowship.
+Thanks to the three anonymous peer reviewer and Matthew Zook for their comments that greatly improved the final paper.
 
-# References
+# References {-}
 

### 2020-11-24 analysis/paper/001-UNESCO-CS-WHL-world-map-counts.R

@@ -40,6 +40,17 @@ wh_unesco_countries <-
     TRUE ~ as.character(states_name_en)
   ))
 
+
+wh_unesco_countries$states_name_en <-
+  ifelse(str_detect(wh_unesco_countries$name_en, "Greenland"),
+         "Greenland",
+         wh_unesco_countries$states_name_en)
+
+wh_unesco_countries$country <-
+  ifelse(str_detect(wh_unesco_countries$name_en, "Greenland"),
+         "Greenland",
+         wh_unesco_countries$country)
+
 wh_unesco_countries_count <-
   wh_unesco_countries %>%
   separate_rows(states_name_en, sep = ",") %>%
@@ -70,7 +81,8 @@ sf_map_data_unesco <-
   left_join(wh_unesco_countries_count,
             by = c( 'name_long' = 'country')) %>%
   select(name, n, geometry) %>%
-  mutate(n = ifelse(is.na(n), 0, n)) %>%
+  # sites with no CHL-WS: 0 or NA?
+  # mutate(n = ifelse(is.na(n), 0, n)) %>%
   filter(name != "Antartica")
 
 wh_country_unesco_count_map <-

### 2020-11-24 analysis/paper/002-Wikipedia-CS-WHL-world-map-counts.R

@@ -127,7 +127,7 @@ sf_map_data <-
    left_join(wh_wk_country_counts,
             by = c( 'name' = 'country2')) %>%
   select(name, n, geometry) %>%
-  mutate(n = ifelse(is.na(n), 0, n)) %>%
+ # mutate(n = ifelse(is.na(n), 0, n)) %>%
   filter(name != "Antartica") # %>% sf::st_drop_geometry() %>% View
 
 ###
@@ -138,7 +138,7 @@ sf_map_data <-
 wh_wk_country_count_map <-
   ggplot(data = sf_map_data) +
   geom_sf(aes(fill = n), lwd = 0) +
-  scale_fill_viridis_c(# na.value="black",
+  scale_fill_viridis_c(na.value="black",
                        name = "Number of\nWikipedia articles\non CS-WHL") +
   coord_sf(ylim = c(-50, 90), datum = NA) +
   theme_minimal(base_size = 8)  +
@@ -194,16 +194,16 @@ sf_map_data_unesco %>%
     name == "United States" ~ "United States of America",
     name == "Czech Rep." ~ "Czech Repu", # no idea why
     TRUE ~ as.character(name))) %>%
-  left_join(sf_map_data_unesco_wk_prop) %>%
-  mutate(prop_sites_with_wp_articles = ifelse(is.na(prop_sites_with_wp_articles),
-                                              0,
-                                              prop_sites_with_wp_articles))
+  left_join(sf_map_data_unesco_wk_prop)# %>%
+ # mutate(prop_sites_with_wp_articles = ifelse(is.na(prop_sites_with_wp_articles),
+ #                                             0,
+ #                                             prop_sites_with_wp_articles))
 
 
 wh_wk_country_prop_map <-
   ggplot(data = sf_map_data_unesco_wk_prop_sf) +
   geom_sf(aes(fill = prop_sites_with_wp_articles), lwd = 0) +
-  scale_fill_viridis_c( #na.value="black",
+  scale_fill_viridis_c(na.value="black",
                        name = "Proportion of CS-WHL\nsites in a country that\nhave Wikipedia\narticles") +
   coord_sf(ylim = c(-50, 90), datum = NA) +
   theme_minimal(base_size = 8)  +

### 2020-11-24 analysis/paper/008-Wikipedia-WHL-time-series.R

@@ -73,12 +73,14 @@ bind_rows(
 
 ) %>%
   ggplot() +
-  geom_density(aes(as.numeric(edit_span / 365),
+  # seconds to years
+  geom_density(aes(as.numeric(edit_span / 31536000),
                    fill = source),
                alpha = 0.3) +
   geom_vline(xintercept = year(Sys.Date()) - 2001,
              colour = "red") +
-  annotate("text", x = 15, y = 0.2, label = "start of Wikipedia → ") +
+  annotate("text", x = 15, y = 0.2,
+           label = "start of Wikipedia → ") +
   xlab("Age of Wikipedia page (years)") +
   scale_fill_viridis_d(labels = c("Random",
                                   "CS-WHL"),

### 2020-11-24 analysis/paper/009-ethnologue-english-speakers.R
add ethnologue code

@@ -1,0 +1,30 @@
+# highly iconic sites in the Western canon of culture history
+
+# Only one of the controversial sites discussed above is in the group of articles where the talk page is longer than the article itself, and none of the site on the UNESCO heritage in danger list are in this group.
+
+
+library(tidyverse)
+library(rvest)
+
+el <- here::here("analysis/data/raw_data/English _ Ethnologue.htm")
+
+number_of_speakers <-
+el %>%
+  read_html() %>%
+  html_nodes(".views-field-field-population-1 .field-content") %>%
+  html_text() %>%
+  str_remove_all(" in .*") %>%
+  parse_number()
+
+country <-
+  el %>%
+  read_html() %>%
+  html_nodes(".views-field-field-population-1 .field-content") %>%
+  html_text() %>%
+  str_remove_all(", all users.*") %>%
+  str_remove_all(".* in ")
+
+
+tibble(country = country,
+       number_of_speakers= number_of_speakers) %>%
+  arrange(desc(number_of_speakers)) %>% View

### 2020-11-25 analysis/paper/paper.Rmd
reduce wordcount to under 10k, many small edits

@@
 It follows that user interactions in the process of generating content in online peer production communities includes technological and social mechanisms that enact the community's governance policies, for example, limiting a user's activity according to their status in the community's hierarchy, or managing conflict with highly structured procedures.
-Here we show how the distinctive organizational and technical qualities of online peer production communities make them an intriguing novel context of heritage production to study digital traces of human activity resulting from engagement with the past.
-We show how these technological and social mechanisms constrain the representation of controversies about CS-WHL.
+Here we show how the distinctive organizational and technical qualities of online peer production communities make them a unique context of heritage production to study digital traces of human activity resulting from engagement with the past.
 
@@
 Originating in 2001, this is a highly influential and well-known online encyclopedia, that anyone can edit, currently with 11 billion page views per month (<https://stats.wikimedia.org/#/en.wikipedia.org>).
-Although anyone can edit, most internet users do not, and the characteristics of people who do edit are important to understand to identify biases in the encyclopedia's content.
-In a survey of 1,512 American adults, @shaw2018pipeline found that majority of internet users (96.5%) had heard of Wikipedia, and 82.5% of those said that they had ever visited the site.
-Just over two thirds (67.3%) knew that Wikipedia can be edited, but only 8.2% of the full sample had ever edited any page.
-Factors that strongly predict if a user has ever edited Wikipedia include their gender (male), age (younger), education level (has BA), Internet use frequency (higher) and Internet use skills (higher).
-@hill2013wikipedia a similarly found that among U.S.
-adult contributors to the English-language edition of Wikipedia, at least 75% are male.
-While gender disparities have been documented throughout Wikipedia [@adams2015wikipedia; @ford2017anyone], there are also geographical disparities.
-@johnson2016not examined 218,709 English geotagged articles about places in the contiguous United States and 46,124 Chinese geotagged articles about places in China to investigate differences in articles about urban and rural places.
-They found that articles about rural areas have systematically lower quality, are less likely to have been produced by contributors who focus on the local area, and are more likely to have been generated by bots (automated software agents).
-These studies indicate that inequalities on a range of variables mean that participation in online peer production communities often exacerbates existing patterns of social exclusion.
+Although anyone can edit, most internet users do not.
+Factors that strongly predict if a user has ever edited Wikipedia include their gender (male), age (younger), education level (has BA), Internet use frequency (higher) and Internet use skills (higher) [@shaw2018pipeline; @hill2013wikipedia; @adams2015wikipedia; @ford2017anyone].
+There are also geographical disparities.
+Articles about rural areas have systematically lower quality, are less likely to have been produced by contributors who focus on the local area, and are more likely to have been generated by bots (automated software agents) [@johnson2016not].
+These studies indicate that participation in online peer production communities often follow existing patterns of social exclusion.
 @graham2014uneven examined the global distribution of 3.4 million geotagged Wikipedia articles and find a pattern of places in the Global North being represented in local languages, while articles about places in the Global South are largely being written by others.
-They find that most of the variation in the spatial distribution of geotagged articles could be explained by three variables: the population of the country, the number of fixed broadband connections, and the number of edits emanating from that country.
 
@@
 On the other hand, they constrain and limit the agency of the user, canalizing their behaviour into a small number of possible actions and acceptable modes of discourse and engagement with other users [@iba2010analyzing].
-While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity, resulting in very specific types of relationships between human users and the technical elements of the Wikipedia project [@niederer2010wisdom; @weltevrede2016platform].
+While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity, resulting in specific types of relationships between human users and the technical elements of the Wikipedia project [@niederer2010wisdom; @weltevrede2016platform].
 For example, every edit to an article is tracked in a publicly accessible version control system attached to that article.
@@
 This special revert action, combined with a 'talk' page attached to each encyclopedia article for threaded discussion among editors, allows us to detect and study the social dynamics arising from the creation and editing of articles, for example the controversiality of an article [@yasseri2012dynamics; @suh2007us].
-While articles themselves must be written to conform to the fundamental Wikipedia policy of NPOV (Neutral Point Of View), the talk page is where different views are expressed and negotiated among editors in detail.
-
-```{r bot-table}
-library(tidyverse)
-
-bot_table <- 
-  tribble(~"Role", ~"Function", ~"Example",
-          "Generator", "Generate article pages based on predefined templates.", "Rambot, RussBot",
-          "Fixer", "Fix errors in article pages in order to keep the information neat and correct.", "CmdrObot, Yobot",
-          "Connector", "Connect Wikipedia with other sites and databases", "KasparBot",
-          "Tagger", "Tag articles with different templates and categories", "AnomieBot, Smackbot, Cydebot",
-          "Clerk", "A variety of tasks including updating statistical information, documenting user status, updating maintenance pages", "AnomieBot, Smackbot",
-          "Archiver", "Archive closed discussions and maintain the archived content by assigning an index and sorting them alphabetically", "AnomieBot, Cyberbot_I",
-          "Protector", "Detect and regulate destructive behaviors", "ClueBot NG",
-          "Advisor", "Provide editors with suggestions about articles that they might want to contribute to.", "SuggestBot",
-          "Notifier", "Deliver messages to editors.", "NoomBot"
-          )
-
-knitr::kable(bot_table, caption = "Summary of Wikipedia bot types and functions, from Zheng et al. (2019)")
-```
+While articles themselves must be written to conform to the fundamental Wikipedia policy of NPOV (Neutral Point Of View), the talk page is where different views are expressed and negotiated among editors.
 
 In addition to the human users and the technological system that enables and constrains their activities on Wikipedia, there is an important third element of the ecosystem that contributes to Wikipedia's uniqueness: the bots.
-Wikipedia bots are computer scripts that automatically handle repetitive and mundane tasks to develop, improve, and maintain the encyclopedia.
-While bots are not unique to Wikipedia, they are important contributors, responsible for a large proportion of edits, and shape the human experience in significant ways [@niederer2010wisdom; @geiger2009social; @geiger2014bots].
+Wikipedia bots are computer scripts that automatically handle repetitive and mundane tasks to develop, improve, and maintain the encyclopedia [@zheng2019roles].
+While bots are not unique to Wikipedia, they are important contributors, and are responsible for a large proportion of edits [@niederer2010wisdom; @geiger2009social; @geiger2014bots].
 They also evolve and autonomously engage in complex interactions with other bots to modify the encyclopedia [@tsvetkova2017even; @geiger2017operationalizing].
-@zheng2019roles studied all 1,601 bots that were registered at the time of their study, and classified them into 9 bot roles and 25 associated bot functions.
-Table \@ref(tab:bot-table) shows the bots that were identified in our study and their categories and functions according to @zheng2019roles.
 
@@
 # from https://whc.unesco.org/en/syndication on 22 May 2020
+library(tidyverse)
 wh_unesco <- 
@@
 
-We investigate how the unique technicity of Wikipedia shapes interactions between people and the past with a case study on the processes of constructing knowledge about cultural sites inscribed on the WHL.
+We investigate how the unique technicity of Wikipedia shapes interactions between people and the past with a case study of cultural sites inscribed on the WHL.
 We chose the CS-WHL as a bounded set of cultural heritage elements with several characteristics that make it of general interest.
@@
 
-In her institutional ethnography of UNESCO's role in protecting world heritage, @meskell2018future argues that the WHL is less about preserving heritage than about political and economic transactions between states and state-like actors.
-Sites that are listed, or candidates for listing, are often foci of disputes and negotiations about territory, sovereignty, and security, as well as international corporate activity [@meskell2018future].
-This is because the process of selecting of sites to be inscribed on the WHL has become politicized and driven by countries' political influence and national strategic interests [@bertacchini2016politicization].
-For example, the members of the World Heritage Committee are mostly career diplomats rather than heritage specialists, indicating that the processes and decisions of this committee may be motivated more by political trade-offs than by heritage expertise and judgment [@von2011concept].
-
-Several CS-WHL sites are notable for the conflicts and tensions that have surrounded their inscription.
+Several CS-WHL sites are notable for the conflicts and tensions that have surrounded their inscription [@meskell2018future].
 The 1992 inscription of Angkor (an ancient city and empire in Cambodia, prominent during the 9th to the 15th centuries AD) was supported by exiled supporters of the genocidal Khmer Rouge regime, hoping to strengthen territorial claims [@locard2015myth].
@@
 
-Physical conflicts at or near CS-WHL are also major events that galvanize public interest in these locations.
-World Heritage sites in Palestine, Mali, Syria, Congo and Cambodia have recently been sites of violence, in many cases specifically linked to their potential WHL nomination, listing or management.
+Physical conflicts at or near CS-WHL are major events that also galvanize public interest in these locations.
+World Heritage sites in Palestine, Mali, Syria, Congo and Cambodia have recently been sites of violence, in many cases specifically linked to their potential WHL nomination, listing, or management.
 In 1998 anti-government and mostly Hindu Tamil groups bombed the holy Buddhist site of the Temple of the Tooth at the WHL site of Kandy (the last capital of the ancient kings of Sri Lanka), killing 17 people and substantially damaging the temple [@coningham1999paradise].
@@
 Although both Thailand and Cambodia supported the nomination of the site to the WHL, the Thai government objected to maps in the nomination package that showed Cambodia as the owner of disputed land next to the temple, leading to protests and military clashes [@sothirak2013cambodia].
-@meskell2020world's analysis of US diplomatic cables released by WikiLeaks further reveals that settlement of disputes over Preah Vihear were intricately tied to broader issues of foreign policy and US and Chinese investment, especially access to natural gas reserves in the Gulf of Thailand.
-For example, the cables reveal negotiations for Cambodia to retain their temple, leading to the enhancement of Thailand's underwater assets, and the United States negotiating for extended contracts with both countries.
+US diplomatic cables released by WikiLeaks reveal that settlement of disputes over Preah Vihear were intricately tied to broader issues of foreign policy and US and Chinese investment, especially access to natural gas reserves in the Gulf of Thailand [@meskell2020world].
 
@@
 Our goal in this study is to answer the question of how this interest is expressed within the socio-technical constraints of Wikipedia.
-We attempt to answer this question by studying all the CS-WHL that have Wikipedia articles.
 We surveyed the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics).
-There are many other additional metrics available for Wikipedia articles, an we have limited ourselves to the most basic for this initial investigation to establish a baseline for future studies that might similarly investigate Wikipedias written in languages other than English.
 By comparing these basic characteristics of Wikipedia articles about CS-WHL to 10,000 random Wikipedia articles we can approach the question: can metrics of content, consumption, and production indicate engagement with the past via CS-WHL on Wikipedia?
@@
 This helps us to answer the question: are the editors of articles about CS-WHL located near the sites they edit, indicating local community interest in the online representation of their heritage?
-Or are editors located in other countries, implying a digital colonialism of world heritage information on Wikipedia where one community's heritage is interpreted and communicated by another?
 The time and date stamps attached to every edit on every article allows us to investigate temporal patterns of activity on CS-WHL Wikipedia articles.
@@
 
-The highly structured nature of most Wikipedia pages afforded us much efficiency during data collection, however, a not insignificant number of pages had technical irregularities, for example, exotic table formatting or minor deviations from widely used templates, that necessitated more complex programming for data collection.
-An especially challenging issue was irregularities in spelling place names, for example, "Saint Kitts and Nevis" and "St.
-Kitts and Nevis", which can confound programmatic joining and summarizing of data by failing to recognize as the same place and leading to under-counting.
-We attempted to correct these manually in our code.
-Another challenge was in the formatting of tables on Wikipedia pages, for example a merged cell in a table introduced an irregularity that made parsing and scraping complicated and fragile.
-We collected data during May 2019, and due to the dynamic nature of Wikipedia, it is highly likely that articles in our study have subtly changed since our data collection as users and bots continue their activity.
-It is possible that new articles have since appeared about sites that were not represented on Wikipedia since we collected the data.
-Our original scraping code may no longer work on the most current version of Wikipedia without modification as the tables on Wikipedia articles continue to be modified by editors.
-
 # Reproducibility and Open Source Materials {-}
 
+We collected data during May 2019, and due to the highly dynamic nature of Wikipedia, it is  likely that articles in our study have subtly changed since our data collection.
+It is possible that new articles have since appeared about sites that were not represented on Wikipedia since we collected the data.
+Our original code may no longer work on the most current version of Wikipedia without modification as the tables on Wikipedia articles continue to be modified by editors.
 Although we recognize that the fragility and temporally specific nature of our methods limits the reproducibility of our results, we include the entire R code [@rprogram] used for all the analysis and visualizations contained in this article in our compendium at <http://doi.org/10.17605/OSF.IO/AY27G> to enable reuse of our materials and improve reproducibility and transparency [@marwick2017computational].
@@
 
-Of the `r nrow(wh_unesco)` cultural sites on the World Heritage List at the time of writing, we found Wikipedia articles for `r nrow(some_page_variables)`.
-To characterize the overall variability of article according to the basic characteristics described above, we applied a Uniform Manifold Approximation and Projection (UMAP) to reduce the dimensionality of our data [@mcinnes2018umap].
-After a two-dimensional projection was obtained, we used Hierarchical Density-Based Spatial Clustering of Applications with Noise (HDBSCAN) to identify clusters [@campello2013density], and Random Forests to identify variable loadings [@breiman2001random] so we could determine which of the basic characteristics were most important in driving variability between the articles.
-This revealed `r n_clusters` clusters, with the most important variables for determining cluster membership being the number of items in the reference list at the end of the article, the number of words in the article, and the number of Wikilinks out from the target article to other Wikipedia articles.
-Put simply, articles about CS-WHL vary the most in how detailed and researched they are.
-That said, `r n_no_cluster` (`r round(prop_no_cluster * 100)`%) articles were not assigned to a cluster by the HDBSCAN algorithm, indicating that the basic characteristics of CS-WHL articles do not partition the articles in highly structured and discrete groups.
-
 ```{r wh-wiki-content-and-consumption, fig.cap="Content and consumption of Wikipedia articles about CS-WHL.
@@
 
+Of the `r nrow(wh_unesco)` cultural sites on the World Heritage List at the time of writing, we found Wikipedia articles for `r nrow(some_page_variables)`.
 As a group, the basic details of content for Wikipedia articles for CS-WHL differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
@@
 The most active bot on CS-WHL articles is Cluebot NG (vandalism detection and reverting), compared to Cydebot (automatic implementation of category deletions) for the random articles.
-The AnomieBOT is very active on CS-WHL articles compared to random articles, this bot performs clerical duties in an article's reference list.
-Most bot edits on on CS-WHL articles are in the fixer, tagger, connector, and clerk roles.
+The AnomieBOT is highly active on CS-WHL articles compared to random articles, this bot performs clerical duties in an article's reference list.
+Most bot edits on on CS-WHL articles are in the fixer, tagger, connector, and clerk roles [@zheng2019roles].
 None of these articles with intensive bot activity are CS-WHL sites of conflict or on the List of World Heritage in Danger, indicating that these sites receive little or no vandalism.
@@
 
-For the special 'revert' edit type, we see that the proportion of all edits per CS-WHL articles is similar to other articles, but has a left-skewed distribution indicating a higher number of articles that have very few revert edits (Figure \@ref(fig:wh-wiki-vandal-revert)).
+For the special 'revert' edit type, we see that the proportion of all edits per CS-WHL articles is similar to other articles, but has a left-skewed distribution indicating a higher number of articles that have few revert edits (Figure \@ref(fig:wh-wiki-vandal-revert)).
 We also identified edits with the string 'vandal' in the edit summary as a similar type of edit to the revert edit, e.g.
@@
 CS-WHL articles generally have fewer edits about vandalism than our random sample.
-The shape of the distribution of edits about vandalism has a smaller second mode to the left of the peak, indicating that a large number of CS-WHL articles have very few edits about vandalism (Figure \@ref(fig:wh-wiki-vandal-revert)).
+The shape of the distribution of edits about vandalism has a smaller second mode to the left of the peak, indicating that a large number of CS-WHL articles have few edits about vandalism (Figure \@ref(fig:wh-wiki-vandal-revert)).
 Among the CS-WHL articles that have high proportions of reverts and edits about vandalism are highly iconic sites in the Western canon of culture history, e.g.
@@
 Talk pages for CS-WHL articles tend to be much longer than other articles, which we expect due to the CS-WHL articles themselves being generally longer than other articles.
-However, the distribution of talk page lengths for CS-WHL articles has a long right tail, indicating that a higher number of articles have very long talk pages, compared to other articles.
+However, the distribution of talk page lengths for CS-WHL articles has a long right tail, indicating that a higher number of articles have long talk pages, compared to other articles.
 Some of these articles with long talk pages, such as Cologne Cathedral and Troy, have clear evidence of conflict among the editors in the contents of the text.
 However, close reading of the discussions on these talk pages reveals that these debates are dominated by technical issues of article production, rather than conflicts and tensions at the CS-WHL or surrounding their inscription.
-For example, the Cologne Cathedral talk page includes some debate about the correct calculation of the interior volume of the structure, and on Troy talk page includes heated comments by one editor about another editor removing of some of their text containing unsourced claims and unencyclopedic writing style.
+For example, the Cologne Cathedral talk page includes some debate about the correct calculation of the interior volume of the structure, and the Troy talk page includes heated comments by one editor about the removal of unsourced claims and unencyclopedic prose.
 
@@
 In this remarkable case we see the Wikipedia editors engaging conflicts that go beyond the typical technical details of article production.
-What is especially notable about these discussions on the talk page is how closely they echo the themes identified by @meskell2011paris in her analysis of the WHC process.
-The editors involved in this debate did not make any edits to the article itself which raises questions about their motivations for engaging in debate on the talk page, since they are not personally invested in the content of the article.
+What is especially notable about these discussions on the talk page is how closely they echo the debates of land ownership that complicated the WHC process [@meskell2011paris].
+The editors involved in this debate did not make any edits to the article itself which raises questions about their motivations for engaging in debate on the talk page, since they do not seem personally invested in the content of the article.
 Without directly interviewing these editors, we cannot be sure of their motives for participating in the talk page.
@@
 Although not notable for the length of its talk page, the discussions among editors of the article about Preah Vihear Temple include a strongly worded disagreement among seven editors about the legitimacy of the ownership claims by Thailand and Cambodia of the territory that includes the temple.
-As for Mapungubwe, the debate among Wikipedia editors mirrors very closely the political tensions surrounding the nomination of Preah Vihear.
+As for Mapungubwe, the debate among Wikipedia editors mirrors closely the political tensions surrounding the nomination of Preah Vihear.
 The talk page also has a lengthy argument from to 2008, involving several editors, about whether or not the Thai name of the site should be included in the text of the article.
@@
 They are also much more often linked to by other Wikipedia articles than our random sample of other articles, indicating consumption by other Wikipedia articles and Wikipedia users in their editing work (Figure \@ref(fig:wh-wiki-content-and-consumption)).
-This indicates that consumption of CS-WHL articles is generally very high, relative to other articles, and confirms our assertion of Wikipedia as an important source of heritage information.
+This indicates that consumption of CS-WHL articles is generally high, relative to other articles, and confirms our assertion of Wikipedia as an important source of heritage information.
 But is how is attention distributed across all CS-WHL articles, and how does it relate to sites with conflicts and tensions?
@@
 The majority of talk page content for Timbuktu is about filling in missing detail, suggestions for or notifications of minor corrections.
-This is also the case for the talk page for Auschwitz, another very popular CS-WHL article with six archived talk pages including over 100,000 words.
-Although Wikipedia articles in other languages on Auschwitz have different points of emphasis [@wolniewicz2016framing], the majority of the discussion among editors on the talk pages is generally technical and precise.
+This is also the case for the talk page for Auschwitz, another popular CS-WHL article with six archived talk pages including over 100,000 words.
+Although Wikipedia articles in other languages on Auschwitz have different points of emphasis [@wolniewicz2016framing], the majority of the discussion among editors on the talk pages is technical and precise.
 Provocative comments on the English language Auschwitz talk pages, for example by editors denying the Holocaust, usually end after brief exchanges with other editors requesting credible sources.
@@
 The lower panel of figure \@ref(fig:wh-wiki-map) further demonstrates this with South American countries having low proportions of their CS-WHL sites represented on Wikipedia.
-The pattern in African countries is that they either have a very small number of sites that are all on Wikipedia (indicated by yellow on the figure), or they do not have any CS-WHL at all.
+The pattern for African countries is that they either have a very small number of sites that are all on Wikipedia (indicated by yellow on the figure), or they do not have any CS-WHL.
 
@@
 The country with the next highest proportion of editors is India, and nearly half of those edits are on CS-WHL sites located India.
-The majority of countries in this chord diagram indicate that articles about CS-WHL sites in those countries receive edits from editors located elsewhere, mostly the US and other English-speaking countries.
+Generally, articles about CS-WHL sites receive edits from editors located elsewhere, mostly the US and other English-speaking countries.
 
@@
 Our results show how the technicity of Wikipedia shapes how people engage with elements of the past and attribute social and cultural meanings on Wikipedia.
-What we have found resembles the "contingent collaborations" and "productive frictions" described by @tsing2011friction where local, individual actions of knowledge creation are circumscribed by forces and structures that encompass their expression, but also give meaning to their interactions.
+What we have found resembles "contingent collaborations" and "productive frictions" [@tsing2011friction] where local, individual actions of knowledge creation are circumscribed by forces and structures that encompass their expression, but also give meaning to their interactions.
 
@@
 The United States, United Kingdom, Australia and Canada, are an important group because they are collectively known as the core Anglosphere countries, sharing a common heritage as former colonies of the British empire [@Richards2019].
-@vucetic2011anglosphere defines the Anglosphere as a 'distinct international, transnational, civilisational, and imperial entity within the global society.
+@vucetic2011anglosphere defines the Anglosphere as a 'distinct international, transnational, civilisational, and imperial entity within the global society'.
 The dominance of editors of CS-WHL articles located in the Anglosphere indicates an extension of this imperial project into the organization of world heritage information on Wikipedia.
@@
 
-We found that some CS-WHL talk pages referenced a 'Geopolitical, ethnic, and religious conflicts noticeboard' elsewhere on Wikipedia, as a forum for arbitration of disputes created in 2008 following a recommendation by an investigation into edit wars on articles about Northern Ireland (The Troubles), Palestine-Israel and other locations with ethnic or cultural based conflicts.
-However the noticeboard was closed in 2012 due to an absence of activity.
 Overall we find that editors of CS-WHL articles appear conflict-averse, probably because many of them come from similar cultural, socio-economic and educational backgrounds due to their Anglosphere origins.
 This means they share similar values about heritage that align with their shared goal of making an encyclopedia.
-The low levels of conflict reflect the continuity between the printed encyclopedia project as a compendium of universal knowledge, and the World Heritage List as universal heritage.
+The low levels of conflict show continuity between the printed encyclopedia project as a compendium of universal knowledge, and the World Heritage List as universal heritage.
 These projects share origins in the cultural elites of Western Europe, and their distinctive sense of what is universal that is linked to nineteenth-century nationalism and liberal modernity, vestiges of which are still evident in the modern political philosophy of the Anglosphere [@smith2006uses].

### 2021-03-31 README.Rmd
update readme

@@
 # Please put your title here to include it in the file below.
-Title <- "Title of your paper goes here"
+Title <- "World Heritage Sites on Wikipedia: Cultural Heritage Activism in a Context of Constrained Agency"
 ```
@@
 
-[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/worldheritagewikipedia/master?urlpath=rstudio)
+[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/benmarwick/worldheritagewikipedia/master?urlpath=rstudio) [![Knit-Rmd-in-Docker](https://github.com/benmarwick/worldheritagewikipedia/workflows/.github/workflows/knit-Rmd-in-docker.yaml/badge.svg)](https://github.com/benmarwick/worldheritagewikipedia/actions)
 
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>
+> Marwick, B and P. Smith, (2021). `r Title`. _Big Data and Society_ <https://doi.org/xxx/xxx>
 
@@
 
-> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Marwick, B and P. Smith, (2021). `r Title`.  Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31235/osf.io/7gvza>
 
@@
 
-> Authors, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>
+> Marwick, B and P. Smith, (`r format(Sys.Date(), "%Y")`). Compendium of R code and data for `r Title`. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/AY27G>
+
+## Contents
+
+The **analysis** directory contains:
+
+- [:file_folder: paper](/analysis/paper): R Markdown source document for manuscript and R script files.
+Includes R code to reproduce the figures and tables generated by the analysis.
+It also has a rendered version, `paper.docx`, suitable for reading (the code is replaced by figures and tables in this file)
+- [:file_folder: data](/analysis/data): Data used in the analysis.  
+- [:file_folder: figures](/analysis/figures): Plots and other illustrations using in the paper
 

### 2021-03-31 README.Rmd
update readme

@@
 
-> Marwick, B and P. Smith, (2021). `r Title`. _Big Data and Society_ <https://doi.org/xxx/xxx>
+> Marwick, B.[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531) and P.
+Smith, (2021).
+`r Title`.
+_Big Data and Society_ <https://doi.org/xxx/xxx>
 
@@
 
-> Marwick, B and P. Smith, (2021). `r Title`.  Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.31235/osf.io/7gvza>
+> Marwick, B.[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531) and P.
+Smith, (2021).
+`r Title`.
+Accessed `r format(Sys.Date(), "%d %b %Y")`.
+Online at <https://doi.org/10.31235/osf.io/7gvza>
 
@@
 
-> Marwick, B and P. Smith, (`r format(Sys.Date(), "%Y")`). Compendium of R code and data for `r Title`. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.17605/OSF.IO/AY27G>
+> Marwick, B.[![](https://orcid.org/sites/default/files/images/orcid_16x16.png)](https://orcid.org/0000-0001-7879-4531) and P.
+Smith, (`r format(Sys.Date(), "%Y")`).
+Compendium of R code and data for `r Title`.
+Accessed `r format(Sys.Date(), "%d %b %Y")`.
+Online at <https://doi.org/10.17605/OSF.IO/AY27G>
 
@@
 # install.packages("devtools")
-remotes::install_github("benmarwick/worldheritagewikipedia")
+devtools::install_github("benmarwick/worldheritagewikipedia")
 ```

### 2021-03-31 analysis/paper/paper.Rmd
working on revisions

@@
 
-# Introduction {-}
+# Introduction {.unnumbered}
 
@@
 First, we introduce Wikipedia as an example of an online peer production community where people engage with elements of the past in measurable ways.
-Second, we present a case study using data science methods to investigate the ways people create and consume Wikipedia articles on cultural sites inscribed on the UNESCO World Heritage List (hereafter CS-WHL).
+Second, we present a case study using data science methods to investigate the ways people create and consume English-language Wikipedia articles on cultural sites inscribed on the UNESCO World Heritage List (hereafter CS-WHL).
 
@@
 
-## Wikipedia as a Context of Heritage Production {-}
+## Wikipedia as a Context of Heritage Production {.unnumbered}
 
-Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, Wikipedia.
+Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, the English-language Wikipedia.
 Originating in 2001, this is a highly influential and well-known online encyclopedia, that anyone can edit, currently with 11 billion page views per month (<https://stats.wikimedia.org/#/en.wikipedia.org>).
@@
 
-## UNESCO World Heritage Cultural Sites {-}
+## Contentious UNESCO World Heritage Cultural Sites {.unnumbered}
 
@@
 
-```{r wh-unesco-map, fig.cap="Cultural Sites on the UNESCO World Heritage List.
-Countries coloured black currently have no listed cultural sites.
+```{r wh-unesco-map, fig.cap="Cultural Sites on the UNESCO World Heritage List as of September 2020.
+Countries coloured black have no listed cultural sites at the time of writing.
 Inset shows the distribution of sites per country.
@@
 In 1975 the UNESCO-drafted "Convention Concerning the Protection of the World Cultural and Natural Heritage" came into force and established the World Heritage List (WHL) to protect natural and cultural sites and landscapes around the world that have outstanding universal value.
-Currently there are `r nrow(wh_unesco)` cultural properties on the UNESCO WHL, with the first sites inscribed in `r min(wh_unesco$date_inscribed)`.
+As of September 2020 there are `r nrow(wh_unesco)` cultural properties on the UNESCO WHL, with the first sites inscribed in `r min(wh_unesco$date_inscribed)`.
 On average, most countries have 2-3 sites, with most sites located in Italy and western Europe, and several countries having no sites at all, for example, several central African countries, Taiwan, and New Zealand (Figure \@ref(fig:wh-unesco-map)).
@@
 
-# Methods {-}
+# Methods {.unnumbered}
 
@@
 Many CS-WHL are symbols of national, cultural, political, and religious identity, and the extent of political involvement in negotiations of WHL inscriptions indicates they are of great public interest among local and diasporic communities.
-Our goal in this study is to answer the question of how this interest is expressed within the socio-technical constraints of Wikipedia.
+Our goal in this study is to answer the question of how this interest is expressed within the socio-technical constraints of the English-language Wikipedia.
 We surveyed the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics).
-By comparing these basic characteristics of Wikipedia articles about CS-WHL to 10,000 random Wikipedia articles we can approach the question: can metrics of content, consumption, and production indicate engagement with the past via CS-WHL on Wikipedia?
+By comparing these basic characteristics of English-language Wikipedia articles about CS-WHL to 10,000 random English-language Wikipedia articles we can approach the question: can metrics of content, consumption, and production indicate engagement with the past via CS-WHL on Wikipedia?
 Can we detect conflict in the edit histories, bot activity, and talk pages for Wikipedia articles about CS-WHL sites, and how does this conflict relate to the types of controversies noted above?
@@
 
-# Reproducibility and Open Source Materials {-}
+# Reproducibility and Open Source Materials {.unnumbered}
 
@@
 
-# Results {-}
+# Results {.unnumbered}
 
@@
 
-## Article content {-}
+## Article content {.unnumbered}
 
@@
 
-## Article production {-}
+## Article production {.unnumbered}
 
@@
 The most active bot on CS-WHL articles is Cluebot NG (vandalism detection and reverting), compared to Cydebot (automatic implementation of category deletions) for the random articles.
-The AnomieBOT is highly active on CS-WHL articles compared to random articles, this bot performs clerical duties in an article's reference list.
+The AnomieBOT, which performs clerical duties in an article's reference list, is highly active on CS-WHL articles compared to random articles, reflecting the longer reference lists that CS-WHL articles tend to have relative to other articles.
 Most bot edits on on CS-WHL articles are in the fixer, tagger, connector, and clerk roles [@zheng2019roles].
@@
 
-## Article consumption {-}
+## Article consumption {.unnumbered}
 
@@
 
-## Spatial patterns {-}
+## Spatial patterns {.unnumbered}
 
@@
 Inset shows the distribution of numbers of CS-WHL articles per country.
-Countries coloured black currently have no CS-WHL with Wikipedia articles.
+Countries coloured black have no CS-WHL with Wikipedia articles at the time of writing.
 Map data from naturalearthdata.com", fig.width=15}
@@
 
-## Temporal patterns {-}
+## Temporal patterns {.unnumbered}
 
@@
 
-# Discussion {-}
+# Discussion {.unnumbered}
 
@@
 
-# Conclusion {-}
+# Conclusion {.unnumbered}
 
@@
 
-# Acknowledgments {-}
+# Acknowledgments {.unnumbered}
 
@@
 
-# References {-}
+# References {.unnumbered}
 

### 2021-03-31 analysis/paper/paper.Rmd
update rnaturalearth

@@
 
-```{r wh-wiki-content-and-consumption, fig.cap="Content and consumption of Wikipedia articles about CS-WHL.
-The top row of density plots show the distributions of basic content characteristics of Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey).
-The density plots on the lower left show basic characterstics of consumption.
-The lower right shows a scatterplot of consumption metrics for Wikipedia articles about CS-WHL and labels on the most intensively consumed articles", fig.width=15}
+```{r wh-wiki-content, fig.cap="Content of Wikipedia articles about CS-WHL.
+The density plots show the distributions of basic content characteristics of Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey).", fig.width=15}
 source(here::here("analysis/paper/003-Wikipedia-random-basic-content.R"))
-knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic.png"))
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic_content.png"))
 ```
@@
 ## Article consumption {.unnumbered}
+
+```{r wh-wiki-consumption, fig.cap="Consumption of Wikipedia articles about CS-WHL.
+The density plots on the left show basic characterstics of consumption.
+The right shows a scatterplot of consumption metrics for Wikipedia articles about CS-WHL, with labels on the most intensively consumed articles", fig.width=15}
+knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic_consumption.png"))
+```
 

### 2021-03-31 analysis/paper/003-Wikipedia-random-basic-content.R

@@ -1,4 +1,5 @@
 ## Basic qualities of the content of WP articles about WH sites
+library(tidyverse)
 
 # load the random pages
 if(!exists("ten_k_random_wp_pages")){
@@ -158,7 +159,7 @@ page_data_for_all_pages %>%
       filter(page_views_last_n_days_total > 1e5),
     segment.size  = 0.2,
    # force = 0,
-    size = 1.7,
+    size = 2.5,
     segment.color = "grey50",
     nudge_x = -0.1,
     nudge_y = -0.1,
@@ -197,15 +198,25 @@ page_data_for_all_pages %>%
   select(Site)
 
 library(patchwork)
-layout <- "
-AAAA
-BBCC
-BBCC
-"
-basic_content_plot + basic_consumption_plot + basic_consumption_scatter_plot +
-  plot_layout(design = layout)
 
-ggsave(here::here("analysis/figures/wh_wikipedia_articles_basic.png"),
+# content plot
+basic_content_plot
+
+ggsave(here::here("analysis/figures/wh_wikipedia_articles_basic_content.png"),
        width = 12,
-       height = 8,
+       height = 4,
+       dpi = 300)
+
+# consumption plot
+design <- "
+  11
+  22
+  22
+"
+basic_consumption_plot + basic_consumption_scatter_plot +
+  plot_layout(design = design)
+
+ggsave(here::here("analysis/figures/wh_wikipedia_articles_basic_consumption.png"),
+       width = 12,
+       height = 12,
        dpi = 300)

### 2021-03-31 analysis/paper/paper.Rmd
update rnaturalearth

@@
 Of the `r nrow(wh_unesco)` cultural sites on the World Heritage List at the time of writing, we found Wikipedia articles for `r nrow(some_page_variables)`.
-As a group, the basic details of content for Wikipedia articles for CS-WHL differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+As a group, the basic details of content for Wikipedia articles for CS-WHL differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content)).
 The scholarly nature of the articles, measured by the number of sources cited in the reference list per thousand words in the article body, have similarly distributions for CS-WHL articles and random articles.
@@
 ```{r wh-wiki-consumption, fig.cap="Consumption of Wikipedia articles about CS-WHL.
-The density plots on the left show basic characterstics of consumption.
-The right shows a scatterplot of consumption metrics for Wikipedia articles about CS-WHL, with labels on the most intensively consumed articles", fig.width=15}
+The density plots on the top show basic characterstics of consumption for Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey).
+The scatterplot at the bottom shows consumption metrics for Wikipedia articles about CS-WHL, with labels on the most intensively consumed articles", fig.width=15}
 knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic_consumption.png"))
@@
 
-The basic metrics of consumption of CS-WHL articles show substantial differences from our sample of random articles (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+The basic metrics of consumption of CS-WHL articles show substantial differences from our sample of random articles (Figure \@ref(fig:wh-wiki-consumption)).
 We measure consumption by counting the total number of views of the article over the 100 days prior to our data collection date, and the the number of Wikilinks from other articles into the target article.
@@
 CS-WHL articles are typically viewed far more frequently than other Wikipedia articles, reflecting high consumption by internet users generally.
-They are also much more often linked to by other Wikipedia articles than our random sample of other articles, indicating consumption by other Wikipedia articles and Wikipedia users in their editing work (Figure \@ref(fig:wh-wiki-content-and-consumption)).
+They are also much more often linked to by other Wikipedia articles than our random sample of other articles, indicating consumption by other Wikipedia articles and Wikipedia users in their editing work (Figure \@ref(fig:wh-wiki-consumption)).
 This indicates that consumption of CS-WHL articles is generally high, relative to other articles, and confirms our assertion of Wikipedia as an important source of heritage information.
@@
 
-We can see an answer to this question in the scatterplot on the lower right of Figure \@ref(fig:wh-wiki-content-and-consumption), which shows the values of inward Wikilinks, article views, and article word count for all CS-WHL articles.
+We can see an answer to this question in the scatterplot on the lower part of Figure \@ref(fig:wh-wiki-consumption), which shows the values of inward Wikilinks, article views, and article word count for all CS-WHL articles.
 The labeled points in the upper right quadrant are the articles that receive most of the attention.

### 2021-03-31 analysis/paper/003-Wikipedia-random-basic-content.R

@@ -88,6 +88,14 @@ ggplot(page_data_for_all_pages_basic_qualities_long,
   # ggtitle("Basic qualities about Wikipedia article content") +
   NULL
 
+# content plot
+basic_content_plot
+
+ggsave(here::here("analysis/figures/wh_wikipedia_articles_basic_content.png"),
+       width = 12,
+       height = 4,
+       dpi = 300)
+
 ## Basic qualities of the consumption of WP articles about WH sites
 
 library(ggrepel)
@@ -199,17 +207,10 @@ page_data_for_all_pages %>%
 
 library(patchwork)
 
-# content plot
-basic_content_plot
-
-ggsave(here::here("analysis/figures/wh_wikipedia_articles_basic_content.png"),
-       width = 12,
-       height = 4,
-       dpi = 300)
-
 # consumption plot
 design <- "
   11
+  22
   22
   22
 "
@@ -217,6 +218,6 @@ basic_consumption_plot + basic_consumption_scatter_plot +
   plot_layout(design = design)
 
 ggsave(here::here("analysis/figures/wh_wikipedia_articles_basic_consumption.png"),
-       width = 12,
-       height = 12,
+       width = 10,
+       height = 10,
        dpi = 300)

### 2021-03-31 analysis/paper/paper.Rmd
rgeos
rrtools

@@
 The highly detailed edit histories that Wikipedia keeps for every article allow us to further investigate spatial and temporal questions relating to engagement with the past and conflicts surrounding CS-WHL sites.
-For example, when an article is edited by a user who does not have a Wikipedia user account (or is not logged into their account), their edit is identified by that person's IP address.
-This IP address can be used to geo-locate the user to the country they were in when the made the edit.
-We geo-located all edits with IP addresses for all Wikipedia articles CS-WHL sites to determine the country of origin of those edits using the rgeolocate package for R [@rgeolocate].
+For example, when an article is anonymously edited, for example, by a user who does not have a Wikipedia user account (or is not logged into their account), their edit is identified by that person's IP address.
+Edits made by people who are logged in to their Wikipedia user account do not include the user's IP address, only their Wikipedia user account name.
+An IP address can be used to geo-locate the user to the country they were in when the made the edit.
+This means that edits from registered Wikipedia users cannot be used for tracing the geographic origin of an edit, but anonymous edits, because they are identified by an IP address, can be used for tracing the geographic origin of an edit.
+We geo-located all edits with IP addresses for all English-language Wikipedia articles CS-WHL sites to determine the country of origin of those edits using the rgeolocate package for R [@rgeolocate].
 This helps us to answer the question: are the editors of articles about CS-WHL located near the sites they edit, indicating local community interest in the online representation of their heritage?
@@
 Inset plot shows variable loadings to show variables most influential on cluster membership", fig.width=15}
-rrtools:::quietly(source(here::here("analysis/paper/002-Wikipedia-umap-hdbscan.R")))
+# rrtools:::quietly(source(here::here("analysis/paper/002-Wikipedia-umap-hdbscan.R")))
 # knitr::include_graphics(here::here("analysis/figures/wh_country_umap_hdbscan.png"))
@@
 This pattern is consistent with @graham2014uneven's observations that places in the Global North tend to be over-represented on Wikipedia.
+We also see that some Asian countries outside of the Global North are highly represented on Wikipedia (e.g.
+India and China).
 The lower panel of figure \@ref(fig:wh-wiki-map) further demonstrates this with South American countries having low proportions of their CS-WHL sites represented on Wikipedia.
@@
 
-The distribution of editor locations shown in figure \@ref(fig:wh-wiki-circle) was determined by geo-locating the IP addresses attached to each anonymous edit on all CS-WHL articles.
+The distribution of editor locations shown in figure \@ref(fig:wh-wiki-circle) was determined by geo-locating the IP addresses attached to each anonymous edit on all CS-WHL articles (only anonymous edits contain IP addresses, edits made by registered Wikipedia users contain no information suitable for geolocation).
 This figure shows the flow of edits, with the arrows starting at the country where the editor was located when they made their edit, and ending at the country where the CS-WHL site that they are editing is located.
@@
 
-The most striking spatial pattern in our results is the high proportion of anonymous edits of articles about CS-WHL sites, in any part of the world, that come from the United States.
+The most striking spatial pattern in our results is the high proportion of anonymous edits (as the only type of edit that can be geolocated) that come from the United States on articles about CS-WHL sites, regardless of where in the world the CS-WHL site is located.
 These anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing.

### 2021-03-31 analysis/paper/paper.Rmd
add rrtools to dockerfile

@@
 Inset plot shows variable loadings to show variables most influential on cluster membership", fig.width=15}
-# rrtools:::quietly(source(here::here("analysis/paper/002-Wikipedia-umap-hdbscan.R")))
+rrtools:::quietly(source(here::here("analysis/paper/002-Wikipedia-umap-hdbscan.R")))
 # knitr::include_graphics(here::here("analysis/figures/wh_country_umap_hdbscan.png"))
@@
 We might similarly expect that the French language Wikipedia (2.3 m articles, 173 m edits, 3.9 m users) would have more edits originating in France or francophone on articles about CS-WHL sites in any part of the world.
-It is beyond the scope of this paper to analyze spatial patterns of edits in Wikipedias written in languages other than English; we focus on the English language Wikipedia because it is the largest by a considerable margin [6.2 m articles, 998 m edits, 40 m users, @wiki:listoflangs].
+We have limited the scope of our initial foray into this topic to the English language Wikipedia because it is the largest by a considerable margin [6.2 m articles, 998 m edits, 40 m users, @wiki:listoflangs].
+The question of whether or not our findings generalise to non-English-language Wikipedias should be priority for future research.
 
@@
 @vucetic2011anglosphere defines the Anglosphere as a 'distinct international, transnational, civilisational, and imperial entity within the global society'.
-The dominance of editors of CS-WHL articles located in the Anglosphere indicates an extension of this imperial project into the organization of world heritage information on Wikipedia.
+The dominance of editors of CS-WHL articles located in the Anglosphere indicates an extension of this imperial project into the organization of world heritage information on the English-language Wikipedia.
 The prominence of Anglosphere editors on CS-WHL articles articles represents a digital colonisation of world heritage information on Wikipedia, where heritage is interpreted and communicated by people who are not part of the descendant communities traditionally associated with the site.
-Although we could only geo-locate about 20% of edits, our spatial patterns resemble those found by @Mandiberg_2020 who examined 884 m edits to the English Wikipedia and found that at the country level, the 'five largest contributors were part of what once was the British Empire, and account for nearly 75 percent of all editors'.
+Although we could only geo-locate about 20% of edits, our spatial patterns resemble those found by @Mandiberg_2020 who examined 884 m edits to the English-language Wikipedia and found that at the country level, the 'five largest contributors were part of what once was the British Empire, and account for nearly 75 percent of all editors'.
 
@@
 the poor representation of CS-WHL sites located in the Global South).
-Second is that traditional communities associated with CS-WHL have little control over how their own heritage is represented on Wikipedia.
+Second is that traditional communities associated with CS-WHL have little control over how their own heritage is represented on the English-language Wikipedia.
 We see this spatial pattern on Wikipedia as part of a trend of globalization of heritage, where places that had traditionally contributed to local or regional identities are turned into sanitized playgrounds for rich tourists [@bernbeck2004political].

### 2021-03-31 analysis/paper/paper.Rmd
tamp

@@
 We have limited the scope of our initial foray into this topic to the English language Wikipedia because it is the largest by a considerable margin [6.2 m articles, 998 m edits, 40 m users, @wiki:listoflangs].
-The question of whether or not our findings generalise to non-English-language Wikipedias should be priority for future research.
+The narrow linguistic focus of our study is an important limitation, and question of whether or not our findings generalise to non-English-language Wikipedias should be priority for future research.
 
@@
 are minor.
-Typical conflicts about Wikipedia CS-WHL articles are hyper-local, and process-centered.
+Typical conflicts about English-language Wikipedia CS-WHL articles are hyper-local, and process-centered.
 There are also cases of editorial conflicts about substantive issues of specific CS-WHL, such as Mapungubwe and Preah Vihear, that include editors with a personal investment in the debate, if not the article.

### 2021-03-31 analysis/paper/002-Wikipedia-umap-hdbscan.R
comment out umap etc

@@ -28,138 +28,138 @@ some_page_variables <-
   mutate(page_wikilinks_out_per_word = page_wikilinks_out / page_wordcount,
          page_cited_items_on_per_word = page_cited_items_on / page_wordcount)
 
-
-
-# umap
-library(uwot)
-library("tmap")
-data("World")
-
-pages_umap_input <-
-  some_page_variables  %>%
-  mutate(page_wordcount_norm = normalize(page_wordcount),
-         page_wikilinks_in_norm= normalize(page_wikilinks_in),
-         page_wikilinks_out_per_word_norm = normalize(page_wikilinks_out_per_word),
-         page_cited_items_on_per_word_norm = normalize(page_cited_items_on_per_word)) %>%
-  select(-page_wordcount,
-         -page_cited_items_on,
-         -page_wikilinks_out,
-         -page_wikilinks_in,
-         -page_wikilinks_out_per_word,
-         -page_cited_items_on_per_word) %>%
-  bind_cols(., page_data_for_all_pages[ , 'country'] ) %>%
-  filter_all(all_vars(!is.na(.))) %>%
-  left_join(World %>%
-              select(name, continent),
-            by = c('country' = 'name'))
-
-# compute umap
-
-pages_umap_input_selected <-
-  pages_umap_input %>%
-  select(-country,
-         -continent,
-         -geometry
-  )
-
-pages_umap_output <-
-  pages_umap_input_selected %>%
-  umap(.,
-       n_neighbors = 60,
-       min_dist = 0.7,
-       nn_method = "annoy",
-       init = "spca") %>%
-  as_tibble()
-
-# compute hdbscan clusters
-library(dbscan)
-hdbscan_out <- hdbscan(pages_umap_output,
-                       minPts = 5)
-
-clus_tbl <-
-tibble(clus = names(table(hdbscan_out$cluster)),
-       n = table(hdbscan_out$cluster))
-
-n_clusters <- nrow(clus_tbl) -1
-
-n_no_cluster <- clus_tbl %>% filter(clus == 0) %>% pull(n) %>% unname
-prop_no_cluster <- (n_no_cluster / sum(clus_tbl$n)) %>% unname
-
-main_plot <-
-  ggplot(pages_umap_output,
-         aes(V1, V2)) +
-  geom_point(
-    aes(colour = factor(hdbscan_out$cluster),
-      #  size =  pages_umap_input_selected$page_wordcount_norm  ,
-        shape = pages_umap_input$continent,
[…]

### 2021-03-31 analysis/paper/paper.Rmd
many small edits and change csl

@@
 bibliography: references.bib
-csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
+csl: "../templates/harvard-cite-them-right.csl" # Insert path for the bib-style
 abstract: |
@@
 in the World Heritage inscription process are present, but rare on Wikipedia’s World Heritage pages.
-Instead hyper-local, and process issues dominate controversies on Wikipedia.
+Instead, hyper-local, and process issues dominate controversies on Wikipedia.
 We describe how this kind of research, drawing on big data and data science methods, contributes to digital heritage studies, and also reveals its limitations.
@@
 
-While social media is a vast and diverse online space that we are only just beginning to explore how people engage with the past, there are other contexts of online interactions where heritage is practiced in distinctive, if poorly understood, ways.
-We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with online peer production communities, where users participate in the collaborative, asynchronous creation, sharing, promoting, and classification of content in highly structured and goal-directed ways [@wilkinson2008strong].
-Online peer production communities are comparable to more traditions kinds of voluntary associations where groups set and execute goals, with explicitly democratic organizational ideals.
+While social media, such as Facebook and Twitter, is a vast and diverse online space that we are only just beginning to explore how people use to engage with the past, there are other contexts of online interactions where heritage is practiced in distinctive, if poorly understood, ways.
+We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with online peer production communities, where users participate in the collaborative, asynchronous, creating, sharing, promoting, and classifying of content in highly structured and goal-directed ways [@wilkinson2008strong].
+Online peer production communities are comparable to more traditional kinds of voluntary associations where groups set and execute goals, with explicitly democratic organizational ideals.
 While the ideals of many online peer production communities emphasize non-hierarchical and non-bureaucratic organization, analysis of large amounts of user activity indicates that most of these communities are actually undemocratic and noninclusive, functioning as entrenched oligarchies [@shaw2014laboratories].
 This emphasis on governance and management of collective action is a key detail that distinguishes social media from online peer production.
-It follows that user interactions in the process of generating content in online peer production communities includes technological and social mechanisms that enact the community's governance policies, for example, limiting a user's activity according to their status in the community's hierarchy, or managing conflict with highly structured procedures.
+It follows that user interactions in the process of generating content in online peer production communities includes technological and social mechanisms that enact the community's written or unwritten governance policies.
+These may include, for example, limiting a user's activity according to their status in the community's hierarchy, or managing conflict with highly structured procedures.
 Here we show how the distinctive organizational and technical qualities of online peer production communities make them a unique context of heritage production to study digital traces of human activity resulting from engagement with the past.
@@
 
-Here we present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, the English-language Wikipedia.
-Originating in 2001, this is a highly influential and well-known online encyclopedia, that anyone can edit, currently with 11 billion page views per month (<https://stats.wikimedia.org/#/en.wikipedia.org>).
+We present a study of how people engage with elements of the past in one of the largest and long-lived online peer production communities, the English-language Wikipedia.
+Originating in 2001, this is a highly influential and well-known online encyclopedia, that anyone can edit, with 9 billion page views per month as of September 2020 (<https://stats.wikimedia.org/#/en.wikipedia.org>).
 Although anyone can edit, most internet users do not.
@@
 
-An additional consideration for understanding participation in online peer production communities are the technical schemas of the software that Wikipedia runs on, MediaWiki.
+An additional consideration for understanding participation in online peer production communities are the technical schemas of MediaWiki, the software that Wikipedia runs on.
 This is a complex toolkit that enables participation in Wikipedia in highly structured ways.
@@
 On the other hand, they constrain and limit the agency of the user, canalizing their behaviour into a small number of possible actions and acceptable modes of discourse and engagement with other users [@iba2010analyzing].
-While Wikipedia has elements that are ubiquitous on the Internet, such as links on articles that take the user to other articles or other pages on the Internet, it also has several less common elements that contribute to its unique technicity, resulting in specific types of relationships between human users and the technical elements of the Wikipedia project [@niederer2010wisdom; @weltevrede2016platform].
-For example, every edit to an article is tracked in a publicly accessible version control system attached to that article.
+While Wikipedia has elements that are ubiquitous on the Internet, such as links that take the user to other articles or pages on the Internet, it also has several less common elements that contribute to its unique technicity, resulting in specific types of relationships between human users and the technical elements of the Wikipedia project [@niederer2010wisdom; @weltevrede2016platform].
+For example, every edit to an article is tracked in a publicly accessible version control system associated with that article.
 This exposes the article creation process in highly granular detail; for any given article, we can see how many editors contributed, the size of their edits and their distribution over time, among other things [@priedhorsky2007creating].
@@
 We chose the CS-WHL as a bounded set of cultural heritage elements with several characteristics that make it of general interest.
-It has a global geographic distribution, broad public interest at local and international scales, in both online and face-to-face communities; a wide temporal distribution in both the age of the cultural sites, the ages of inscription on the WHL, and the ages of their appearance on Wikipedia; and finally many CS-WHL have a high intensity of cultural and political discussions that surround events affecting these sites, such as their inscription on the WHL.
+It has a global geographic distribution; broad public interest at local and international scales, in both online and face-to-face communities; a wide temporal distribution in both the age of the cultural sites, the ages of inscription on the WHL, and the ages of their appearance on Wikipedia; and finally, many CS-WHL have a high intensity of cultural and political discussions that surround events affecting these sites, such as their inscription on the WHL.
 These qualities make it an ideal data set as an entry point for case studies of digital heritage in online peer production communities, where activities are typically goal-driven (e.g.
@@
 In Mali during 2012, fighting between government and rebel groups lead to the damage and destruction of tombs at the CS-WHL sites of Gao and Timbuktu [@brioschi2017discourses].
-The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are currently among the 36 cultural sites on the List of World Heritage in Danger (<https://whc.unesco.org/en/danger/>).
+The World Heritage Committee found itself powerless to intervene because of political gridlock [@meskell2015gridlock], and these Mali sites are among the 53 cultural sites on the List of World Heritage in Danger, as of March 2021 (https://whc.unesco.org/en/danger/).
 In 2015, ISIS militants destroyed the Temple of Bel in Palmyra, Syria (a CS-WHL site of monumental ruins, once great city at the crossroads between east and west in the ancient world) [@gornik2015can].
@@
 
-Our brief review of controversial cultural sites on the WHL shows the intensity and diversity of conflicts and tensions that surround these sites.
+Our brief review of contentious cultural sites on the WHL shows the intensity and diversity of conflicts and tensions that surround these sites.
 Many CS-WHL are symbols of national, cultural, political, and religious identity, and the extent of political involvement in negotiations of WHL inscriptions indicates they are of great public interest among local and diasporic communities.
@@
 We surveyed the basic characteristics of content (article length, number of wikilinks out to other pages, number of citations to non-Wikipedia items), consumption (page view counts, wikilinks in from other Wikipedia pages), and production (edit counts, edit densities, edit sizes, number of unique editors per article, talk page length, talk page topics).
-By comparing these basic characteristics of English-language Wikipedia articles about CS-WHL to 10,000 random English-language Wikipedia articles we can approach the question: can metrics of content, consumption, and production indicate engagement with the past via CS-WHL on Wikipedia?
+By comparing these basic characteristics of English-language Wikipedia articles about CS-WHL to 10,000 random English-language Wikipedia articles, we can approach the question: can metrics of content, consumption, and production indicate engagement with the past via CS-WHL on Wikipedia?
 Can we detect conflict in the edit histories, bot activity, and talk pages for Wikipedia articles about CS-WHL sites, and how does this conflict relate to the types of controversies noted above?
@@
 For example, when an article is anonymously edited, for example, by a user who does not have a Wikipedia user account (or is not logged into their account), their edit is identified by that person's IP address.
+An IP address can be used to geolocate the user to the country they were in when the made the edit.
 Edits made by people who are logged in to their Wikipedia user account do not include the user's IP address, only their Wikipedia user account name.
-An IP address can be used to geo-locate the user to the country they were in when the made the edit.
 This means that edits from registered Wikipedia users cannot be used for tracing the geographic origin of an edit, but anonymous edits, because they are identified by an IP address, can be used for tracing the geographic origin of an edit.
-We geo-located all edits with IP addresses for all English-language Wikipedia articles CS-WHL sites to determine the country of origin of those edits using the rgeolocate package for R [@rgeolocate].
+We used the rgeolocate package for R [@rgeolocate] to geolocate all edits with IP addresses for all English-language Wikipedia articles CS-WHL sites to determine the country of origin of those edits.
 This helps us to answer the question: are the editors of articles about CS-WHL located near the sites they edit, indicating local community interest in the online representation of their heritage?
 The time and date stamps attached to every edit on every article allows us to investigate temporal patterns of activity on CS-WHL Wikipedia articles.
-Analyses of these data help us to answer the question: is Wikipedia editing activity correlated with events outside of Wikipedia relating to the CS-WHL sites, such as conflict events, or their inscription on the WHL?
+Analyses of these temporal data help us to answer the question: is Wikipedia editing activity correlated with events outside of Wikipedia relating to the CS-WHL sites, such as conflict events, or their inscription on the WHL?
 
@@
 As a group, the basic details of content for Wikipedia articles for CS-WHL differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content)).
-The scholarly nature of the articles, measured by the number of sources cited in the reference list per thousand words in the article body, have similarly distributions for CS-WHL articles and random articles.
+The scholarly nature of the articles, measured by the number of sources cited in the reference list per thousand words in the article body, have similar distributions for CS-WHL articles and random articles.
 The number of Wikilinks out from the target article to other Wikipedia articles are also similarly distributed for CS-WHL articles and random articles.
@@
 The most active bot on CS-WHL articles is Cluebot NG (vandalism detection and reverting), compared to Cydebot (automatic implementation of category deletions) for the random articles.
-The AnomieBOT, which performs clerical duties in an article's reference list, is highly active on CS-WHL articles compared to random articles, reflecting the longer reference lists that CS-WHL articles tend to have relative to other articles.
+The AnomieBOT, which performs clerical duties in an article's reference list, is highly active on CS-WHL articles compared to random articles.
 Most bot edits on on CS-WHL articles are in the fixer, tagger, connector, and clerk roles [@zheng2019roles].
@@
 In particular, editors were concerned about the depiction of Indigenous people, especially the degree to which early European colonists were aware of Indigenous communities, and the correct cultural affiliation of the Indigenous groups that originally occupied the site.
-In this remarkable case we see the Wikipedia editors engaging conflicts that go beyond the typical technical details of article production.
+In this remarkable case we see the Wikipedia editors engaging in conflicts that go beyond the typical technical details of article production.
 What is especially notable about these discussions on the talk page is how closely they echo the debates of land ownership that complicated the WHC process [@meskell2011paris].
-The editors involved in this debate did not make any edits to the article itself which raises questions about their motivations for engaging in debate on the talk page, since they do not seem personally invested in the content of the article.
+The specific editors involved in this debate did not make any edits to the article itself, which raises questions about their motivations for engaging in debate on the talk page, since they do not seem personally invested in the content of the article.
 Without directly interviewing these editors, we cannot be sure of their motives for participating in the talk page.
@@
 Although not notable for the length of its talk page, the discussions among editors of the article about Preah Vihear Temple include a strongly worded disagreement among seven editors about the legitimacy of the ownership claims by Thailand and Cambodia of the territory that includes the temple.
-As for Mapungubwe, the debate among Wikipedia editors mirrors closely the political tensions surrounding the nomination of Preah Vihear.
+As for Mapungubwe, the debate among Wikipedia editors here mirrors closely the political tensions surrounding the nomination of Preah Vihear.
 The talk page also has a lengthy argument from to 2008, involving several editors, about whether or not the Thai name of the site should be included in the text of the article.
@@
 One editor indicates their likely Thai ethnicity here through their use of Thai language phrases (using the Thai alphabet).
-This debate also recapitulates broader substantive issues of whether Thailand or Cambodia country has the stronger claim for ownership of the temple.
-Amid accusations of nationalism among the editors, one of them asks "Can we put aside politics and be more collaborative on the encyclopedia project?" and appeals to Wikipedia policies 'Third opinion' and 'Dispute resolution' to diffuse the tensions and refocus attention on the common goal.
+This debate also recapitulates broader substantive issues of whether Thailand or Cambodia has the stronger claim for ownership of the temple.
+Amid accusations of nationalism among the editors, one of them asks "Can we put aside politics and be more collaborative on the encyclopedia project?" and appeals to Wikipedia's policies of 'Third opinion' and 'Dispute resolution' to diffuse the tensions and refocus attention on the common goal.
 Unlike the Mapungubwe talk page, many of the editors involved in the Preah Vihear talk page debates have made contributions directly to the Preah Vihear article, and are deeply invested in how the article represents the site.
@@
 This figure shows the flow of edits, with the arrows starting at the country where the editor was located when they made their edit, and ending at the country where the CS-WHL site that they are editing is located.
-The inset plot on figure \@ref(fig:wh-wiki-circle) shows that this visualisation only accounts for a relatively small proportion of all edits to CS-WHL articles.
+The inset plot on figure \@ref(fig:wh-wiki-circle) shows that this visualisation accounts for a relatively small proportion of all edits to CS-WHL articles.
 Around 20% of edits of most CS-WHL articles are anonymous, a higher proportion than our random sample.
@@
 
-Time series analysis of edits on articles about CS-WHL sites can help us identify relationships between activity on Wikipedia articles and external events related to the sites.
+Time series analysis of edits on articles about CS-WHL sites help us identify relationships between activity on Wikipedia articles and external events related to the sites.
 Figure \@ref(fig:wh-wiki-time1) shows that most articles about CS-WHL sites are much older than articles in our random sample, with most CS-WHL articles created 5-10 years after Wikipedia first appeared in 2001.
-This rapid addition of articles early in the life of Wikipedia supports the observation from the in-bound Wikilinks data that articles about CS-WHL sites are more central to the encyclopedia and considered worthy of inclusion than many other types of articles.
+This rapid addition of articles early in the life of Wikipedia supports our earlier observation that articles about CS-WHL sites are more central to the encyclopedia and considered more worthy of inclusion than many other types of articles.
 The distribution of years between the date of a site's inscription on the WHL and the date of the creation of that site's Wikipedia article has a distinctive trimodal shape.
@@
 Timbuktu shows spikes of editing activity right after the rebel attacks in mid June 2012, with descriptions of the attacks added to the text of the article at that time.
-However the tallest peak in editing activity on the Timbuktu occurs slightly earlier, in April 2012, those edits concentrated on expanding the sections on local prehistory.
+However the tallest peak in editing activity on the Timbuktu occurs slightly earlier, in April 2012, with numerous edits concentrated on expanding the sections on local prehistory.
 A detailed analysis of all the article-specific time series is beyond the scope of this paper, but we can see several patterns indicating important relationships between editorial activities and WHL listing.
@@
 
-Our results establish Wikipedia as an online community actively engaging with cultural heritage [@pentzold2017digging], especially cultural sites on the UNESCO World Heritage List.
+Our results establish the English-language Wikipedia as an online community actively engaging with cultural heritage [@pentzold2017digging], especially cultural sites on the UNESCO World Heritage List.
 We have defined Wikipedia as an online peer production community with technical and cultural qualities that make it distinct from social media services such as Twitter and Facebook.
 On Wikipedia, the editing mechanics, bots, reverts, and talk pages work together to enable and limit discourse and debate about CS-WHL.
-The goal-driven culture of Wikipedia editors, and the policies that guide the production of articles strongly constrain heritage discourse, such that the exchange of different perspectives are rarely found in articles themselves.
+The goal-driven culture of Wikipedia editors, and the policies that guide the production of articles strongly constrain heritage discourse, such that exchanges of different perspectives are rarely found in articles themselves.
 However, we have identified conflict and tension on the article talk pages, sometimes in technical and highly specific discussions, and sometimes in overtly hostile exchanges between editors.
@@
 98].
-For example, CS-WHL in countries in the Global South are under-represented on Wikipedia, a geographical tension that is also evident in the World Heritage List [@brumann2014shifting].
+For example, CS-WHL in countries in the Global South are generally under-represented on Wikipedia, a geographical tension that is also evident in the World Heritage List [@brumann2014shifting].
 Articles about CS-WHL in the Global South are also shorter and have received less attention in the form of page views and inward Wikilinks.
@@
 These anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing.
-Finding the United States at the first ranked location for anonymous edits is not surprising as it has the world's largest number of English speakers.
-We might similarly expect that the French language Wikipedia (2.3 m articles, 173 m edits, 3.9 m users) would have more edits originating in France or francophone on articles about CS-WHL sites in any part of the world.
+Finding the United States at the first ranked location for anonymous edits is perhaps not surprising as it has the world's largest number of English speakers.
+We might similarly expect that the French language Wikipedia (2.3 m articles, 173 m edits, 3.9 m users) would have more edits originating in France or francophone countries on articles about CS-WHL sites in any part of the world.
 We have limited the scope of our initial foray into this topic to the English language Wikipedia because it is the largest by a considerable margin [6.2 m articles, 998 m edits, 40 m users, @wiki:listoflangs].
-The narrow linguistic focus of our study is an important limitation, and question of whether or not our findings generalise to non-English-language Wikipedias should be priority for future research.
+The narrow linguistic focus of our study is an important limitation, and question of whether or not our findings generalise to non-English-language Wikipedias should be a priority for future research.
 
-Although the dominance of the United States in the spatial patterns is unsurprising, our data show some patterns that that language dominance cannot not fully explain.
+Although the dominance of the United States in the spatial patterns may be unsurprising, our data show some patterns that cannot be fully explained by language dominance alone.
 After the United States (297 m speakers), the top five countries for numbers of English speakers are India (238 m), Nigeria (104 m), United Kingdom (60 m), Philippines (50 m), and Germany (45 m) [@Ethnologue].
@@
 This is an important observation because it is these editors that control the production of knowledge about CS-WHL articles, and the ability to control information about heritage has several implications.
-First is that the choices of these editors define community identity, that is, the community of Wikipedia editors, and also the broader community of Internet users that read Wikipedia, by indicating which sites are important and visible, and which are not by contributing to a digital 'authorized heritage discourse' [@smith2012constrained] that prioritizes their own self-interests (cf.
+First is that the choices of these editors define community identity, that is, the community of Wikipedia editors, and also the broader community of Internet users that read Wikipedia, by indicating which sites are important and visible, and which are not, by contributing to a digital 'authorized heritage discourse' [@smith2012constrained] that prioritizes their own self-interests (cf.
 the poor representation of CS-WHL sites located in the Global South).
-Second is that traditional communities associated with CS-WHL have little control over how their own heritage is represented on the English-language Wikipedia.
+Second, traditional communities associated with CS-WHL have little control over how their own heritage is represented on the English-language Wikipedia.
 We see this spatial pattern on Wikipedia as part of a trend of globalization of heritage, where places that had traditionally contributed to local or regional identities are turned into sanitized playgrounds for rich tourists [@bernbeck2004political].
@@
 There are also cases of editorial conflicts about substantive issues of specific CS-WHL, such as Mapungubwe and Preah Vihear, that include editors with a personal investment in the debate, if not the article.
-Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the Anglosphere, and poor coverage of CS-WHL in the Global South.
+Spatial patterns in the edits to Wikipedia articles about CS-WHL show a kind of digital colonialism of world heritage information, with most edits emanating from the Anglosphere, and generally poor coverage of CS-WHL in the Global South.
 Because of these technical and cultural characteristics of Wikipedia, its articles present a discourse that actively obscures the power relations that give rise to them, and makes opaque debates about how heritage is involved in the production of identity and power [cf.
@@
 These structures serve to normalize and historize inequalities, and manage threats to models of control and expertise about heritage [@harrison2015beyond].
-As a context of heritage production, a resource of information on heritage, and itself an artefact of contemporary digital heritage, Wikipedia is remarkable and holds substantial research potential.
+As a context of heritage production, a resource of information on heritage, and itself an artefact and archive of contemporary digital heritage, Wikipedia is remarkable and holds substantial research potential.
 While the Neutral Point of View is a central policy for Wikipedia articles, representations and definitions of cultural heritage are never neutral in any discourse, because they always come from some perspective [@lahdesmaki2019conflicts].

### 2021-04-16 analysis/paper/paper.Rmd
edits after third round of reviews

@@
 These are important to understand because they shape peoples' identities and influence how they think and behave towards other people.
-Digital heritage are these engagements that are enabled by the Internet [@bonacchi2019digital], leaving traces that can be identified and quantified using data science methods.
+Digital heritage are engagement with elements of the past that are enabled by the Internet [@bonacchi2019digital], leaving traces that can be identified and quantified using data science methods.
 Digital heritage studies represent a major turn from traditional heritage studies, characterized by post-modernism [@kristiansen2014towards], critical theory, and qualitative methods, towards novel ontologies, data-intensive ethnographies, and a new role for heritage scholars as data scientists.
@@
 
-While social media, such as Facebook and Twitter, is a vast and diverse online space that we are only just beginning to explore how people use to engage with the past, there are other contexts of online interactions where heritage is practiced in distinctive, if poorly understood, ways.
+While social media, such as Facebook and Twitter, is a vast and diverse online space in which we are only just beginning to explore how people use to engage with the past, there are other contexts of online interactions where heritage is practiced in distinctive, if poorly understood, ways.
 We can contrast social media, with its fundamental elements of identity, conversations, sharing, presence, relationships, reputation, and groups [@kietzmann2011social], with online peer production communities, where users participate in the collaborative, asynchronous, creating, sharing, promoting, and classifying of content in highly structured and goal-directed ways [@wilkinson2008strong].
@@
 Several CS-WHL sites are notable for the conflicts and tensions that have surrounded their inscription [@meskell2018future].
-The 1992 inscription of Angkor (an ancient city and empire in Cambodia, prominent during the 9th to the 15th centuries AD) was supported by exiled supporters of the genocidal Khmer Rouge regime, hoping to strengthen territorial claims [@locard2015myth].
+The 1992 inscription of Angkor (an ancient city and empire in Cambodia, prominent during the 9th to the 15th centuries AD) was encouraged by exiled supporters of the genocidal Khmer Rouge regime, hoping to strengthen territorial claims [@locard2015myth].
 They appropriated Western discourse on national cultural heritage to argue for the safeguarding of Angkor as part of their quest for national independence and international recognition.
@@
 The highly detailed edit histories that Wikipedia keeps for every article allow us to further investigate spatial and temporal questions relating to engagement with the past and conflicts surrounding CS-WHL sites.
-For example, when an article is anonymously edited, for example, by a user who does not have a Wikipedia user account (or is not logged into their account), their edit is identified by that person's IP address.
+When an article is anonymously edited, for example, by a user who does not have a Wikipedia user account (or is not logged into their account), their edit is identified by that person's IP address.
 An IP address can be used to geolocate the user to the country they were in when the made the edit.
 Edits made by people who are logged in to their Wikipedia user account do not include the user's IP address, only their Wikipedia user account name.
-This means that edits from registered Wikipedia users cannot be used for tracing the geographic origin of an edit, but anonymous edits, because they are identified by an IP address, can be used for tracing the geographic origin of an edit.
+This means that edits from registered Wikipedia users cannot be used for tracing the geographic origin of an edit, but anonymous edits can.
 We used the rgeolocate package for R [@rgeolocate] to geolocate all edits with IP addresses for all English-language Wikipedia articles CS-WHL sites to determine the country of origin of those edits.
@@
 
-We collected data during May 2019, and due to the highly dynamic nature of Wikipedia, it is likely that articles in our study have subtly changed since our data collection.
-It is possible that new articles have since appeared about sites that were not represented on Wikipedia since we collected the data.
+We collected data during May 2019, and due to the highly dynamic nature of Wikipedia, it is likely that articles in our study have subtly changed since our data collection, or that new ones have appeared.
 Our original code may no longer work on the most current version of Wikipedia without modification as the tables on Wikipedia articles continue to be modified by editors.
@@
 Of the `r nrow(wh_unesco)` cultural sites on the World Heritage List at the time of writing, we found Wikipedia articles for `r nrow(some_page_variables)`.
-As a group, the basic details of content for Wikipedia articles for CS-WHL differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content)).
+As a group, the basic details of content for CS-WHL Wikipedia articles differ little from a sample of 10,000 random Wikipedia articles (Figure \@ref(fig:wh-wiki-content)).
 The scholarly nature of the articles, measured by the number of sources cited in the reference list per thousand words in the article body, have similar distributions for CS-WHL articles and random articles.
@@
 The AnomieBOT, which performs clerical duties in an article's reference list, is highly active on CS-WHL articles compared to random articles.
-Most bot edits on on CS-WHL articles are in the fixer, tagger, connector, and clerk roles [@zheng2019roles].
+Most bot edits on CS-WHL articles are in the fixer, tagger, connector, and clerk roles [@zheng2019roles].
 None of these articles with intensive bot activity are CS-WHL sites of conflict or on the List of World Heritage in Danger, indicating that these sites receive little or no vandalism.
@@
 As for Mapungubwe, the debate among Wikipedia editors here mirrors closely the political tensions surrounding the nomination of Preah Vihear.
-The talk page also has a lengthy argument from to 2008, involving several editors, about whether or not the Thai name of the site should be included in the text of the article.
+The talk page also has a lengthy argument from July to October 2008, involving several editors, about whether or not the Thai name of the site should be included in the text of the article.
 The editors appear to be people of Thai and Khmer heritage, with comments that personalise the national tensions such as "we invaded you", and references to contemporary political tensions such as the 2008 street demonstrations in Thailand that saw conflict between the royalist People's Alliance for Democracy and the populist People's Power Party.
@@
 This indicates that consumption of CS-WHL articles is generally high, relative to other articles, and confirms our assertion of Wikipedia as an important source of heritage information.
-But is how is attention distributed across all CS-WHL articles, and how does it relate to sites with conflicts and tensions?
+But how is attention distributed across all CS-WHL articles, and how does it relate to sites with conflicts and tensions?
 
@@
 The country with the next largest proportion, the United Kingdom, is less than half of the United States, and a much greater proportion of edits originating in the UK are on articles about CS-WHL sites located in the UK, compared to the US.
-The country with the next highest proportion of editors is India, and nearly half of those edits are on CS-WHL sites located India.
-Generally, articles about CS-WHL sites receive edits from editors located elsewhere, mostly the US and other English-speaking countries.
+After the United Kingdom is India, and nearly half of those edits are on CS-WHL sites located in the same country Generally, articles about CS-WHL sites receive edits from editors located elsewhere, mostly the US and other English-speaking countries.
 
@@
 The distribution of years between the date of a site's inscription on the WHL and the date of the creation of that site's Wikipedia article has a distinctive trimodal shape.
-The first two modes reflect the relatively large number of sites inscribed on the WHL in 1983 and the early 1990s, before Wikipedia was created in 2001.
+The first two modes reflect the relatively large number of sites inscribed on the WHL in 1983 and the early 1990s, well before Wikipedia was created in 2001.
 The third mode at the zero point on the horizontal axis corresponds to CS-WHL sites that were inscribed after the creation of Wikipedia, and have Wikipedia articles that were created in or around the same year the CS-WHL site was inscribed on the list.
@@
 
-The time series of editing activity at individual sites are highly variable and show display complex patterns (Figure \@ref(fig:wh-wiki-time2)).
+The time series of editing activity at individual sites are highly variable and  display complex patterns (Figure \@ref(fig:wh-wiki-time2)).
 Timbuktu shows spikes of editing activity right after the rebel attacks in mid June 2012, with descriptions of the attacks added to the text of the article at that time.
@@
 For example, one pattern is of editing activity spiking sharply at the time of WHL inscription (e.g.
-Tyre, Masada), a second pattern is editorial activity spiking at the time of WHL inscription and slowly decaying to a baseline level (e.g.
-Carthage), a third pattern is editorial activity that peaks shortly after the time of WHL inscription (e.g.
+Tyre, Masada), a second pattern is editorial activity peaking at the time of WHL inscription and slowly decaying to a baseline level (e.g.
+Carthage), a third pattern is editorial activity that is highest shortly after the time of WHL inscription (e.g.
 Troy, Masada), and finally many sites where editorial activity that shows no signal at all at the time of WHL inscription (Figure \@ref(fig:wh-wiki-time2)).
@@
 They are more frequently viewed, are more frequently linked to by other articles, are longer, and more intensively edited by a greater variety of editors, than the average article.
-These results indicate the high value that Wikipedia users place on CS-WHL, consistent with the goal of the UNESCO World Heritage Committee to maintain a list reflects the world's cultural diversity of outstanding universal value.
+These results indicate the high value that Wikipedia users place on CS-WHL, consistent with the goal of the UNESCO World Heritage Committee to maintain a list that reflects the world's cultural diversity of outstanding universal value.
 Similarly, we found that the effort and attention sites receive on Wikipedia is highly unequal, reflecting the fairly narrow demographic traits of the majority of Wikipedia users and editors, which is further exacerbated by the Eurocentric value system of the World Heritage Committee [@cleere2003uneasy; @smith2006uses p.
@@
 These anonymous editors of articles about CS-WHL are generally not located in the same country as the site they are editing.
-Finding the United States at the first ranked location for anonymous edits is perhaps not surprising as it has the world's largest number of English speakers.
+Finding the United States at the first ranked location for anonymous edits is perhaps not surprising, as it has the world's largest number of English speakers.
 We might similarly expect that the French language Wikipedia (2.3 m articles, 173 m edits, 3.9 m users) would have more edits originating in France or francophone countries on articles about CS-WHL sites in any part of the world.
@@
 
-This is an important observation because it is these editors that control the production of knowledge about CS-WHL articles, and the ability to control information about heritage has several implications.
+This is an important observation because it is these editors that control the production of knowledge about CS-WHL articles, which has several implications for understanding how information about heritage is curated.
 First is that the choices of these editors define community identity, that is, the community of Wikipedia editors, and also the broader community of Internet users that read Wikipedia, by indicating which sites are important and visible, and which are not, by contributing to a digital 'authorized heritage discourse' [@smith2012constrained] that prioritizes their own self-interests (cf.
@@
 We see this spatial pattern on Wikipedia as part of a trend of globalization of heritage, where places that had traditionally contributed to local or regional identities are turned into sanitized playgrounds for rich tourists [@bernbeck2004political].
-Wikipedia may be seen as virtual playground for Anglosphere citizens to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities, perhaps reflecting a cultural rhetoric of 'heritage populism' [@reynie2016specter].
+Wikipedia may be seen as virtual space for Anglosphere citizens to construct a universal heritage that reflects their neo-liberal cultural values, and validates their identities, perhaps reflecting a cultural rhetoric of 'heritage populism' [@reynie2016specter].
 In this way, the representation of heritage on Wikipedia recapitulates a long-standing tradition of colonial subordination of one group's heritage and identity by a more powerful and dominant group.
@@
 
-The results of our time series analyses reveal complex patterns in how heritage-related concerns are realized on Wikipedia.
+The results of our time series analyses reveal complex patterns in how heritage concerns are realized on Wikipedia.
 Some sites show spikes in Wikipedia editing activity that are directly related to the inscription of the site on the WHL, or conflict events at the site.
-However at other sites the rhythms of editing activity seem unrelated to events directly related to the site.
+However for other locations the rhythms of editing activity seem unrelated to events directly related to the site.
 Like the talk pages, which have potential for close reading of heritage activism and disputes, close study of individual edit histories of CS-WHL articles may reveal further patterns of how people engage with heritage on Wikipedia.
@@
 The agency of people participating in heritage-related activities on Wikipedia is highly constrained by the technical characteristics of editing, bots, and consensus-valuing culture.
-Although there are some niches where editors can debate, concerns about state-like actors, violence & destruction, deal-making, etc.
+Although there are some niches where editors can debate, concerns about state-like actors, violence and destruction, deal-making, etc.
 are minor.
@@
 This has important ethical implications because it eliminates the need for academic collaboration with commercial platforms, whose business interests may not align with the researchers' ethics [@schroeder2014big].
-Although free of these commercial interests, a different set of ethics is implied by the exquisite administrative and technical complexity of Wikipedia.
+Although free of these commercial interests, a different set of ethics is implied by the substantial administrative and technical complexity of Wikipedia.
 These structures serve to normalize and historize inequalities, and manage threats to models of control and expertise about heritage [@harrison2015beyond].
@@
 While the Neutral Point of View is a central policy for Wikipedia articles, representations and definitions of cultural heritage are never neutral in any discourse, because they always come from some perspective [@lahdesmaki2019conflicts].
-Given the tremendous popularity and visibility of Wikipedia, is it important that future work on digital heritage in this context continue to critically examine what is absent from, and uncontested in, Wikipedia, and who benefits and suffers from these absences.
+Given the tremendous popularity and visibility of Wikipedia, it is important that future work on digital heritage in this context continue to critically examine what is absent from, and uncontested in, Wikipedia, and who benefits and suffers from these absences.
 
